\documentclass[hyperref={bookmarks=true},xcolor=pdflatex,svgnames,table,compress]{beamer}

\usepackage{config}

\title{One Sentence Joke}
\author{}
\date{}

\beamertemplateshadingbackground{black}{blue}
\setbeamercolor{normal text}{fg=white}
\setbeamercolor{alerted text}{fg=yellow}
\setbeamerfont{rm text}{family=\rmfamily,size=\Large}
\setbeamerfont{sf text}{family=\sffamily,size=\Huge}

\setbeamerfont{title}{shape=\itshape,family=\rmfamily,size=\Huge}
\setbeamercolor{title}{fg=yellow}

\newcommand{\joke}[1]{%
\section{}
\begin{frame}

\begin{columns}[c]
\usebeamerfont{rm text}
\begin{column}{0.1\textwidth}
\alert{\thesection}
\end{column}
\usebeamerfont{rm text}
\begin{column}{0.9\textwidth}
#1
\end{column}

\end{columns}


\end{frame}
}


\begin{document}
\begin{frame}
\titlepage
\end{frame}

\joke{I asked God for a bike, but I know God doesn't work that way. So I stole a bike and asked for
  forgiveness.}

\joke{I want to die peacefully in my sleep, like my grandfather \ldots Not screaming and yelling like the
passengers in his car.}

\joke{Do not argue with an idiot. He will drag you down to his level and beat you with experience.}

\joke{The last thing I want to do is hurt you. But it's still on the list.}

\joke{If sex is a pain in the ass, then you're doing it wrong \ldots}

\joke{The early bird might get the worm, but the second mouse gets the cheese.}

\joke{We live in a society where pizza gets to your house before the police.}

\joke{Having sex is like playing bridge. If you don't have a good partner, you'd better have a good
hand.}

\joke{Some people are like Slinkies \ldots not really good for anything, but you can't help smiling when
you see one tumble down the stairs.}

\joke{Politicians and diapers have one thing in common. They should both be changed regularly, and for
the same reason.}

\joke{War does not determine who is right - only who is left.}

\joke{Women might be able to fake orgasms. But men can fake a whole relationship.}

\joke{We never really grow up, we only learn how to act in public.}

\joke{Men have two emotions: Hungry and Horny. If you see him without an erection, make him a sandwich.}

\joke{Light travels faster than sound. This is why some people appear bright until you hear them speak.}

\joke{My mother never saw the irony in calling me a son-of-a-bitch.}

\joke{I thought I wanted a career, turns out I just wanted paychecks.}

\joke{If you think nobody cares if you're alive, try missing a couple of payments.}

\joke{Sex is not the answer. Sex is the question. ``Yes'' is the answer.}

\joke{Evening news is where they begin with `Good evening', and then proceed to tell you why it isn't.}

\joke{How is it one careless match can start a forest fire, but it takes a whole box to start a
campfire?}

\joke{If 4 out of 5 people SUFFER from diarrhea \ldots does that mean that one enjoys it?}

\joke{Knowledge is knowing a tomato is a fruit; Wisdom is not putting it in a fruit salad.}

\joke{If God is watching us, the least we can do is be entertaining.}

\joke{Never, under any circumstances, take a sleeping pill and a laxative on the same night.}

\joke{I didn't fight my way to the top of the food chain to be a vegetarian.}

\joke{A bus station is where a bus stops. A train station is where a train stops. On my desk, I have a
work station \ldots}

\joke{If I agreed with you we'd both be wrong.}

\joke{Did you know that dolphins are so smart that within a few weeks of captivity, they can train
people to stand on the very edge of the pool and throw them fish?}

\joke{A computer once beat me at chess, but it was no match for me at kick boxing.}

\joke{I saw a woman wearing a sweat shirt with ``Guess'' on it \ldots so I said ``Implants?''.}

\joke{Children: You spend the first 2 years of their life teaching them to walk and talk. Then you spend
the next 16 years telling them to sit down and shut-up.}

\joke{Why does someone believe you when you say there are four billion stars, but check when you say the
paint is wet?}

\joke{Better to remain silent and be thought a fool, than to speak and remove all doubt.}

\joke{A bank is a place that will lend you money, if you can prove that you don't need it.}

\joke{Laugh at your problems, everybody else does.}

\joke{The voices in my head may not be real, but they have some good ideas!}

\joke{A clear conscience is usually the sign of a bad memory.}

\joke{Good girls are bad girls that never get caught.}

\joke{He who smiles in a crisis has found someone to blame.}

\joke{Women will never be equal to men until they can walk down the street with a bald head and a beer
gut, and still think they are sexy.}

\joke{The shinbone is a device for finding furniture in a dark room.}

\joke{The main reason Santa is so jolly is because he knows where all the bad girls live.}

\joke{To steal ideas from one person is plagiarism. To steal from many is research.}

\joke{Some cause happiness wherever they go. Others whenever they go.}

\joke{I discovered I scream the same way whether I'm about to be devoured by a great white shark or if a
piece of seaweed touches my foot.}

\joke{Crowded elevators smell different to midgets.}

\joke{I didn't say it was your fault, I said I was blaming you.}

\joke{Whenever I fill out an application, in the part that says ``If an emergency, notify:'' I put
``DOCTOR''. What's my mother going to do?}

\joke{God must love stupid people. He made SO many.}

\joke{Behind every successful man is his woman. Behind the fall of a successful man is usually another
woman.}

\joke{I always take life with a grain of salt, \ldots plus a slice of lemon, \ldots and a shot of tequila.}

\joke{The sole purpose of a child's middle name, is so he can tell when he's really in trouble.}

\joke{It's not the fall that kills you; it's the sudden stop at the end.}

\joke{Artificial intelligence is no match for natural stupidity.}

\joke{Never hit a man with glasses. Hit him with a baseball bat.}

\joke{There's a fine line between cuddling and holding someone down so they can't get away.}

\joke{A bargain is something you don't need at a price you can't resist.}

\joke{Never get into fights with ugly people, they have nothing to lose.}

\joke{My opinions may have changed, but not the fact that I am right.}

\joke{My psychiatrist told me I was crazy and I said I want a second opinion. He said okay, you're ugly
too.}

\joke{A little boy asked his father, ``Daddy, how much does it cost to get married?'' Father replied,
``I don't know son, I'm still paying.''}

\joke{Some people say ``If you can't beat them, join them''. I say ``If you can't beat them, beat
them'', because they will be expecting you to join them, so you will have the element of surprise.}

\joke{When in doubt, mumble.}

\joke{I intend to live forever. So far, so good.}

\joke{Hospitality: making your guests feel like they're at home, even if you wish they were.}

\joke{If at first you don't succeed, skydiving is not for you!}

\joke{A TV can insult your intelligence, but nothing rubs it in like a computer.}

\joke{Knowledge is power, and power corrupts. So study hard and be evil.}

\joke{Money can't buy happiness, but it sure makes misery easier to live with.}

\joke{Always borrow money from a pessimist. He won't expect it back.}

\joke{Worrying works! 90\% of the things I worry about never happen.}

\joke{Virginity is like a soapbubble, one prick and it is gone.}

\joke{Nostalgia isn't what it used to be.}

\joke{With sufficient thrust, pigs fly just fine.}

\joke{I should've known it wasn't going to work out between my ex-wife and me. After all, I'm a Libra
and she's a bitch.}

\joke{Hallmark Card: ``I'm so miserable without you, it's almost like you're still here.''}

\joke{You're never too old to learn something stupid.}

\joke{A diplomat is someone who can tell you to go to hell in such a way that you will look forward to
the trip.}

\joke{I got in a fight one time with a really big guy, and he said, ``I'm going to mop the floor with
your face.'' I said, ``You'll be sorry.'' He said, ``Oh, yeah? Why?'' I said, ``Well, you won't be
able to get into the corners very well.''}

\joke{Some people hear voices \ldots Some see invisible people \ldots Others have no imagination whatsoever.}

\joke{I like work. It fascinates me. I sit and look at it for hours.}

\joke{We have enough gun control. What we need is idiot control.}

\joke{Women may not hit harder, but they hit lower.}

\joke{Just remember \ldots if the world didn't suck, we'd all fall off.}

\joke{Jesus loves you, but everyone else thinks you're an asshole.}

\joke{I used to be indecisive. Now I'm not sure.}

\joke{I don't trust anything that bleeds for five days and doesn't die.}

\joke{If you keep your feet firmly on the ground, you'll have trouble putting on your pants.}

\joke{To be sure of hitting the target, shoot first and call whatever you hit the target.}

\joke{You are such a good friend that if we were on a sinking ship together and there was only one life
jacket \ldots I'd miss you heaps and think of you often.}

\joke{Going to church doesn't make you a Christian any more than standing in a garage makes you a car.}

\joke{Change is inevitable, except from a vending machine.}

\joke{If you are supposed to learn from your mistakes, why do some people have more than one child.}

\joke{A bus is a vehicle that runs twice as fast when you are after it as when you are in it.}

\joke{Whoever coined the phrase ``Quiet as a mouse'' has never stepped on one.}

\joke{You do not need a parachute to skydive. You only need a parachute to skydive twice.}

\joke{The difference between an oral thermometer and a rectal thermometer is in the taste.}

\joke{When tempted to fight fire with fire, remember that the Fire Department usually uses water.}

\joke{Remember, if you smoke after sex you're doing it too fast.}


\end{document}