\documentclass[12pt,a4paper,onecolumn]{article}
\title{Digest of The New York Times}
\author{The New York Times}
\include{wuxch_config}
\makeindex
\begin{document}
\begin{CJK*}{GBK}{song}
\date{}
\maketitle
\tableofcontents
\pagebreak

\section{Chinese Baby Formula Scandal Widens as 2nd Death Is Announced}

BEIJING -- China's Ministry of Health announced on Monday that a second baby had died in recent
months and that 1,253 others had been sickened by contaminated milk powder in a widening food safety
scandal that has exposed persistent weaknesses in the country's regulatory system.

More than 340 infants remain hospitalized, including 53 in serious condition. Inspection teams are
visiting dairy farms and processing centers in the country's four main milk-producing provinces to
ensure that producers are not violating safety standards.

The Chinese authorities have confirmed that the tainted baby formula was laced with melamine, a
chemical additive sometimes used to make plastics and fertilizer. Last year, after thousands of pets
became ill in the United States, the same chemical was found in pet food and traced to a Chinese
ingredient.

The tainted milk powder has been traced to the Sanlu Group, one of China's biggest dairy producers,
which operates as a joint venture with a New Zealand-based dairy conglomerate, Fonterra. China does
not export milk powder to the United States.

Last week, Sanlu ordered a belated recall of its milk powder even though Chinese state media have
reported that some parents had been complaining of problems since March. More than 10,000 tons of
milk powder have been seized or recalled, according to the Health Ministry, and the authorities have
ordered the company to halt production.

Sickened infants have suffered from kidney stones, and investigators are trying to determine how the
formula became contaminated and whether Sanlu concealed the problem before announcing the recall.

The tainted milk has renewed concerns about China's system of food safety regulation, even as
Communist Party leaders have pledged to improve oversight, with the country now a major food
exporter.

Chinese regulators have repeatedly failed to detect food safety problems in a timely manner.
Moreover, despite ample evidence that secrecy tends to compound safety problems, companies and local
officials still appear determined to minimize or cover up problems in the food supply rather than
alert the public.

Four years ago, at least 13 Chinese babies died of malnutrition after their parents unwittingly fed
them fake baby formula that lacked any nutritional value.

Officials say they are questioning nearly 80 people suspected of involvement in the latest scandal.
On Monday, the police arrested two brothers who ran a milk collection center in Hebei Province
suspected of adding melamine to diluted milk, according to the official news agency Xinhua. Adding
the chemical makes the material test at higher concentrations of protein.

Fonterra, the New Zealand conglomerate that owns a 43 percent share in Sanlu, said it first learned
last month that the Chinese company was selling contaminated powder. On Monday, New Zealand
officials blamed local Chinese officials for failing to take action until the New Zealand government
contacted the central authorities in Beijing.

The prime minister of New Zealand, Helen Clark, said Fonterra officials had been ``trying for weeks
to get official recall, and the local authorities in China would not do it.''

``I think the first inclination was to try and put a towel over it and deal with it without an
official recall,'' she said, according to Television New Zealand, a government network.

Chinese health officials said physicians had examined 10,000 infants who had been fed the Sanlu
formula and found that 1,253 had been sickened. Ma Shaowei, a vice health minister, said many of the
ailing children were from poorer areas, according to a transcript on the Internet. But at least
three babies were hospitalized as far away as Hainan, the island province not far from Vietnam.

It seems likely that contaminated formula had been distributed for several months.

The two deaths attributed to the bad formula, both in Gansu, occurred long before the scandal became
public. One was a 5-month-old boy who died on May 1; the other was an 8-month-old girl who died on
July 22, according to the Health Ministry.

Last year, the pet food scandal touched off a trade dispute between the United States and China.

Chinese regulators responded last year with a high-profile crackdown and banned such uses of
melamine. Regulators expressed outrage about the latest problems, but did not clarify why it took so
long to uncover.

Li Changjiang, minister of the General Administration of Quality Supervision, Inspection and
Quarantine, visited Sanlu's hometown in Hebei Province and was shown bags of the tainted milk powder
seized by the police. ``It's shocking,'' Mr. Li said, according to China Daily. ``It's a crime
against the people.''

Mr. Li said that the result of the investigation would be announced this week but suggested that the
problem occurred at milk processing centers rather than on farms. The centers collect milk from
farmers and then pool it for sale to larger dairy concerns.

``It's unlikely that dairy farmers mixed the industrial chemical melamine in fresh milk,'' Mr. Li
said, according to China Daily. ``We believe the contamination is more likely to have occurred at
milk collecting stations.''

China's state media reported the formula scandal on Wednesday. The next day, the Sanlu Group
recalled all formula that the company had produced before Aug. 6.

But state media have also reported that parents began complaining about the formula in March -- and
that Sanlu did not order a recall.

The Sanlu Group could not be reached for comment on Monday morning. But a Sanlu vice president,
Zhang Zhenling, read a formal apology during a news briefing on Monday in the city of Shijiazhuang,
where the corporation is based.

``The serious safety accident of the Sanlu formula milk powder for infants has caused severe harm to
many sickened babies and their families,'' Mr. Zhang said, according to Xinhua. ``Sanlu Group
expresses its most sincere apology to you.''

\section{G.M., Once a Powerhouse, Pleads for Bailout}

DETROIT --- Just two months after celebrating its 100th birthday, General Motors is facing the grim
prognosis that it may not survive to see another year unless it is rescued by a bailout from the
federal government.

Shares in G.M. sank to their lowest point in 65 years, to \$2.92, on Tuesday, the day after the
company revealed in a federal filing that its ``ability to continue as a going concern'' is in
substantial doubt because it may run out of money by the end of the year.

Its cash cushion has been shrinking by more than \$2 billion a month this fall. If that continues,
G.M.'s reserves will fall below the minimum of \$10 billion in cash it needs to run its global
operations by January, the company said in its third-quarter S.E.C. filing.

In that event, G.M. said it might be unable to pay its suppliers, meet its loan covenants or cover
health care obligations in its labor contracts. The extent of G.M.'s financial crisis, revealed in
greater detail in its filing than it acknowledged before, is proving to be far worse than investors
and analysts expected just last week.

Only an emergency federal bailout seemingly stands between G.M. and a bankruptcy filing, according
to industry analysts.

As the G.M.'s crisis deepens, the pressure increases in Washington to pass a rescue package for up
to \$50 billion in assistance for Detroit's troubled Big Three or risk the economic fallout of a
bankruptcy that would affect hundreds of thousands of jobs that rely on the auto industry.

Democratic Congressional leaders said Tuesday they would push next week for emergency legislation to
help the automakers.

Despite a recent plea from President-elect Barack Obama, the Bush administration has been unwilling
to commit any funds to Detroit beyond a \$25 billion loan program to assist the companies in
developing more fuel-efficient cars.

G.M.'s chairman, Rick Wagoner, says the company cannot wait for aid that may come when Mr. Obama
takes office in January.

``This is an issue that needs to be addressed urgently,'' Mr. Wagoner said in an interview with
Automotive News.

Investors drove G.M.'s stock down for a fifth consecutive day Tuesday. The company's market value
fell to about \$1.7 billion, a more than 90 percent decline from a year ago. A spokesman for G.M.,
Steve Harris, said Tuesday that Mr. Wagoner's job was not in jeopardy and reaffirmed the G.M.
board's support for its embattled chairman.

``Nothing has changed relative to the G.M. board's support for the G.M. management team during this
historically difficult economic period for the U.S. auto industry,'' he said.

The depths of G.M.'s problems came to light in its federal filing that painted a bleak picture of a
company that has lost more than \$20 billion this year and is in danger of not being able to pay its
bills in a few weeks.

``We do not currently expect our operations to generate sufficient cash flow to fund our obligations
as they come due,'' the company said. ``And we do not have other traditional sources of liquidity
available to fund these obligations.''

G.M. ended the third quarter with \$16.2 billion in available cash. The company estimates it needs a
minimum of \$11 billion at any time to pay its bills.

At its current pace, G.M. will have less than \$10 billion by the end of the year -- and that is
after cutting 30 percent of its white-collar work force, halting the development of new models and
temporarily shutting down most of its North American assembly plants in a desperate bid to save
money.

The credit-rating agency Standard \& Poor's cut its ratings on G.M. debt further into junk status on
Tuesday, and Fitch ratings is also considering another cut.

Analysts said G.M.'s inability to raise cash, other than from federal loans, will force another,
deeper round of restructuring -- at a minimum -- to keep it solvent.

``We expect cash outflows to quickly reduce the company's liquidity during the next few quarters,
perhaps to levels that would force G.M. to consider a financial restructuring, even if it does not
file for bankruptcy,'' S. \& P. said.

By its own admission, G.M. cannot cut its costs fast enough to balance the sharp fall in revenue in
what is the worst United States vehicle market in 15 years.

``Looking into the first two quarters of 2009, even with our planned actions, our estimated
liquidity will fall significantly short of the minimum required to operate our business,'' the
company said its third-quarter filing.

G.M. said the deterioration in its balance sheet could make it difficult to pay its suppliers by the
end of this year, and it has no other sources of cash to tap except federal funds.

It also said it might not be in compliance with its credit agreements, including a \$4.5 billion
revolving credit line and a \$1.5 billion term loan. ``There is no assurance we could cure a
default, secure a waiver or arrange substitute financing,'' G.M. said.

\section{Obama and the War on Brains}

Barack Obama's election is a milestone in more than his pigmentation. The second most remarkable
thing about his election is that American voters have just picked a president who is an open,
out-of-the-closet, practicing intellectual.

Maybe, just maybe, the result will be a step away from the anti-intellectualism that has long been a
strain in American life. Smart and educated leadership is no panacea, but we've seen recently that
the converse -- a White House that scorns expertise and shrugs at nuance -- doesn't get very far
either.

We can't solve our educational challenges when, according to polls, Americans are approximately as
likely to believe in flying saucers as in evolution, and when one-fifth of Americans believe that
the sun orbits the Earth.

Almost half of young Americans said in a 2006 poll that it was not necessary to know the locations
of countries where important news was made. That must be a relief to Sarah Palin, who, according to
Fox News, didn't realize that Africa was a continent rather than a country.

Perhaps John Kennedy was the last president who was unapologetic about his intellect and about
luring the best minds to his cabinet. More recently, we've had some smart and well-educated
presidents who scrambled to hide it. Richard Nixon was a self-loathing intellectual, and Bill
Clinton camouflaged a fulgent brain behind folksy Arkansas aphorisms about hogs.

As for President Bush, he adopted anti-intellectualism as administration policy, repeatedly
rejecting expertise (from Middle East experts, climate scientists and reproductive health
specialists). Mr. Bush is smart in the sense of remembering facts and faces, yet I can't think of
anybody I've ever interviewed who appeared so uninterested in ideas.

At least since Adlai Stevenson's campaigns for the presidency in the 1950s, it's been a disadvantage
in American politics to seem too learned. Thoughtfulness is portrayed as wimpishness, and careful
deliberation is for sissies. The social critic William Burroughs once bluntly declared that
``intellectuals are deviants in the U.S.''

(It doesn't help that intellectuals are often as full of themselves as of ideas. After one of
Stevenson's high-brow speeches, an admirer yelled out something like, You'll have the vote of every
thinking American! Stevenson is said to have shouted back: That's not enough. I need a majority!)

Yet times may be changing. How else do we explain the election in 2008 of an Ivy League-educated law
professor who has favorite philosophers and poets?

Granted, Mr. Obama may have been protected from accusations of excessive intelligence by his race.
That distracted everyone, and as a black man he didn't fit the stereotype of a pointy-head ivory
tower elitist. But it may also be that President Bush has discredited superficiality.

An intellectual is a person interested in ideas and comfortable with complexity. Intellectuals read
the classics, even when no one is looking, because they appreciate the lessons of Sophocles and
Shakespeare that the world abounds in uncertainties and contradictions, and -- President Bush, lend
me your ears -- that leaders self-destruct when they become too rigid and too intoxicated with the
fumes of moral clarity.

(Intellectuals are for real. In contrast, a pedant is a supercilious show-off who drops references
to Sophocles and masks his shallowness by using words like ``fulgent'' and ``supercilious.'')

Mr. Obama, unlike most politicians near a microphone, exults in complexity. He doesn't condescend or
oversimplify nearly as much as politicians often do, and he speaks in paragraphs rather than sound
bites. Global Language Monitor, which follows linguistic issues, reports that in the final debate,
Mr. Obama spoke at a ninth-grade reading level, while John McCain spoke at a seventh-grade level.

As Mr. Obama prepares to take office, I wish I could say that smart people have a great record in
power. They don't. Just think of Emperor Nero, who was one of the most intellectual of ancient
rulers -- and who also killed his brother, his mother and his pregnant wife; then castrated and
married a slave boy who resembled his wife; probably set fire to Rome; and turned Christians into
human torches to light his gardens.

James Garfield could simultaneously write Greek with one hand and Latin with the other, Thomas
Jefferson was a dazzling scholar and inventor, and John Adams typically carried a book of poetry.
Yet all were outclassed by George Washington, who was among the least intellectual of our early
presidents.

Yet as Mr. Obama goes to Washington, I'm hopeful that his fertile mind will set a new tone for our
country. Maybe someday soon our leaders no longer will have to shuffle in shame when they're caught
with brains in their heads.


\section{Chinese Activist Wins Rights Prize}

BEIJING -- Hu Jia, a soft-spoken, bespectacled advocate for democracy and human rights in China, was
awarded the Sakharov Prize for Freedom of Thought, Europe's most prestigious human rights prize, on
Thursday. The award was a pointed rebuke of China's ruling Communist Party that came as European
leaders were arriving in Beijing for a weekend summit meeting.

Mr. Hu, 35, was given the prize by the European Parliament despite warnings from Beijing that his
selection would harm relations with the European Union.

Last year, Mr. Hu testified via video link before a hearing of the European Parliament about China's
human rights situation. Weeks later, he was jailed and later sentenced to three and a half years in
prison for subversion based on his writings criticizing Communist Party rule.

Mr. Hu has been one of China's leading figures on a range of human rights issues, while also
speaking out on behalf of AIDS patients and for environmental protection. He had been considered a
front-runner for the Nobel Peace Prize, but lost to the former president of Finland, Martti
Ahtisaari.

``Hu Jia is one of the real defenders of human rights in the People's Republic of China,'' said the
president of the European Parliament, Hans-Gert P\"ottering. ``The European Parliament is sending
out a signal of clear support to all those who support human rights in China.''

The timing may make for a frosty weekend in Beijing, where European leaders are to meet with top
Chinese officials at the Asia-Europe summit meeting, held every two years. This year, the global
financial crisis is expected to dominate, and cooperation will be high on the agenda.

In Beijing on Thursday, Jos\'e Manuel Barroso, the European Commission president, called for
``unprecedented levels of global coordination.''

``It's very simple: we swim together, or we sink together,'' he said in comments reported by The
Associated Press.

Behind the scenes, China had lobbied against Mr. Hu's candidacy for the Sakharov Prize. On Oct. 16,
Song Zhe, the Chinese ambassador to the European Union, wrote a critical letter to Mr. P\"ottering.

``If the European Parliament should award this prize to Hu Jia, that would inevitably hurt the
Chinese people once again and bring serious damage to China-E.U. relations,'' Mr. Song wrote,
according to The Associated Press.

China had also warned against awarding Mr. Hu the Nobel Peace Prize, and a Foreign Ministry
spokesman, Qin Gang, had described him in scathing terms as a convicted criminal.

``The Chinese government will be upset,'' said Teng Biao, a legal expert who has written essays with
Mr. Hu. ``But as a responsible nation that is trying to integrate into the international community,
China has to understand that its conduct should follow international protocols. It should embrace
the criticism as an opportunity to improve China's human rights condition.''

Mr. Hu remains imprisoned in Beijing and could not be reached for comment. His wife, Zeng Jinyan, a
prominent blogger and human rights activist, also could not be contacted. She has lived for months
under house arrest with the couple's infant daughter.

The award to Mr. Hu is an embarrassment for the Communist Party two months after China's successful
staging of the Olympic Games. During the Olympics, the Chinese government proved it could smoothly
manage the world's biggest sporting event, but the government also prevented demonstrations at
designated protest zones, instituted broad censorship restrictions on the domestic news media and
placed numerous dissidents under house arrest or surveillance.

Mr. Hu's conviction in April was part of a nationwide crackdown against dissidents in what many
human rights advocates considered a pre-Olympic silencing campaign. Mr. Hu, a Buddhist, has
dedicated himself to a range of issues during the past 12 years, including environmental protection,
helping AIDS patients, championing the legal rights of Chinese citizens and promoting greater
democracy.

He also used a personal Web site and e-mail messages to become a one-man clearinghouse of
information on rights abuses and other controversies that officials preferred to keep quiet.

``Whatever he does, he always stands in the forefront,'' Mr. Teng said in an earlier interview.
``Everything he wrote, everything he said, is straight from his heart. We have poor people and
marginalized people in society whose voices are being muzzled. Hu Jia was trying to be the spokesman
for the unheard voices.''

Mr. Hu graduated from Beijing's Capital University of Economics and Business in 1996 and almost
immediately plunged into China's nascent civil society. He traveled to Inner Mongolia to plant trees
as a measure to slow the advance of the Gobi Desert.

By 2000, China was facing the rapid spread of AIDS, a problem the government had initially denied
and remained reluctant to publicly confront. Mr. Hu formed a nongovernmental organization, Loving
Source, and focused on caring for people infected with H.I.V. in a blood-selling scandal in Henan
Province.

Gao Yaojie, a prominent advocate for AIDS patients in China, recalled how Mr. Hu once rode a bicycle
down a rutted dirt road to reach an isolated village decimated by AIDS. The road became narrower and
potted with holes until Mr. Hu simply put the bike on his shoulder and walked to deliver help to a
village where local officials were trying to cover up the problem.

``We didn't do anything wrong,'' Dr. Gao said in an interview earlier this month. ``The only thing
we did was to help H.I.V.-positive people. But we were always under great pressure from the
government.''

Mr. Hu later began joining Internet petition campaigns calling for the release of political
prisoners, while also calling on the authorities to uphold legal rights under the Chinese
Constitution.

His activism quickly made him a target. In 2006, he spent 168 days under house arrest. Rather than
disappear from public view, he produced a documentary, ``Prisoners in Freedom City,'' which included
video of state security agents harassing his wife as she tried to leave their apartment complex,
which is known as Bo Bo Freedom City.

Indeed, as Mr. Hu faced constant surveillance and harassment, he continued to use the Internet to
push for political reform and publicize abuses. His testimony via video link before the European
parliamentary committee came last November.

``It is ironic that one of the people in charge of organizing the Olympic Games is the head of the
Bureau of Public Security, which is responsible for so many human rights violations,'' he testified.
``It is very serious that the official promises are not being kept before the Games.''

\section{Guilty Verdict in Cyberbullying Case Provokes Many Questions Over Online Identity}

Is lying about one's identity on the Internet now a crime?

The verdict\index{verdict}\hypertarget{verdict}{}\footnote{\textbf{verdict}:$[$\textprimstress
v\schwa\textlengthmark dikt$]$. \textit{n}. the findings of a jury on the issues of fact submitted
to it for examination and trial.(陪审团的)裁决,裁定\hyperlink{verdict}{\textasciicircum}} Wednesday
in the MySpace
cyberbullying\index{bully}\hypertarget{bully}{}\footnote{\textbf{bully}:$[$\textprimstress buli$]$.
\textit{vt}.恃强欺弱者;恶霸\hyperlink{bully}{\textasciicircum}} case raised a variety of questions
about the terms that users agree to when they log on to Web sites.


The defendant in the case, a Missouri woman, was convicted by a federal jury in Los Angeles on three
misdemeanor\index{misdemeanor}\hypertarget{misdemeanor}{}\footnote{\textbf{misdemeanor}:$[$\textsecstress
misdi\textprimstress min\schwa$]$. \textit{n}.轻罪\hyperlink{misdemeanor}{\textasciicircum}} counts
of computer
fraud\index{fraud}\hypertarget{fraud}{}\footnote{\textbf{fraud}:$[$fr\openo\textlengthmark d$]$.
\textit{n}. deliberate deception, trickery, or cheating intended to gain an advantage.欺诈, 欺骗行为
\hyperlink{fraud}{\textasciicircum}} for having misrepresented herself on the popular social network
MySpace. The woman, Lori Drew, posed as a teenage boy in using the account to send first friendly
and then
menacing\index{menacing}\hypertarget{menacing}{}\footnote{\textbf{menacing}:$[$\textprimstress
men\schwa s$]$. \textit{n vt vi}. to threaten with violence, danger, etc.威胁
\hyperlink{menacing}{\textasciicircum}} messages to Megan Meier, 13, who killed herself shortly
after receiving a message in October 2006 that said in part, ``The world would be a better place
without you.''

MySpace's terms of service require users to submit ``truthful and accurate'' registration
information. Ms. Drew's creation of a phony profile amounted to ``unauthorized access'' to the site,
prosecutors\index{prosecute}\hypertarget{prosecute}{}\footnote{\textbf{prosecute}:$[$\textprimstress
pr\openo sikju\textlengthmark t$]$. \textit{vi vt}. to bring a criminal action against (a person)
for some offence.检举、告发某人; 对某人提起公诉\hyperlink{prosecute}{\textasciicircum}} said, a
violation of the Computer Fraud and Abuse Act of 1986, which until now has been used almost
exclusively to prosecute hacker crimes.

While the Internet's anonymity was used in this case as a cloak to bully Megan, other users say they
have perfectly good reasons to construct false identities online, if only to help protect against
the theft of personal information, for example.

``It will be interesting to see if issues of safety and security will eventually trump the hallmark
ideology of free, largely anonymous or pseudonymous participation in cyberspace,'' said Sameer
Hinduja, a professor of criminology and criminal justice at Florida Atlantic University.

Andrew M. Grossman, senior legal policy analyst for the Heritage Foundation, said the possibility of
being prosecuted for online misrepresentation, while remote, should worry users nonetheless.

``If this verdict stands,'' Mr. Grossman said, ``it means that every site on the Internet gets to
define the criminal law. That's a radical change. What used to be small-stakes contracts become
high-stakes criminal prohibitions.''

The judge in the Los Angeles case, George H. Wu, is to hear motions next month for its dismissal.
Ms. Drew's defense asserts among other things, as it did at trial, that she never read MySpace's
terms of service in detail.

``The reality, recognized by almost everyone, is that the vast majority of Internet users do not
read Web site terms of service carefully or at all,'' said Phil Malone, director of the Cyberlaw
Clinic at Harvard Law School.

Representatives of MySpace declined to make any executives available for interviews about the case.
In a statement, the site said that it did not tolerate cyberbullying and would continue to work with
industry experts to raise awareness of the ``harm it can potentially cause.''

Mr. Hinduja, who writes for the research site CyberBullying.us, said there had been a handful of
cases involving teenagers who were ``driven to suicide in part because of cyberbullying by peers.''
What drew the greatest attention to Megan's death, he said, was that it involved the actions of an
adult, Ms. Drew, now 49, whose daughter's friendship with Megan had soured.

It remains easy to create a fraudulent account on social networking sites like MySpace and Facebook,
though a witness at Ms. Drew's trial, Jae Sung, a MySpace vice president for customer care, said
``impostor profiles'' were deleted when they were flagged by users or discovered by the Web site's
employees.

A number of corporations are competing to develop age verification software for Web sites. But
relying on technology to confirm a user's identity is not without drawbacks. There are legitimate
reasons to hide one's name and other information online, be it concern about identity theft or a
need for comfort when asking for advice or help.

``We've been telling our kids to lie about ID information for a long time now,'' said Danah Boyd, a
fellow at the Berkman Center for Internet and Society, at Harvard.

Ms. Boyd said forms of digital street outreach were needed.

``There are lots of kids hurting badly online,'' she said. ``And guess what? They're hurting badly
offline, too. Because it's more visible online, people are blaming technology rather than trying to
solve the underlying problems of the kids that are hurting.''

\section{Hoping to Draw Market Share With Touch Screens}

This holiday, cellphone makers and carriers are pushing some shiny new toys: phones with
touch-sensitive screens like the one on Apple's iPhone.

The companies are hoping to duplicate the blockbuster success of the iPhone with models that, in
their glassy minimalism, end up looking a lot like it. These include the G1, powered by Google's
Android software; the Instinct from Samsung; the LG Dare; and, most recently, Research in Motion's
much-anticipated BlackBerry Storm.

But with consumers keeping a close watch on their bank balances, analysts and industry experts say
most touch-screen phones will have trouble getting onto the list of this season's must-have gadgets.

The surge of touch screens has its roots in the introduction of the iPhone on AT\&T's network in
June 2007, which left rival carriers scrambling for comparable offerings.

``What you're seeing right now is the first wave of competitors spurred by the media juggernaut for
the iPhone,'' said Ed Snyder, a telecommunications industry analyst with Charter Equity Research.
Mr. Snyder said that when the iPhone
hype\index{hype}\hypertarget{hype}{}\footnote{\textbf{hype}:$[$haip$]$. \textit{n}. 天花乱坠的广告宣
传\hyperlink{hype}{\textasciicircum}} hit, ``no credible cellphone executive could not get a
touch-screen phone started.''

Since its introduction, the iPhone, which is available only through AT\&T in the United States, has
helped AT\&T steal customers from other carriers. Wireless service operators are now concentrating
on retaining current subscribers as much as they are trying to reel in new ones, said Charles
Golvin, a principal analyst at Forrester Research. Part of that strategy, Mr. Golvin said, is
offering perks like exclusive ``presales'' of hot new models to subscribers.

Phone shoppers say carriers and contracts have a big influence on their decisions about phones.
``I'm pretty sure my next phone will be a touch screen,'' said Vernon McIntosh, 40, a personal
trainer from New York who is an AT\&T customer.

Mr. McIntosh was in a Verizon store last week and said he was choosing between an iPhone and the
BlackBerry Storm. ``But I'm not
eligible\index{eligible}\hypertarget{eligible}{}\footnote{\textbf{eligible}:$[$\textprimstress
elid\yogh\schwa bl$]$. \textit{adj}. fit, worthy, or qualified, as for an office or function.有资格当
选的, 有条件被选中的.\hyperlink{eligible}{\textasciicircum}} for an upgrade at AT\&T,'' he said.
``It might be cheaper to switch contracts.''

To help drum up excitement for the release of the Storm, Verizon Wireless rolled out a teaser
campaign in early October that zeroed in on the phone's distinctive feature: a palpable clicking
sensation when the screen is pressed.

The Storm, which costs \$200 after rebate with a new two-year contract, also has built-in appeal for
the existing base of BlackBerry fanatics, and it appears to be a hit. When the Storm went on sale
Nov. 21, people lined up outside Verizon stores to get their hands on it, and many stores quickly
sold out.

An employee at a Verizon Wireless store in Midtown Manhattan said Friday that none of the company's
stores in Manhattan had the Storm in stock, but that people were still streaming in to place orders.
The earliest those customers can expect their phones to ship is Dec. 15, the employee said.

Nancy Stark, a spokeswoman for Verizon, said she could not provide figures on sales or inventory for
the Storm, although she did say it had been the company's ``fastest-selling phone to date.''
Verizon's next touch-screen models are the \$350 HTC Touch Pro, available now, and the \$249 Samsung
Omnia, which is for sale online and will be in stores next week.

Touch-screen phones do have their critics. Mr. Snyder says the bigger screens are a drain on battery
life, and the phones require users to look at the screen instead of getting to know the phone's
buttons by feel.

``You're getting all these extras so you can look at the phone and stand still, when you bought the
phone so you could move,'' he said. ``Only a niche of users are going to be willing to spend money
to have the extra capability.''

``The hype surrounding the touch-screen technology far exceeds its impact,'' Mr. Snyder said.

Dave Perry, a business developer who was shopping in a Verizon store in Manhattan last week, said he
liked the user-friendliness and big screens of touch-screen phones. ``But there are drawbacks: the
accuracy of typing and reliability of the screen,'' he said.

``I don't necessarily think the technology is where it needs to be,'' Mr. Perry said, adding that
the occasional problems and slow responses from the devices were ``not something I'm willing to wait
for.''

Touch-screen phones remain a fraction of the overall mobile phone market, but sales have been
soaring. In the 12 months through September, sales of the phones in North America grew 130 percent,
in contrast to 4 percent growth in the overall phone market, according to comScore M:Metrics, a
market research firm.

As of September, M:Metrics data shows, more than 2.6 million people in North America had some model
of the iPhone. The second-most-popular touch-screen model was the LG Voyager, which was available
through Verizon Wireless and had 851,000 users.

Mr. Golvin said it was unlikely that touch-screen phones would take over the industry.

``There's no question that it's a very fast-growing segment of the market,'' Mr. Golvin said. ``It's
become one of the form factors that some consumers want.''

But Mr. Golvin said there had been similar frenzies for flip phones and candy-bar-style phones when
they were introduced. ``And yet today, there are still plenty of people who prefer a flip phone.''

Touch-screen technology first appeared in devices like the Treo that were aimed at professional
users, and the screens were best activated with thin plastic styluses. Since the advent of the
iPhone, more touch screens are activated with the fingers, and the phones themselves are aimed at
mainstream users.

The phones also tend to cost several hundred dollars, which could hurt sales in an economic
downturn. For its part, Sprint is fighting the barrage of high-end phones from its competitors with
a new marketing campaign that emphasizes the money-saving value of its phones and plans.

Ev Gonzalez, director of device marketing for Verizon Wireless, said the company recognized that
touch-screen technology was not for everyone. In fact, he said, touch screens are likely to show up
on a limited number of the company's devices.

``There are consumers who are looking for straight phone services,'' Mr. Gonzalez said. ``Where the
touch screen is not needed, we won't provide it.''

\section{Top Indian Security Official Resigns as Toll Eclipses 180}

MUMBAI, India -- The top domestic security official resigned in disgrace on Sunday for the failure
to thwart or quickly contain the horrific terrorist attacks in Mumbai last week, as India's
government announced a raft of measures to bolster antiterrorism efforts and struggled to
calibrate\index{calibrate}\hypertarget{calibrate}{}\footnote{\textbf{calibrate}:$[$\textprimstress
k\ae libreit$]$. \textit{vt}. to measure the calibre of (a gun, mortar, etc).校
准.\hyperlink{calibrate}{\textasciicircum}} a response to what it views as Pakistani complicity.

The Bush administration, hoping to defuse the possibility of hostilities, announced it was sending
Secretary of State Condoleezza Rice to India this week ``to stand in
solidarity\index{solidarity}\hypertarget{solidarity}{}\footnote{\textbf{solidarity}:$[$\textsecstress
s\openo li\textprimstress d\ae riti$]$. \textit{n}. unity of interests, sympathies, etc, as among
members of the same class.团结一致; 休戚相关.\hyperlink{solidarity}{\textasciicircum}} with the
people of India as we all work together to hold these
extremists\index{extremists}\hypertarget{extremists}{}\footnote{\textbf{extremists}:$[$iks\textprimstress
tri\textlengthmark mist$]$. \textit{n}. a person who favours or resorts to immoderate,
uncompromising, or fanatical methods or behaviour, esp in being politically radical. 过激主义者, 极端
分子.\hyperlink{extremists}{\textasciicircum}} accountable.''

Top officials have suggested that groups based in Pakistan had some involvement in the attacks, but
the officials have not blamed the Pakistan government. Among the options on the table for
responding, officials and analysts said, are the suspension of diplomatic relations and a
cross-border raid into Pakistan against suspected training camps for militants.

The security official, Shivraj Patil, the home minister, became the first senior official in Prime
Minister Manmohan Singh's administration to leave office over the Mumbai attacks, which have
traumatized\index{trauma}\hypertarget{trauma}{}\footnote{\textbf{trauma}:$[$\textprimstress
  tr\openo\textlengthmark m\schwa$]$. \textit{n}. a powerful shock that may have long-lasting
  effects. 心灵创伤, 精神创伤.\hyperlink{trauma}{\textasciicircum}} the nation for their
audacity\index{audacity}\hypertarget{audacity}{}\footnote{\textbf{audacity}:$[$\openo\textlengthmark\textprimstress
  d\ae siti$]$. \textit{n}. 大胆;胆识;厚脸无耻;无礼.\hyperlink{audacity}{\textasciicircum}} and have
laid bare glaring deficiencies in India's intelligence and enforcement abilities. The pressures on
the government are especially acute with elections only six months away.

While Indian officials insisted publicly that the mayhem was carried out by only 10 heavily armed
men, there were new indications that others had been involved and that the attackers had at least
some accomplices pre-positioned on the ground.

The three-day siege of Mumbai, the country's financial capital, ended Saturday with a death toll of
at least 188, hundreds wounded and two famous five-star hotels, the Taj Mahal Palace \& Tower and
the Oberoi, where most of the killing took place, partly in ruins.

At least 28 of the dead were foreigners, including at least six Americans and eight Israelis killed
at a Jewish religious center that had been seized by the attackers. It was stormed by
elite\index{elite}\hypertarget{elite}{}\footnote{\textbf{elite}:$[$ei\textprimstress
li\textlengthmark t$]$. \textit{n}. the most powerful, rich, gifted, or educated members of a group,
community, etc.精华,精锐,中坚分子.\hyperlink{elite}{\textasciicircum}} Indian commandos.

Despite repeated assertions by Pakistan's government that it bore no responsibility, the attacks
have raised the pitch of India-Pakistan tensions to their most dangerous level in years. Not since
the December 2001 suicide attack on the Indian Parliament in New Delhi, which India blamed on
Pakistani groups, have there been such blunt Indian accusations about outlaws based across the
border; that episode prompted the two countries to send their armies to the border, sparking fears
of war between the nuclear neighbors.

On Sunday, a senior government official said Mr. Singh's administration would have to consider a
range of measures to show toughness toward Pakistan. ``The government is under pressure; we are
taking steps,'' the official said. ``We're not trying to say we're going to attack them. Short of
that everything will have to be pursued.''

The official, who spoke on condition of anonymity because of the delicacy of the situation, said,
``Certainly we are not going to sit back with Pakistan unleashing this terror on India.''

Reuters quoted a senior police official as saying Sunday that the sole gunman captured alive had
told the police he was a member of the Pakistan-based Lashkar-e-Taiba organization, blamed for
attacks in Indian-administered Kashmir and elsewhere.

The government has not allowed outside access to the captive, who is said to have identified himself
as Ajmal Amir Qasab, a Pakistani citizen who was wounded in the leg and was being treated at a
military hospital.

An officer of the Anti-Terror Squad branch in Mumbai, who spoke on condition of anonymity because he
was not authorized to speak to the news media, said the man had given inconsistent answers to
questioning, sometimes saying there were 10 attackers, sometimes more than 10.

The officer also said that Anti-Terror Squad investigators believed there were accomplices who may
have left weapons at the hotels for the gunmen, and that names and telephone numbers of five Mumbai
residents were found among the cellphones and wallets of the attackers.

He also confirmed reports in the Indian press that a satellite phone used by the attackers had been
used to call a phone number in the Pakistani city of Karachi during the assault.

The officer also disputed assertions in the Indian press that the attackers were Pakistani, saying
they were of many nationalities, including Malaysian.

While there was no immediate suggestion of Pakistani-Indian hostilities, it is clear that India must
carefully consider how to deal with its concerns about Pakistan. On the one hand, public pressure
compels Mr. Singh's administration to take a tough stance, at least publicly. On the other hand, his
government may not want to squander a chance at negotiating peace with Pakistan's elected civilian
government.

In any event, the mere idea of Indian-Pakistani hostilities cannot bring much comfort to Washington,
which needs Pakistan's attention on curbing radical groups on the Afghan border and can hardly
afford another crisis between Pakistan and India.

At the same time, particularly with elections looming, Indian officials are keenly aware of the need
to shore up confidence in the domestic security apparatus.

On Sunday evening, Mr. Singh said his government would expand the National Security Guards, the
elite antiterrorist unit that sent commandos to flush out the attackers from the two hotels and the
headquarters of a Jewish religious organization.

Mr. Singh also said in a written statement that discussions were under way to establish a federal
agency of investigation to streamline the work of state and national agencies, and fortify maritime
and air security. The police have said the attackers came by boat. The Indian government had been
warned as far back as March 2007 of infiltration by sea.

``Clearly, much more needs to be done,'' Mr. Singh said, ``and we are determined to take all
necessary measures to overhaul the system.''

The chairman of the Tata Group, the
conglomerate\index{conglomerate}\hypertarget{conglomerate}{}\footnote{\textbf{conglomerate}:$[$k\openo
n\textprimstress l\openo m\schwa rit$]$. \textit{n}. 联合大企
业.\hyperlink{conglomerate}{\textasciicircum}} that owns the Taj hotel, asserted that it had been
warned about the possibility of a terrorist attack and had taken some measures, but that the
assailants knew exactly how to penetrate the hotel's security.

``They came from somewhere in the back; they planned everything,'' the chairman, Ratan Tata, said in
an interview broadcast Sunday on CNN. ``They went through the kitchen; they knew what they were
doing.''

In a telephone interview from the capital, the junior home minister, Shriprakash Jaiswal, said the
government would double the size of the 7,400-strong National Security Guards. The force was created
after the 1984 siege of the Golden Temple in Amritsar by Sikh separatist militants.

The guard's Black Cat commandos emerged as heroes last week, having slithered down ropes from
helicopters and rescued trapped civilians as gunmen marauded through the hotels.

But uncomfortable questions have been raised about whether the guard could have begun its operations
sooner and why it took its commandos so long to defeat the attackers.

In Israel, while leaders publicly praised India for its response to the attack, questions also were
raised about whether the commando mission to rescue hostages in the Jewish center, Nariman House,
had been botched\index{botch}\hypertarget{botch}{}\footnote{\textbf{botch}:$[$b\openo t\esh$]$.
\textit{vt vi}. to spoil through clumsiness or ineptitude.粗拙地修补; 因笨手笨脚弄
坏.\hyperlink{botch}{\textasciicircum}}.

Witnesses have compared the destruction inside the center to an earthquake, with floors, walls and
stairwells blasted apart by two days of shooting, explosions and grenades.

The head of the guard, J. K. Dutt, confirmed on Sunday in a news conference that most of the
civilians had been killed in the hotels before the guard's operation began. His troops' first
obligation\index{obligation}\hypertarget{obligation}{}\footnote{\textbf{obligation}:$[$\textsecstress\openo
bli\textprimstress ei\esh\schwa n$]$. \textit{n}. a moral or legal requirement; duty. 义务; 职
责.\hyperlink{obligation}{\textasciicircum}}, he told reporters, was to make sure that there was
``no loss of innocent lives.''

One commando, Sunil Kumar Yadav, who was recovering at a hospital from bullet wounds in his leg,
echoed that he was instructed to be extremely cautious inside the Taj hotel, because foreign guests
were inside.

He said the commandos could not determine the exact locations of the gunmen, nor their total number,
in such a large sprawling
sprawl\index{sprawl}\hypertarget{sprawl}{}\footnote{\textbf{sprawl}:$[$spr\openo\textlengthmark
l$]$. \textit{vt vi}. to sit or lie in an ungainly manner with one's limbs spread out.懒散, (拙笨地)
伸开(手足);使蔓生, 使散漫地伸开, 潦草地书写.\hyperlink{sprawl}{\textasciicircum}} hotel -- until
they came out with guns blazing. It was dark and smoky from the countless explosions inside, he
said, and visibility was poor.

Explaining the nearly 60 hours that passed before the Taj was cleared entirely, Mr. Dutt said that
the terrorists were ``well trained'' and more familiar with the hotel than expected.

In addition, the Taj was littered with unexploded
grenades\index{grenade}\hypertarget{grenade}{}\footnote{\textbf{grenade}:$[$ri\textprimstress
neid$]$. \textit{n}. a small container filled with explosive thrown by hand or fired from a rifle.手
榴弹.\hyperlink{grenade}{\textasciicircum}}, which had to be defused. He said the last three gunmen
at the Taj eluded capture for so long by repeatedly setting fires.

On one side of the Taj, workers boarded up the sidewalk at one of the city's most exclusive shopping
arcades, barricading the now-improbable row of luxury labels, from Zegna to Louis Vuitton.

Remu Javeri, owner of Joy Shoes, the only Indian boutique there, stood across the street. He had
practically grown up at the Taj, he said, where his family opened the store before independence in
1947. ``I know every single waiter in here,'' he said. ``I've grown up with them. I've lost some
very good friends.''

\section{The Special Sting of Personal Terrorism}

VERLA, India -- This was not terror -- not as Indians understood it. This was war.

The killers stormed the streets of Mumbai, India's financial capital, with machine guns and bags of
grenades. They did not strike with the terrorist's fleeting anonymity. Their work was fastidiously
deliberate. It went into a second day, then a third. They took time to ask your nationality and
vocation. Then they spared you, or herded you elsewhere, or shot you in the back of your skull.

As a surprise attack became a 48-hour struggle, the burden of responding transferred from the police
to soldiers. The language was of war: television anchors spoke of buildings ``sanitized'' and
``flushed out,'' of ``final assaults'' and ``collateral damage.'' Helicopters hovered over Mumbai,
and commandos dropped onto roofs. The grainy television imagery suggested not so much a terrorist
attack as the shapeless, omnidirectional chaos of Iraq.

While the hostage situation endured, more was unknown than known. Rumors flew, unconfirmed. Did you
hear? They shot all the women at the hotel switchboard. Did you hear? They executed a young mother
and her children. Did you hear? They sent a hostage out of the building to get food for their
attackers. Truth was complicated; everything blurred.

But what slowly became clear was that this was an attack of especial barbarism, because it was so
personal. It was unlike the many strikes of the last many months, bombs left in thronging markets or
trains or cars: acts of shrinking cowardice. The new men were not cowards. They seemed to prolong
the fight as long as they could. They killed face to face; they wanted to see and speak to their
victims; they could taste the violence they made.

A good story has characters, and a terrorist attack without characters tempts a society to forget. A
wave of recent Indian attacks, more anonymous and less dramatic, offered little focus for public
opinion.

For better or worse, the public has its characters now. As the weekend arrived, it was not clear who
the men were, even as India's government hinted at Pakistani connections. But even without learning
their names, it was so easy to imagine them this time, combing the hallways, asking life-or-death
questions, pulling women and children from their rooms at midnight.

For a country with no dearth of terrorism in its past, it is perhaps the fleshy immediacy of these
men and their deeds that makes this a defining assault -- one that separates all attacks of the past
from those yet to come. In the television studios, on the roads, in the anguished phone calls of
friends to friends, Indians said the words again and again: This is our 9/11.

``It is an Indian variant of 9/11, and today India needs to respond the way America did,'' Ravi
Shankar Prasad, a member of Parliament from the rightist Bharatiya Janata Party, said on television.

But if this was India's 9/11, it seemed so only to certain citizens, and not, apparently, to their
government.

It took 18 hours for Prime Minister Manmohan Singh to come on television. He is a reflective, decent
man. But he was emotionless, his mouth moving and nothing else. He knows all too well the history of
blaming Pakistan and its militants for attacks, only to come up short on evidence. He said the
attacks ``probably'' had a foreign hand. His most specific idea was ``police reform'' and the
``tightening'' of laws to close ``loopholes.'' He called for ``peace and harmony.''

His temperateness helped to keep the ever-present threat of religious riots at bay. But it also
seemed to misread the mood of a country that wanted it to be 9/11 -- if not in the sense of war and
conquest, then in the sense of instant clarity, of the simple feeling that an era had ended and that
enough was, at last, enough.

When the video of Mr. Singh's address was posted on YouTube, many said online what others were
saying on the ground. He was ``expressionless,'' a ``brilliant teacher but no leader,'' an
``ineffective puppet.'' One user wrote: ``He should have given a strong warning and threat to
terrorists and those who support them. Unfortunately he is too soft.''

Nor did the government's retaliation inspire. The commandos who came at long last and saved the day
were heroic, working room by room to retake the two besieged hotels. But India learned thereby that
Mumbai, with its 19 million people, lacks commandos of its own. They were flown in from the capital,
New Delhi.

Meanwhile, ``army sources'' leaked to the press that they had warned the government of an impending
attack days before, only to be ignored, as usual.

``The scale, intensity and level of orchestration of terror attacks in Mumbai put one thing beyond
doubt: India is effectively at war and it has deadly enemies in its midst,'' The Times of India, a
leading English-language daily, wrote in an editorial published Friday. ``The question now,'' it
added, ``is whether the nation can show any serious degree of resolve and coordination in
confronting terror.''

The government, in its defense, walks a fine line. Show too little resolve, and attacks happen. Show
too much, and you galvanize hatred domestically and exacerbate tensions abroad, notably with
Pakistan.

``It is extremely important to understand that the criminal activities of a minuscule group, even if
it turns out to have home-grown elements, say nothing about Indian Muslims in general, who are an
integral part of the country's social fabric,'' Amartya Sen, the Harvard economist and Indian-born
Nobel laureate, wrote in an e-mail message. ``Even if it turns out that the Mumbai terrorists had a
base in Pakistani territory, India has to take full note of the fact that the bulk of Pakistani
civil society is an ally, not an enemy, in the battle against Islamist terrorism, for they too
suffer greatly from the violence of a determined minority based in their country.''

On Friday, Pakistan's prime minister, Yousuf Raza Gilani, agreed to send the powerful chief of his
country's intelligence services to India, to receive any evidence, as a gesture of good will.

People purporting to be the attackers have said they belong to a group called the Deccan Mujahedeen,
and have claimed to be waging a war in Islam's name. It was uncertain whether they are of domestic
or foreign origin.

Whichever it is, they have crossed yet another line with these attacks. Islamist militants in India
have in recent years lived somewhat apart from the global Islamist struggle. They bombed and killed,
but their enemies were Indian Hindus, not ``Jews and crusaders,'' and their targets were markets and
cinema halls that drew Indians, not foreigners.

This attack, in contrast, went after five-star hotels, a popular restaurant and a Jewish community
center. The gunmen were reported to show a preference for Britons and Americans as hostages.

With their brutality, their sophistication, their links to the ideology of terrorism elsewhere,
these attacks seemed, then, to usher in a new day. Late in the week, as the gunfire crackle trailed
off, many Indians appeared to long for a sign that this attack would muster new will.

A text-message moving among Mumbaikars expressed the uniqueness of the now: ``Brothers and sisters,
it's time to wake up and do something for the country -- however little -- related to this or not --
start today and continue it through the years -- do not forget as easily as we are used to
forgetting.''

Many told themselves and each other that this time would change things, just as Americans had told
themselves after 9/11. But they knew their own history, and America's, and they seemed, even as they
spoke the words, to disbelieve them already.

\section{Armed Teams Sowed Chaos With Precision}

MUMBAI, India -- As Prasan Dhanur prepared his 13-foot boat on Wednesday evening for a hard night of
fishing, he saw something strange.

A black inflatable lifeboat equipped with a brand new Yamaha outboard motor threaded its way among
the small, wooden fishing boats at anchor and pulled up to the slum's concrete pier.

Ten men, all apparently in their early 20s, jumped out. They stripped off orange windbreakers to
reveal T-shirts and blue jeans. Then they began hoisting
hoist\index{hoist}\hypertarget{hoist}{}\footnote{\textbf{hoist}:$[$h\openo ist$]$. \textit{vt}. 把…吊
起,升起.\hyperlink{hoist}{\textasciicircum}} large, heavy backpacks out of the boat and onto their
shoulders, each taking care to claim the pack assigned to him.

Mr. Dhanur flipped his boat light toward the men, and Kashinath Patil, a 72-year-old harbor official
on duty nearby, asked the men what they were doing.

``I said: 'Where are you going? What's in your bags?' '' Mr. Patil recalled. ``They said: 'We don't
want any attention. Don't bother us.' ''

Thus began a crucial phase of one of the deadliest terrorist assaults in Indian history, one that
seemed from the start to be coordinated
meticulously\index{meticulous}\hypertarget{meticulous}{}\footnote{\textbf{meticulous}:$[$mi\textprimstress
tikjul\schwa s$]$. \textit{adj}. 极仔细的; 一丝不苟的\hyperlink{meticulous}{\textasciicircum}} to
cause maximum fear and chaos.

Indian officials had said little publicly about the attackers until Saturday, when the Mumbai police
commissioner, Hasan Gafoor, said a total of 10 militants had been responsible for the
mayhem\index{mayhem}\hypertarget{mayhem}{}\footnote{\textbf{mayhem}:$[$\textprimstress meihem$]$.
\textit{n}. 大混乱, 大破坏\hyperlink{mayhem}{\textasciicircum}}. But it remained unclear whether he
was referring to 10 attackers arriving by sea to join other accomplices. Unconfirmed local news
reports suggested some militants had embedded themselves in Mumbai days before the attacks.
Investigations were ongoing Saturday night. In any event, the synchronized assaults suggested a high
level of training and preparation.

Mr. Dhanur and Mr. Patil said in interviews that they did not see the guns hidden in the backpacks,
and did not call the police as they watched the men walk into town on Wednesday, leaving their boat
and windbreakers at the dock. Not long afterward, fanning out across South Mumbai, as other
attackers spread out after landing in other boats, the men began unleashing
unleash\index{unleash}\hypertarget{unleash}{}\footnote{\textbf{unleash}:$[$\textprimstress\pwedge
n\textprimstress li\textlengthmark\esh$]$. \textit{vt}. 解开\ldots的皮带(链索) 释放; 放纵; 发
动.\hyperlink{unleash}{\textasciicircum}} deadly assaults everywhere they went.

At the Chhatrapati Shivaji Terminus, the train station that appears to have been the first location
hit, a
fusillade\index{fusillade}\hypertarget{fusillade}{}\footnote{\textbf{fusillade}:$[$\textprimstress
fju\textlengthmark zi\textsecstress leid$]$. \textit{n}. a simultaneous or rapid continual discharge
of firearms.齐射, 连发.\hyperlink{fusillade}{\textasciicircum}} of bullets left the floor of the
main hall quickly littered with bodies and pools of blood. At the Leopold Cafe, a
chic\index{chic}\hypertarget{chic}{}\footnote{\textbf{chic}:$[$\esh i(\textlengthmark )k$]$.
\textit{n adj}. (esp of fashionable clothes, women, etc) stylish or elegant.$[$法口$]$(美术上的)独创
风格; 别致, 潇洒, 漂亮; (衣服或穿衣服的人)高雅的风格或款式.\hyperlink{chic}{\textasciicircum}}
restaurant popular with Westerners and wealthy Indians and famous for sidewalk dining, a cluster of
gunmen mowed down diners.

At the opulent Taj Mahal and Oberoi hotels, the assailants poured heavy fire into restaurant goers
on the ground floors, then moved upstairs to round up guests as hostages. And at a range of other
locations, from a movie theater to a hospital to a police station, the attackers opened fire
remorselessly on anyone in their path, frequently throwing grenades as well.

With proximity\index{proximity}\hypertarget{proximity}{}\footnote{\textbf{proximity}:$[$pr\openo
k\textprimstress simiti$]$. \textit{n}. nearness in space or time.接
近.\hyperlink{proximity}{\textasciicircum}} to Pakistan and visibility as the hub of India's
financial sector, Mumbai has suffered many terrorist attacks over the years. But the killings this
week, played out so publicly and prolonged over so many days, have shaken many as never before.

``In 51 years, I have never seen this kind of thing,'' said Dev B. Gohil, a tailor and lifelong
Mumbai resident. ``We're scared for ourselves and for our families.''

One reason for the nervousness is that it seems likely that not nearly all the terrorists were
caught or killed -- and so far the whereabouts of the rest are a mystery. At least eight were
confirmed dead on Friday, although more might be found as soldiers and the police combed through the
two hotels. Security officials declared that they had taken control of the Taj Mahal Palace \& Tower
on Saturday morning, killing three militants.

Estimates of the number of attackers have ranged from 20 to 40, with the number depending to a
considerable extent on the number of boats involved. As security forces seek to reconstruct how the
gunmen managed to inflict so much
carnage\index{carnage}\hypertarget{carnage}{}\footnote{\textbf{carnage}:$[$\textprimstress
k\vara\textlengthmark nid\yogh$]$. \textit{n}. extensive slaughter, esp of human beings in battle.大
屠杀, 残杀.\hyperlink{carnage}{\textasciicircum}} so quickly, they have been turning their attention
to how so many assailants managed to reach the heart of Mumbai undetected and with such a large
collection of guns, ammunition and explosives.

Fishermen here said that the police removed and impounded the boat that came ashore here at the
Fishermen's Colony pier where Mr. Dhanur lives. Various local news media have reported the
impoundment of at least one -- and as many as four -- other boats at other nearby locations on the
coast of South Mumbai, one of the city's oldest neighborhoods.

The Times of India newspaper reported on Friday that the Coast Guard had found an Indian fishing
trawler, the Kuber, that disappeared on Nov. 14. The Kuber may have been used as a so-called mother
ship to transport inflatable rafts within range of South Mumbai, much as pirate mother ships from
Somalia, across the Arabian Sea from Mumbai, have used smaller boats to hijack tankers and other
vessels in recent weeks.

The Kuber's 30-year-old captain was found dead on the boat, and his four crew members were missing,
The Times of India said.

Not all of the terrorists may have entered Mumbai on the night of the attack. Local news media,
citing anonymous law enforcement officials, are reporting that one captured terrorist has said
during interrogation that some members of his group had stayed in hotels for four days before the
attacks to prepare for them and even to store
ammunition\index{ammunition}\hypertarget{ammunition}{}\footnote{\textbf{ammunition}:$[$\textsecstress\ae
mju\textprimstress ni\esh\schwa n$]$. \textit{n}. When the soldiers had used up all their
ammunition, they went on fighting with their swords.弹药,军
火.\hyperlink{ammunition}{\textasciicircum}} in the rooms.

When the terrorists landed in front of Mr. Dhanur's boat, they were just three blocks straight down
a narrow lane from Nariman House, a five-story building housing a Jewish center run by a young
rabbi, Gavriel Holtzberg, and his wife, Rivka, who had moved from New York.

But the attack does not appear to have started there. According to India's Home Ministry, the first
shots were fired at the train station, and soon after that at the Leopold Cafe.

Popular with tourists, the cafe is about eight blocks from the dock where Mr. Dhanur was surprised
by the arrival of the inflatable raft. It is just a block behind a top target for the terrorists:
the luxurious Taj Hotel, Mumbai's most famous place for maharajahs and wealthy businesspeople to
stay.

A large red sign over the two double-width entrances to the Leopold Cafe still boasts that the
restaurant has been in business ``since 1871.'' But the steel shutters of the Leopold were pulled
down over the entrances on Friday afternoon, sealing the site of a deadly assault.

The attackers stood at the entrances and raked the diners with heavy fire from assault rifles. The
power of the rounds is still visible from three shots that missed the diners. They struck the thick
concrete columns on either side of an entrance and penetrated more than an inch deep, leaving red
stains.

Through a gap at the top of the shutters, the darkened restaurant could still be seen. Half-eaten
meals still sat on tables and napkins lay on tables and chairs, as though the diners had disappeared
suddenly into thin air.

Few signs of the fallen remained visible on Friday afternoon, and no official tally of casualties
from this attack has been released.

After the train station and the Leopold Cafe, at least some of the terrorists attacked and occupied
three buildings from which the police would find it very difficult to dislodge them: the two hotels
and Nariman House.

At the hotels, the attackers managed to hide in a maze of rooms, especially at the Taj, and so
avoided easy capture. The smaller Oberoi proved more difficult for the assailants, and they were
defeated there first, with the police leading out dozens of hostages at midday on Friday.

Nariman House took a full day on Friday for the army to capture, as the attackers holed themselves
up in the middle floors of the building, where they could not easily be reached from the ground or
from above. Only on Friday evening were the assailants finally overwhelmed.

The most complex building, the Taj Hotel, with its many passageways, took the longest to clear. The
National Security Guard announced Saturday morning that it believed the last three gunmen had been
killed, and declared the siege over.

\section{A Microsoft Veteran Embraces Open Source}

Keith Curtis has just written a book about the future of software.

That in itself isn't unique. More unusual is that Mr.~Curtis, an 11-year
veteran\index{veteran}\hypertarget{veteran}{}\footnote{\textbf{veteran}:$[$\textprimstress vet\schwa r\schwa n$]$.
  \textit{n}. a person or thing that has given long service in some capacity.熟手, 老手; 富有经验的人.战斗经验丰富的军人, 老
  练的兵.\hyperlink{veteran}{\textasciicircum}} of Microsoft, the world's largest software company, believes deeply that
open source is the future of software.

Microsoft, of course, has long been the
archenemy\index{archenemy}\hypertarget{archenemy}{}\footnote{\textbf{archenemy}:$[$\textprimstress\vara r\textprimstress t\esh\epsi n\schwa
  mi$]$. \textit{n}. A principal enemy. Specifically, Satan, the grand adversary of
  mankind.\hyperlink{archenemy}{\textasciicircum}} of the open source community, which is built on the notion of freely
sharing intellectual property for the good of the community. I.B.M. and Sun Microsystems have embraced the open source
cause, as have other technology giants. Even Apple's OS X operating system is at its core open source -- an Apple executive
has said that more than 50 percent of the lines of code in OS X come from the open source Berkeley Software Distribution and
related projects.

In contrast, Microsoft has made only grudging\index{grudge}\hypertarget{grudge}{}\footnote{\textbf{grudge}:$[$gr\pwedge d\yogh$]$.
  \textit{n}. 怨恨;妒忌\hyperlink{grudge}{\textasciicircum}} accommodations to the open source movement, offering some of
its source code to programmers who use its technology while valiantly arguing that for-pay software is less expensive than
free software when you consider the bigger picture.

Mr.~Curtis, who joined Microsoft in 1993 and left in 2004, begs to differ. And while he says he holds no grudge against his
former employer, in the long run, the company ``is toast.''

His book, ``After the Software Wars,'' was published last month by Lulu.com, a Web-based publishing service that makes it
possible for Mr.~Curtis to give the first 1,000 readers the option of downloading a free version of the book (590 people
have already taken advantage of the offer) or purchasing a paperback version for \$19.97 (so far he has sold 11 copies, five
of which were purchased by his mom).

He takes a programmer's approach in ``Software Wars,'' attempting to systematically build a case that software can help pave
the way for a 21st-century renaissance in many fields ranging from artificial intelligence (cars that drive themselves) to
the human journey into space (space elevators). For Mr.~Curtis, the strength of open source software, and why it's the
future, is all about leveraging our collective intelligence.

He argues that, in the same collaborative fashion that the Linux operating system has been built and improved, many things
that are now science-fiction goals -- such as those cars that drive themselves -- can be achieved.

``The key to faster technological progress is making software free,'' he writes. ``The difference between free, and non-free
or proprietary software, is similar to the divide between science and
alchemy\index{alchemy}\hypertarget{alchemy}{}\footnote{\textbf{alchemy}:$[$\textprimstress\ae lkimi$]$. \textit{n}. the pseudoscientific
  predecessor of chemistry that sought a method of transmuting base metals into gold, an elixir to prolong life
  indefinitely, a panacea or universal remedy, and an alkahest or universal solvent. 炼丹术,点金
  术.\hyperlink{alchemy}{\textasciicircum}}. Before science, there was alchemy, where people guarded their ideas because
they wanted to corner the market on the mechanisms used to convert lead into gold.''

He notes that there is an important parallel to the end of the Dark Ages, which came when society began to freely share
advancements in math and science.

None of his arguments are new. What is intriguing is where Mr.~Curtis comes from.

He recalls meeting Microsoft co-founder Bill Gates for the first time at the software magnate's Lake Washington home. Mr.
Curtis was a 20-year-old college intern at the time, and he had planned for the meeting long in advance. He approached Mr.
Gates (who was holding a Coke and had a small ketchup stain on his shirt) with several
arcane\index{arcane}\hypertarget{arcane}{}\footnote{\textbf{arcane}:$[$\vara\textlengthmark\textprimstress kein$]$. \textit{adj}.
  requiring secret knowledge to be understood; mysterious; esoteric.秘密的, 神秘的; 幽晦
  的.\hyperlink{arcane}{\textasciicircum}} questions. Mr.~Gates's answers convinced Mr.~Curtis that Microsoft would be one
of the best places in the world to learn the craft of computer programming. While there, he worked on the company's database
products, its Windows operating sytem, Office, MSN and in research.

Ultimately, he left because he was bored: ``The amount I learned in my 11th year was much less than what I had learned in my
first year, and the stock had become stagnant\index{stagnant}\hypertarget{stagnant}{}\footnote{\textbf{stagnant}:$[$\textprimstress st\ae
  n\schwa nt$]$. \textit{adj}. (of water, etc) standing still; without flow or current. 停滞的, 污浊的, 迟钝的,象死水一潭
  的, 毫无生气的;不景气的.\hyperlink{stagnant}{\textasciicircum}}.''

While he was at Microsoft, he had learned little about the open source world. In cafeteria conversation, he had usually
taken the position that proprietary software would always maintain a technology lead over open source. He recalled a friend
who had tried to install Linux in 1999, but gave up because the backspace key didn't work.

After he left Microsoft, he installed a copy of the Linux operating system on a lark. His world was turned upside down. He
spent three years exploring the open source world -- reading, attending conferences, looking at source code and talking to
the rank-and-file members of the open source community.

Mr.~Curtis says he's not bitter about his time at Microsoft, but the world has moved on. ``I loved working there, learned an
enormous amount, made a few shekels, and enjoyed the privilege of working alongside many brilliant minds. Like many things
in life, it was fun while it lasted.''

\section{For Heroes of Mumbai, Terror Was a Call to Action}
MUMBAI, India -- On any ordinary day, Vishnu Datta Ram Zende used the public-address system at Mumbai's largest railway
station to direct busy hordes\index{horde}\hypertarget{horde}{}\footnote{\textbf{horde}:$[$h\openo\textlengthmark d$]$. \textit{n}. 人群,
  群\hyperlink{horde}{\textasciicircum}} of travelers to their trains.

But last Wednesday just before 10 p.m., when he heard a loud explosion and saw people running across the platform, he
gripped his microphone and calmly directed a panicked crowd toward the safest exit. The station, Victoria Terminus, it
turned out, was suddenly under attack, the beginning of a three-day siege by a handful of young, heavily armed gunmen.

``Walk to the back and leave the station through Gate No. 1,'' he
chanted\index{chant}\hypertarget{chant}{}\footnote{\textbf{chant}:$[$t\esh\vara\textlengthmark nt$]$. \textit{n vt vi}. a simple song or
  melody\hyperlink{chant}{\textasciicircum}} alternately in Hindi and Marathi, barely stopping to take a breath until the
platform was cleared. No sooner, gunmen located his announcement booth and fired, puncturing one of the windows. Mr.~Zende
was not hurt.

Overnight, Mr.~Zende became one of Mumbai's new heroes, their humanity all the more striking in the face of the inhumanity
of the gunmen. As the city faced one of the most horrific terrorist attacks in the nation's history, many ordinary citizens
like Mr.~Zende, 37, displayed extraordinary grace.

Many times, they did so at considerable personal risk, performing acts of heroism that were not part of their job
descriptions. Without their quick thinking and common sense, the toll of the attacks would most likely have been even
greater than the 173 confirmed dead on Monday.

Not far from the train station, as the same network of gunmen stormed the Taj Mahal Palace \& Tower Hotel, a sous chef named
Nitin Minocha and his co-workers shepherded more than 200 restaurant diners into a warren of private club rooms called The
Chambers.

For the rest of the night they prepared snacks\index{snack}\hypertarget{snack}{}\footnote{\textbf{snack}:$[$sn\ae k$]$. \textit{n}. a
  light quick meal eaten between or in place of main meals.快餐, 小吃.\hyperlink{snack}{\textasciicircum}}, served soda,
fetched cigarettes and then, when told it was safe, tried to escort the diners out through the back. They wanted to make
sure their guests, many of them Mumbai's super-elite, were as comfortable as possible.

``The only thing was to protect the guests,'' said the executive chef, Hemant Oberoi. ``I think my team did a wonderful job
in doing that. We lost some lives in doing that.''

During the attacks, six employees from the kitchen staff were slain\index{slay}\hypertarget{slay}{}\footnote{\textbf{slay}:$[$slei$]$. \textit{vt}. to kill, esp violently.杀害, 毁灭.\hyperlink{slay}{\textasciicircum}}. Another hotel employee, a maintenance worker on night
duty, was shot in the abdomen and remained in critical condition on Monday.

Mr.~Minocha, 34, caught two bullets in the left arm. It felt numb.

He could see that the bone had been shattered. He panicked.

``I'm a chef,'' he told himself. ``I cook with both hands.''

Even after an aborted evacuation bid, hotel workers helped get water for their guests and held up bedsheets to create
makeshift urinals. Next to the Nariman House, the headquarters of a Jewish religious organization, where gunmen took
hostages, neighbors helped neighbors evacuate to safety.

At another hotel, the Oberoi, staff members ushered restaurant diners into the kitchen and out the door; at that hotel, 10
employees were among the dead.

At Victoria Terminus, also known as Chhatrapati Shivaji Terminus, Mr.~Zende's calls prevented many commuters from walking
into the path of two gunmen. ``It occurred to me, I should prevent people from going to that side,'' he said.

The attackers had already shot up the other wing of the 130-year-old railway station,
littering\index{litter}\hypertarget{litter}{}\footnote{\textbf{litter}:$[$\textprimstress lit\schwa$]$. \textit{n vt}. small refuse or
  waste materials carelessly dropped, esp in public places. 担架.(供动物睡眠用的)稻草, 树叶, 干草.$[$美$]$在公共场所抛弃垃圾
  等\hyperlink{litter}{\textasciicircum}} it with dead bodies, puncturing windows with bullet holes.

In choosing their targets, the gunmen spared neither rich nor poor, neither Westerners nor Indians.

At the Taj, for instance, Mr.~Minocha was on duty at the Golden Dragon restaurant when gunmen stormed the hotel lobby. He
cracked open the door, saw the commotion and promptly closed it. He and his fellow workers escorted diners at his restaurant
to the city's most expensive Japanese restaurant, and finally up to The Chambers, where guests were invited to sit and wait
it out.

``They were doing everything they could,'' said Bhisham Mansukhani, who had been attending a friend's wedding reception that
night, before he was shepherded into The Chambers.

For the next several hours, the staff tried to keep everyone calm and well-fed. At one point, Mr.~Minocha recalled Monday
from his hospital bed, he had seen the red dome of the hotel on fire.

Well before dawn, security officers instructed that guests leave in groups of four. The hotel staff lined up, as though in a
chain. Some people got out. Others did not. Bullets suddenly came in a burst. That is when Mr.~Minocha was hit twice in the
forearm.

The gunfire led to a near stampede. Mr.~Minocha made it outside, screaming for help. Those who were still inside made a
U-turn to The Chambers, which is when a maintenance worker named Rajan Kamble was shot in the back.

The bullet went straight through his abdomen, perforating his intestines, which a couple who had been dining at the
restaurant, Prashant and Tilu Mangeshikar, both doctors, tried to push back into place with some bandages and bedsheets.

Prashant Mangeshikar said that even when they were trapped inside a room in The Chambers, the young hotel staff kept
unusually calm. ``Everything was looking like a holy mess,'' he recalled. ``The majority was between 20 and 25. Nobody lost
their cool.''

At Victoria Terminus, the gunmen acted with a cool precision.

They first struck the long-distance section of the Victoria Terminus, spraying the large waiting hall with gunfire. Those
waiting were about to board the slow, crowded, poor-man's train to Varanasi, scheduled to depart at 11:55 pm, one of many
that ferry migrant workers between India's hinterland and this, its dream city.

Satya Sheel Mishra, who runs a second-floor restaurant called Re-Fresh Food Plaza, saw the two gunmen take their positions
and fire. Seven bullets pierced his glass windows. Crouching on the ground, he saw the men shoot indiscriminately and then
march toward the other side of the station, where Mr.~Zende made announcements for the commuter trains to the suburbs.

Mr.~Zende saw the gunmen walk in front of his window. Then he crouched on the ground and heard them shoot. One bullet came
through a window. Above his microphone, the Hindu elephant-god Ganesh, believed to be the remover of obstacles, sat in a
blue box with twinkling red lights around him. Mr.~Zende called his wife. ``I am in the office. I'm safe. Don't worry.''

Mr.~Zende joined the railways at the age of 19, when his father, a railway guard, died. With a 10th-grade education, Mr.
Zende began at the bottom of the ladder, working himself up to the announcement booth. Now, he commutes an hour and a half
each way from a working-class corner on the city's northern edges, naturally on the railways. He makes little more than
\$300 a month.

On Monday, a woman strode up the steep, narrow steps to his announcement booth and burst out her praise: ``Mr.~Zende, you
have done such good work. We need more people like you.''

She declined to give her name. She said she was a retired scientist who had stepped out of her home for the first time since
the attacks began. She railed against politicians.

Then she signed off. ``Jai Hind,'' she said, or ``long live India.''

Mr.~Zende quietly replied, ``Jai Hind.''

\section{Treasury's Lead Role in China in Flux}

WASHINGTON -- When Treasury Secretary Henry M. Paulson Jr. leaves office next month, Washington will lose its No. 1 China
hand. Mr.~Paulson, who spent years cultivating Chinese leaders as a Wall Street banker, has spearheaded American policy
toward Beijing since 2006.

That raises some big questions, including who will pick up Mr.~Paulson's
baton\index{baton}\hypertarget{baton}{}\footnote{\textbf{baton}:$[$\textprimstress b\ae t\schwa n$]$. \textit{n}. a thin stick used by
  the conductor of an orchestra, choir, etc, to indicate rhythm or expression.指挥棒.\hyperlink{baton}{\textasciicircum}} in
the Obama administration, and whether the Treasury Department will continue to be the lead agency in steering a relationship
increasingly defined by China's yawning trade gap with the United States.

On Tuesday, Mr.~Paulson will lead a delegation of cabinet officials to China to hold economic talks, the fifth and, for him,
final round of semiannual meetings known as the ``strategic economic dialogue.''

A range of issues are likely to be on the table, including energy, the environment and the economic crisis. Experts said the
global downturn could fray\index{fray}\hypertarget{fray}{}\footnote{\textbf{fray}:$[$frei$]$. \textit{vt vi}. a noisy quarrel;to wear or
  cause to wear away into tatters or loose threads, esp at an edge or end;擦, 磨损(衣[袖]边等); 擦破(绳 子的末端)以致纤维散
  开.(使关系、神经等)紧张.\hyperlink{fray}{\textasciicircum}} American-Chinese ties, as China promotes exports to fuel its
rapidly slowing economy at the same time that the United States is limping.

In an interview, Mr.~Paulson said he worried that the crisis could set off a wave of protectionism on both sides of the
Pacific. He said he planned to press the Chinese on recent measures like their increased tax rebates for exporters, which
make Chinese goods cheaper in Europe and the United States.

``Hank Paulson has a tremendous fervor\index{fervor}\hypertarget{fervor}{}\footnote{\textbf{fervor}:$[$\textprimstress
  f\schwa\textlengthmark v\schwa$]$. \textit{n}. 热情\hyperlink{fervor}{\textasciicircum}} for these issues that I don't
know if Tim Geithner has or not,'' said Kenneth Lieberthal, a China specialist now at the Brookings Institution, referring
to President-elect Barack Obama's choice for Treasury secretary, Timothy F. Geithner.

``One possibility is that the strategic economic dialogue continues, but moves to another venue in the government,'' said
Mr.~Lieberthal, who worked on China policy in the Clinton administration.

As possible coordinators of China policy, he mentioned Lawrence H. Summers, newly named chairman of the National Economic
Council, or Vice President-elect Joseph R. Biden Jr. Then there is Senator Hillary Rodham Clinton, Mr.~Obama's choice for
secretary of state.

What none of these people has is the lengthy China experience that Mr.~Paulson brought with him from Goldman Sachs. Mr.
Geithner comes closest, having studied in China and served as a diplomat in Tokyo, as well as under secretary of the
Treasury for international affairs.

A spokeswoman for Mr.~Obama, Brooke Anderson, declined to comment on the president-elect's plans for China policy, except to
point to a recent essay by Mr.~Obama, in which he called for ``fresh thinking and a change from the U.S. policy approach of
the past eight years.''

China could pose a thorny\index{thorny}\hypertarget{thorny}{}\footnote{\textbf{thorny}:$[$\textprimstress\texttheta\openo\textlengthmark
  ni$]$. \textit{adj}. bearing or covered with thorns.多刺的, 有棘刺的; 象刺的; 刺丛繁茂
  的.\hyperlink{thorny}{\textasciicircum}} challenge to Mr.~Obama, experts said, because its trade surplus with the United
States -- already a record, at \$35.2 billion, in October -- is likely to swell further in the next few months.

That is partly because of the tax rebates. The rebates apply to more than half the Chinese goods covered by trade tariffs,
and while they do not violate World Trade Organization provisions, experts view them as a form of protectionism.

``We've always thought China's export rebates are a bigger driver of their trade relationship than the exchange rate,'' said
John Frisbie, the president of the U.S.-China Business Council.

With a recession biting in the United States, experts say, these new Chinese measures could
reignite\index{reignite}\hypertarget{reignite}{}\footnote{\textbf{reignite}:$[$\textsecstress ri\textlengthmark i\textprimstress nait$]$.
  \textit{vt}. to catch fire or cause to catch fire again. 把...再点火, 再点燃.\hyperlink{reignite}{\textasciicircum}} calls
in Congress to punish China over its trade practices.

``If we're heading toward 9 percent or 10 percent unemployment, and people look around and see China running larger and
larger surpluses, they're going to say, 'What's going on here?' '' said Nicholas Lardy, an expert on the Chinese economy at
the Peterson Institute for International Economics.

In June, with growth slowing, China also ended a brief experiment in letting its currency rise in value against the dollar.

Before that, the currency had risen 20 percent against the dollar in the last two years, as the Chinese central bank stopped
intervening in the currency market.

With Chinese factories shutting down, and the government worried about rising unemployment and social unrest, experts said
it was unrealistic to expect China to show flexibility on its currency now. Besides, some noted, China's currency, by
maintaining its peg to the dollar, has risen in relation to the currencies of other trading partners because the financial
crisis has driven up the dollar.

Mr.~Paulson said he was disappointed that the United States had not been able to push China further on its currency. But he
said it was only the strategic economic dialogue that prevented Congress from passing legislation that would have deepened
the tensions between the countries.

``When we started this, I was told we weren't going to be able to avoid currency legislation in Congress,'' he said. ``We
never got as much as we would have liked'' from the Chinese, he added, ``but people recognize we got a lot more than we
would have without the dialogue.''

Mr.~Paulson said the dialogue had also been useful on difficult issues like product and food safety, as well as the
environment. China had rolled back some energy subsidies after the last meeting in June.

Mr.~Paulson demurred\index{demur}\hypertarget{demur}{}\footnote{\textbf{demur}:$[$di\textprimstress m\schwa\textlengthmark$]$.
  \textit{vi}. to raise objections or show reluctance; object.踌躇; 迟疑; 犹豫.$[$律$]$抗
  辩\hyperlink{demur}{\textasciicircum}} on the question of how the Obama administration should handle China relations,
though he noted that Mr.~Geithner, whom he knows well from the government's rescue effort, speaks Mandarin.

For his part, Mr.~Paulson said he expected China to play a part in his life after the Treasury, though he draws the line at
learning Mandarin. ``I've got a very poor ear for languages,'' he said.

\section{With Saturn, G.M. Failed a Makeover}
General Motors has promised Congress that it can recreate itself as a different kind of car company -- smaller, with a more
cooperative relationship with its union, and a lineup of fuel-efficient cars to compete with the best of the foreign brands.

At least G.M. knows how difficult the challenge will be.

A quarter-century ago, G.M. started Project Saturn\index{Saturn}\hypertarget{Saturn}{}\footnote{\textbf{Saturn}:$[$\textprimstress s\ae
  t\schwa (\textlengthmark )n$]$. \textit{n}. one of the giant planets, the sixth planet from the sun, around which revolve
  planar concentric rings ( Saturn's rings) consisting of small frozen particles. The planet has at least 30 satellites.
  Mean distance from sun: 1425 million km; period of revolution around sun: 29.41 years; period of axial rotation: 10.23
  hours; equatorial diameter and mass: 9.26 and 95.3 times that of the earth, respectively.土
  星.\hyperlink{Saturn}{\textasciicircum}} with the same goals. And it worked, for a time. Saturn owners, including many who
traded in their Hondas and Toyotas to own the first models in 1990, became cheerleaders for the division's customer-friendly
approach, while the United Automobile Workers union gave up many of its traditional restrictions to help Saturn succeed.

The brand became a media darling, and was featured on the cover of Time. ``Can America still compete?'' said the headline.
``With its new Saturn, G.M. bets the answer is yes.''

But Saturn quickly started losing its shine. G.M. executives cut spending, and shoppers flocked to S.U.V.'s. Eventually,
many workers resisted the new management style. Now the brand that was once a symbol of G.M.'s future will have a bit part,
at most.

G.M. said Tuesday that it was ``exploring alternatives'' for Saturn, which come down to selling it or relegating it to a
smaller role in G.M.'s lineup.

G.M. once hoped it would sell 500,000 Saturns a year. But sales peaked at 286,000 in 1994, according to
Motorintelligence.com. Unless Saturn sales rise sharply in December, this year the division will sell fewer than 200,000
vehicles, for the first time since 1992.

Despite the steady decline, Saturn executives can point to bright spots.

Saturn ranks No. 13 in resale value, measured over the last five years, among all automotive brands tracked by Kelley Blue
Book -- the second best showing among G.M. brands behind Pontiac at No. 11.

And the small Saturn Aura, part of a refreshed lineup based on vehicles from G.M.'s European division, ``might be the best
undiscovered car in America,'' said Jack R. Nerad, the executive editorial director at Kelley. Aura sales are up 2.8 percent
this year, while Saturn's sales over all are down 21 percent compared with 2007.

Saturns no longer roll off the assembly line at the plant in Spring Hill, Tenn., that was originally built just for Saturn
and was featured in the company's quirky ads. That factory is now used to build the Chevrolet Traverse, a crossover vehicle.

To some buyers, Saturn's marketing message still
resonates\index{resonate}\hypertarget{resonate}{}\footnote{\textbf{resonate}:$[$\textprimstress rez\schwa neit$]$. \textit{vi}. to resound
  or cause to resound; reverberate.共鸣;回响,反响.\hyperlink{resonate}{\textasciicircum}}.

Joseph Salzburg, a graphic artist from Richmond, Ill., said he purchased a 2007 Saturn Sky sports car last year because he
wanted to support the division.

``I bought it because of the reputation of the company and because I only buy American cars now,'' Mr.~Salzburg said.

True believers in Saturn insist the concept behind the division, which stressed respect, teamwork and communication from the
factory floor to the auto showroom, could have kept G.M. from losing nearly half the market share it held when the first
Saturns went on sale 18 years ago.

``I'm absolutely convinced that the Saturn way could have worked,'' said Michael Bennett, the original U.A.W. leader at
Saturn. ``But what we had was never embraced or adopted.''

Mr.~Bennett, like many others, can point fingers to explain why Saturn fell short of its promise.

Mr.~Bennett blamed a lack of interest by G.M. executives who succeeded Roger Smith, who as chief executive in the 1980s
committed \$5 billion to begin Saturn.

But those who followed him -- including John F. Smith Jr., who became chief executive in 1992, and G.M.'s current chief
executive, Rick Wagoner, who ran its North American operations in the 1990s -- had bigger worries.

They had to lead the company through the financial turbulence at G.M. in the early 1990s. And with managers at G.M.'s other,
older brands begging for investment, G.M. executives declared Saturn would have to prove it deserved more support, even
though its small cars were accomplishing their main goal of winning buyers from imports.

Despite G.M.'s pledge that Saturn would be run as a separate company, with its own car development and purchasing
operations, it was folded into G.M.'s small-car operations in 1994, and its lineup did not receive any new models for the
next five years.

While executives were souring on the concept, U.A.W. officials questioned the consensus approach at the Spring Hill plant,
where G.M. set up a consulting arm that taught other companies how to adopt Saturn principles with their employees.

Fearful that the division might not survive, Mr.~Bennett devised a proposal to spin off Saturn as a separate business, but
was told G.M.'s board would not consider the plan.

In 1998, Mr.~Bennett was voted out of office at the U.A.W., and workers eventually chose to abandon their separate contract.

Since then, Saturn's lineup has shifted from small import fighters to a more conventional G.M. division, with cars from
G.M.'s Opel division, crossovers and the Vue, a small sport utility.

But the Vue, one of the few vehicles that G.M. sells in a hybrid-electric version, and other models have not
stemmed\index{stem}\hypertarget{stem}{}\footnote{\textbf{stem}:$[$stem$]$. \textit{vi}.
  $[$美$]$起源, 发生\hyperlink{stem}{\textasciicircum}} Saturn's decline in sales.

The idea that Saturn may disappear is ``hard news to absorb,'' said Haywood B. Hyman Jr., a founding Saturn dealer.

Mr.~Hyman, who put up \$1 million for his original Saturn franchise, built a series of showrooms in southern Virginia just
for Saturns. He now operates in only two locations, after closing one of his Saturn dealerships last month.

``I would hate to see it go,'' he said. ``I hope it can survive.''



\section{Microsoft Names New Chief for Internet Unit}

SAN FRANCISCO -- Microsoft named Qi Lu, a former Yahoo executive, to run its struggling Internet unit on Thursday. Mr.~Lu
will fill an important position that had been vacant since the departure in July of Kevin Johnson, who played a central role
in Microsoft's failed attempt to buy Yahoo earlier this year.

In selecting Mr.~Lu, who will become president of the money-losing online services group in January, Microsoft chose an
executive with deep technical knowledge over others with more advertising and media experience. He will be leading the
company's challenge to Google, which dominates the search and online advertising business. Despite heavy investment,
Microsoft has had trouble getting traction in those fields.

``Microsoft is trying to emulate Google in naming a technologist to head the online unit,'' said Youssef Squali, an analyst
with Jefferies \& Company.

Microsoft also said that Brian McAndrews, a senior executive in the online unit, had decided to leave. Mr.~McAndrews, the
former chief executive of aQuantive, an advertising technology company that Microsoft acquired for \$6 billion last year,
was one of a handful of internal candidates that Microsoft considered for the position.

Mr.~Lu, a computer scientist with a Ph.D. and a former I.B.M. researcher who holds 20 patents, spent 10 years at Yahoo. He
most recently was an executive vice president overseeing engineering for two important areas at Yahoo: online search and
advertising technology.

``Dr.~Lu's deep technical expertise, leadership capabilities and hard-working mentality are well-known in the technology
industry,'' Steve Ballmer, Microsoft's chief executive, said in a press release. Microsoft declined to make an executive
available to discuss the appointment of Mr.~Lu, who left Yahoo in August.

Mr.~Ballmer reiterated recently that Microsoft is no longer interested in acquiring Yahoo but said that it remained open to
a search advertising partnership between the two companies. He also said that there were no active talks between the two
companies.

On Thursday, a Microsoft spokesman, Frank Shaw, said: ``There is nothing new with regard to Yahoo.''

Mr.~Squali said that if Microsoft and Yahoo eventually strike a search partnership, Mr.~Lu's intimate knowledge of Yahoo's
operations could prove important to Microsoft.

``It will make the prospects of any integration that much easier,'' Mr.~Squali said. But he added that, short of such a
deal, Microsoft would continue to struggle to build a sizeable audience for its search service.

``I don't think it changes the landscape all that much for Microsoft,'' Mr.~Squali said, referring to Mr.~Lu's appointment.

Mr.~Lu left Yahoo as part of a continuing exodus of executives that has depleted its management ranks. Many of the
departures were prompted by Yahoo's struggles to turn around its own business and frustration with the slow pace of change.
Jerry Yang, the chief executive, announced last month that he would step down as soon as the board appoints a replacement.

Last month, Microsoft hired another Yahoo search executive, Sean Suchter, to run its Silicon Valley search technology group.

Microsoft said Mr.~McAndrews had agreed to remain in a ``consultative capacity'' to Mr.~Lu and Mr.~Ballmer for the next
several months. Scott Howe will now oversee Microsoft's advertiser and publisher solutions business, previously headed by
Mr.~McAndrews.

Mr.~Johnson, who along with Mr.~Ballmer led Microsoft's failed bid to buy Yahoo, was also in charge of Microsoft's Windows
operating system business. He left Microsoft in July to become chief executive of the networking technology maker Juniper
Networks.

\section{Who Needs a TV? I'm Watching on a Laptop}

I have been compared to many things in my life; never, though, to Sasquatch.

But that is what Alan Wurtzel, president of research at NBC Universal, suggested when I told him I had gotten rid of my
television set last year and started watching ``30 Rock'' and ``CSI'' on my laptop instead. ``I hear about people like
you,'' he said, a hint of skepticism in his voice. ``But the notion that people have forsaken watching cable and network
television is an urban myth.''

Then he hissed what sounded vaguely like an insult.

``You probably read.''

Yes, I do enjoy The New Yorker or a John Irving novel from time to time. But just because I don't have a television set
doesn't mean I don't crave ``Gossip Girl'' and obsess over whether Serena will (finally!) get back together with Dan. It's
just that I don't have a large television in my living room and a monthly payment to make to my cable company. I don't need
one: the major networks and many other broadcasters have made it easy to find their shows free online.

Most Americans still watch shows primarily on their televisions. I'll concede that point to Mr.~Wurtzel. But there is much
to suggest that watching shows online is more than just a passing fancy. The Internet has proved to be an excellent
promotional vehicle. NBC says 7 out of 10 viewers were spurred to watch some shows on television only after sampling them
first online. At ABC, 8 percent of viewers they track -- or about one out of every 12 people -- watch network shows solely
online.

Consider the following. My friend Louise uses a projector hooked up to her laptop to watch ``Lost'' on a white wall in her
living room. My 24-year-old niece never owned a television set until I gave her mine. Now she uses it for DVDs and watches
``America's Next Top Model'' online. And it's not just for the cosmotini set. A 40-something executive I know watched the
last presidential debate between John McCain and Barack Obama on his home computer.

Of course, my house wasn't always television free. When I lived in Los Angeles, I had cable but was rarely home to catch my
favorite shows. I paid extra for HBO but only to watch ``Entourage.'' Unlike other friends, I never subscribed to TiVo,
knowing I would feel guilty if I let shows stack up.

The funny thing is, despite not having a television, I actually watch more network programming than I did when I had cable.
The difference is that I am more selective. No more flipping channels just to see what's on, the television equivalent of a
one-night stand. Instead I am in a committed relationship.

For network television shows the best places to start are their home Web sites, including ABC.com, NBC.com, CBS.com and
Fox.com, where shows are posted usually within 24 hours of being shown on television. ABC.com, in my experience, is one of
the simplest to use. It was a pioneer in putting shows online, although stingy in the early days because it didn't want to
share its toys with other sites.

ABC.com also demands viewers be engaged, requiring them to click a button to continue watching the program after an ad ends.
It is a deceptively smart strategy: I was forced to sit through a 30-second commercial -- and click -- to find out whether
Mike Delfino actually died from smoke inhalation on ``Desperate Housewives.'' It's only 30 seconds I figured (and I can
watch the countdown) which kept me in my seat.

To save time, I usually stay away from sites like Veoh.com, Joost.com, Bebo.com or AOL. Quite simply, there is little there
to entice\index{entice}\hypertarget{entice}{}\footnote{\textbf{entice}:$[$in\textprimstress tais$]$. \textit{vt}. to attract or draw
  towards oneself by exciting hope or desire; tempt; allure.引诱, 怂恿.\hyperlink{entice}{\textasciicircum}} me. Each has a
similar syndicate\index{syndicate}\hypertarget{syndicate}{}\footnote{\textbf{syndicate}:$[$\textprimstress sindikit$]$. \textit{n}. an
  association of business enterprises or individuals organized to undertake a joint project requiring considerable capital.大
  学委员会的职务; 理事会; (特指剑桥大学的)大学管理会特别委员会.辛迪加, 企业联合组织.\hyperlink{syndicate}{\textasciicircum}}
of already-released movies and television shows, and can be confusing if you are not sure what to look for. The exception is
Sling.com, which offers much of the same content, but with a more user-friendly setup.

Of course there is a plethora\index{plethora}\hypertarget{plethora}{}\footnote{\textbf{plethora}:$[$\textprimstress ple\texttheta\schwa
  r\schwa$]$. \textit{n}. superfluity or excess; overabundance.多血(症);节瘤;过剩,剩余.\hyperlink{plethora}{\textasciicircum}}
of sites with pirated content, but I don't go to those because I don't want to get busted.

Recently I was talking with Quincy Smith, the president of CBS Interactive, who wanted me to visit the CBS channel on
YouTube. But it was so cumbersome\index{cumbersome}\hypertarget{cumbersome}{}\footnote{\textbf{cumbersome}:$[$\textprimstress k\pwedge
  mb\schwa s\schwa m$]$. \textit{adj}. awkward because of size, weight, or shape.不方便的, 笨重
  的.\hyperlink{cumbersome}{\textasciicircum}} to find that Mr.~Smith had to guide me on the phone as I sat in front of my
laptop. MGM plans to offer movies there, too, but the list is not comprehensive.

The one standout is Hulu.com, a joint venture of NBC and Fox. It is well organized and simple to use. (Even Mr.~Smith called
it ``the gold standard.'') It not only has current shows like ``The Office,'' ``The Simpsons,'' ``24,'' and ``Heroes,'' but
a trove of classics like the original ``Battlestar Galactica,'' ``Married With Children'' and ``The Mary Tyler Moore Show.''

The site, too, like others, has cable shows including the quirky ``It's Always Sunny in Philadelphia'' and ``The Daily Show
With Jon Stewart.'' Quite honestly, I never watched ``The Daily Show'' when I owned a television; I discovered it on Hulu. I
can almost say the same for ``Saturday Night Live,'' which I gave up watching in the 1990s. During election season, though,
I eagerly checked Hulu for both shows to see what I might have missed.

Of course, it wouldn't be television without a blooper\index{blooper}\hypertarget{blooper}{}\footnote{\textbf{blooper}:$[$\textprimstress
  blu\textlengthmark p\schwa$]$. \textit{n}. a blunder; bloomer; stupid mistake.$[$美俚$]$(在大庭广众面前所出的)大错, 洋相.
  (棒球)仅仅击出内场的飞球.\hyperlink{blooper}{\textasciicircum}} or two. So many online ``Gossip Girl'' fans showed up to
watch last season's shows, they threatened to crash cwtv.com. As a result the CW banned the show online, hoping viewers
instead would watch it on their televisions. Fans protested, though, and the show reappeared online, much to my delight and
that of my 14-year-old neighbor who agrees that Jenny Humphrey's new model friend, Agnes, is a bad influence.

Then there's iTunes. Apple's media store has been selling TV shows for three years now, and buying is easy to do. The
problem I have with iTunes is that you have to pay for the shows in order to watch them. With so many legal ways to get
shows free, there's little incentive for me to pay unless it's something I can't stream, like ``Mad Men'' or ``Entourage.''
And yes, while a series like ``Lost'' may require multiple viewings to fully appreciate them, do I really need to own
episodes of ``Two and a Half Men''?

Movies, too, pose a problem for entertainment companies who might want to put them on their sites. On Hulu and others, there
are a number free -- ``Ordinary People'' and ``Men in Black'' among them -- but none are current.

``That's a whole different business for us,'' said Albert Cheng, a digital media executive at ABC. ``We are still trying to
figure out if there is a movie audience.'' I am a dinosaur in this regard, so buying a \$10 DVD at the Virgin Megastore and
playing it on my computer works fine until downloading or streaming movies becomes easier.

While watching shows online works for me, I know it is not for everyone. Shows don't appear until the next day, a deal
killer for the truly obsessed. And it is hard to find live sports events (or delayed for that matter) online, particularly
if it is a big game.

Besides, movies and sports events have more appeal when viewed on a large screen -- that's what big-screen TV is made for.
No one is going to mistake their 13-inch laptop screen for a 50-inch high-definition plasma. I recently watched David Lean's
eye candy ``Lawrence of Arabia'' on Hulu and ached to experience it on my brother-in-law's home theater in his den.

Speaking of him, I asked him recently if he would ever watch his beloved San Francisco 49ers football team, or any show for
that matter, on a magazine-size laptop. He looked at me,
incredulous\index{incredulous}\hypertarget{incredulous}{}\footnote{\textbf{incredulous}:$[$in\textprimstress kredjul\schwa s$]$. \textit{adj}.
  not prepared or willing to believe (something); unbelieving.\hyperlink{incredulous}{\textasciicircum}}. ``Are you
serious?'' he asked. ``Does anybody really do that?''

Mr.~Wurtzel is probably smiling.
\section{In Washington, Some Optimism About a Big Three Bankruptcy}
IN the days before Lehman Brothers was allowed to fail, Treasury officials made clear that they did not think the investment
bank's collapse would have a major ripple effect.

And in recent weeks, in Congressional hearing rooms and at water coolers across the country, a lot of people have been
saying the same thing about Detroit's beleaguered automakers.

What Lehman's failure shows, supporters of the Big Three bailout contend, is that there can be unanticipated consequences of
allowing a major company to go under, and the full extent of the risks becomes clear only after the fact -- when it can be
too late to contain the fallout.

Over the weekend, Congressional leaders and the Bush administration provisionally agreed to a bailout in which some \$17
billion in taxpayer money would be used to keep General Motors and Chrysler afloat. Ford, meanwhile, says it does not need
immediate federal aid.

But some lawmakers and economists continue to argue that General Motors and Chrysler are too far gone to be saved and that
trying to bail them out amounts to throwing away taxpayer dollars. Moreover, those lawmakers warn that rushing to the rescue
with federal money will reward the automakers for years of poor management and
myopic\index{myopic}\hypertarget{myopic}{}\footnote{\textbf{myopic}:$[$mai\textprimstress\openo pik$]$. \textit{adj}. 近视
  的.\hyperlink{myopic}{\textasciicircum}} decisions, like producing gas guzzlers.

Back in September, Treasury officials similarly argued that bailing out\index{bail out}\hypertarget{bail out}{}\footnote{\textbf{bail
    out}:\textit{vt}. 保释.\hyperlink{bail out}{\textasciicircum}} Lehman would have wrongly rewarded it for its bad
behavior and excessive risk-taking, and thereby would have given the nation's financial sector a green light for future bad
behavior.

Seeing how Lehman's collapse shocked the stock and credit markets, Robert Barbera, chief economist at ITG, an investment
firm, cautioned that not bailing out the Big Three could prove short-sighted.

``It's very different from Lehman because you don't have the systemic financial system risk, but it would be equally
stupid,'' Mr.~Barbera said. ``If Congress allows the auto companies to fail and with the effect that this would have on
sales and production, what this means to the real economy will have instantaneous and brutal effects on the stock market.''

In other words, Mr.~Barbera warned that opposition to lending either the \$17 billion agreed to -- or the \$34 billon that
the car companies originally requested -- could result in the stock markets' plunging by hundreds of billions of dollars.
And that does not include the billions of dollars in unemployment insurance benefits and pension bailouts that would be
required to assist not just the displaced auto workers, but also the many other workers, like truck drivers and waitresses,
whose jobs depend on the Big Three.

``There will be tremendous regret if we don't help them avoid bankruptcy in the next few weeks or months,'' said Mark Zandi,
chief economist with Moody's Economy.com. ``If they go into bankruptcy now, they'll go into
liquidation\index{liquidation}\hypertarget{liquidation}{}\footnote{\textbf{liquidation}:$[$\textsecstress likwi\textprimstress dei\esh\schwa
  n$]$. \textit{n}. the process of terminating the affairs of a business firm, etc, by realizing its assets to discharge its
  liabilities. (公司等的)清理, 清算; (债务的)清偿, (资产等的)变现;清除, 消灭; 整肃; 取消; 杀
  掉.\hyperlink{liquidation}{\textasciicircum}} and there will be the loss of hundreds of thousands, if not a million, jobs
-- on top of the four or five million we're going to lose. That will add almost a point to unemployment by itself.''

At a House Committee hearing Friday about Detroit's woes, Edward I. Altman, a professor of finance at New York University,
recommended that the automakers enter bankruptcy reorganization. Through such a move, he said, the automakers could sharply
cut their costs by negotiating deals with their creditors, dealers and labor unions.

Many supporters of a bailout say that filing for bankruptcy reorganization could quickly lead to liquidation because car
buyers might lose faith in the companies and worry that their auto warranties would not be honored.

Professor Altman said that large-scale debtor-in-possession lending -- either by the federal government or banks that would
have priority over other creditors -- could help keep the automakers operating (and guaranteeing their warranties) as they
reorganize and reduce costs on the way to regaining their competitiveness.

He said a revamping, helped by such financing under the bankruptcy laws, could actually reassure the stock market that ``the
damage can be minimized with a large debtor-in-possession financing'' because ``there will be more assurance that G.M. will
be around for a long time.''

Spencer Bachus of Alabama, the ranking Republican on the House Committee on Financial Services, which held Friday's hearing,
warned against a wholesale liquidation, saying it would jeopardize three million jobs. Yet he also opposed a federal bailout
``because it's just taking money and putting it into an inefficient operation and that money will be simply washed down the
drain.''

Mr.~Bachus voiced confidence that bankruptcy filings by one or more auto company would not cause markets to plunge. ``I
think a restructuring plan done with the protection of certain benefits of bankruptcy might be positively perceived,'' he
said.

But Mr.~Barbera warned against overconfidence, saying that Treasury officials thought they would carefully exact only a
pound of flesh from Wall Street by letting Lehman fail, helping teach other investment banks not to take excessive risks.

``But,'' he said, ``it turned out not to be a pound of flesh that was taken. It was a ton.''
\section{Luxe Losing Its Edge}
ROME -- With a world-weary sigh, Francesco Trapani slips off his \$10,000 steel and white-gold Bulgari watch, revealing the
band's dull underside. Bulgari once polished it to a fine gleam to match the shiny exterior.

The change is a subtle one, but it captures the cost-consciousness that the first recession in luxury-goods sales in nearly
20 years has forced on companies like Bulgari, Burberry, Cartier, Montblanc and other top designers, a modification of their
traditional focus on glamour and glitter.

The challenge is as delicate as polishing one of Bulgari's hallmark gems. In Bulgari's case, if Mr.~Trapani, the company's
chief executive, cuts too deeply, he risks harming the brand's image of opulence and exclusivity, carefully honed over
decades and reinforced by stars like Nicole Kidman, Charlize Theron and Scarlett Johansson, wearing Bulgari on red carpets
at Cannes or the Oscars.

``Instead of talking about stars and spending, you think about cutting costs,'' Mr.~Trapani said during an interview in his
office overlooking the Tiber. ``Luxury is not immune.''

Economizing does not come naturally to Mr.~Trapani, 51. He is a skilled yachtsman whose wife is a princess from
Liechtenstein. Until now, his claim to fame was transforming Bulgari from a handful of boutiques founded by his
great-grandfather into a worldwide luxury powerhouse.

But with the company's profit plunging 44 percent in the most recent quarter, and its stock suddenly tarnished, he has no
choice. Shares closed Thursday at \euro4.76, less than half what they were a year ago.

Since the 1990s, sales of luxury goods have exploded, along with the growth of a well-heeled new global elite, turning once
little-known European brands into giants and transforming chic addresses like Fifth Avenue, Bond Street and the
Champs-SPECIAL TREATlys\'ees into veritable open-air malls for the upper middle class.

Few brands epitomized this trend better than Bulgari, which has grown to 259 stores from just 5 when Mr.~Trapani took over
as chief executive in 1984. Demand for Bulgari's bold combinations of sapphires, diamonds and emeralds seemed insatiable as
sales boomed worldwide, lifting the company's revenue to more than 1.1 billion euros, or \$1.41 billion.

Even as Wall Street collapsed this fall, Mr.~Trapani presided over the star-studded opening of the flagship Bulgari store in
Paris, and the debut of its first company-owned boutique in the Middle East, with separate parties for men and women in
Qatar.

Now, reality has caught up with Bulgari and the rest of the industry. Sales at the 125-year-old jeweler rose an anemic 2
percent in the third quarter. Analysts are pessimistic about a recovery in its current fourth quarter, a period that is
responsible for an outsize portion of the company's annual results. And demand for luxury goods is expected to drop by 3 to
7 percent next year, according to a recent study by Bain \& Company, the first time the sector has recorded an annual sales
decrease since Bain began tracking it in the early 1990s.

There is no sign of a pre-Christmas rush at Bulgari's boutique on the Via Condotti, where Richard Burton once bought
diamonds for Elizabeth Taylor, and where unique pieces start at \euro70,000, or \$88,900.

``It's not politically correct to show off in this environment,'' said Claudia D'Arpizio, a partner at Bain who specializes
in luxury goods. ``Even if they're not affected in terms of purchasing power, consumers feel it's ethical to spend less.
They don't want the additional piece of jewelry.''

In response to the times, Mr.~Trapani has embarked on broad cost-cutting that includes shelving plans for new stores, except
in locations where leases have already been signed.

Burberry has announced a similar initiative, while Richemont, the owner of Cartier and Montblanc, is limiting openings to a
few fast-growing markets in the Middle East and Asia.

``Past slowdowns were more regional in nature and people could perceive the end game,'' Angela Ahrendts, Burberry's chief
executive, said in an interview. ``This is global. We were with an investor last week who has had to rerun his worst-case
scenario five times in the last five months, and we're still not there yet.''

Bulgari is also renegotiating existing leases with landlords to save on rent, Mr.~Trapani said, and even pressing suppliers
for better deals on diamonds, sapphires and other precious stones that are the raw material of its most expensive creations.

Then there are slight adjustments -- like the unpolished watch band -- that may save only a few euros an item but add up at
a company that sells thousands of timepieces annually, most priced from \$4,000 to \$32,000. Or introducing lower-cost boxes
and bottles for Bulgari's perfume line, which Mr.~Trapani said customers will not notice.

``We want the best solution for both the eye and the cost,'' Mr.~Trapani said. ``The challenge is to cut costs and diminish
expenses, without negatively affecting the image of the brand or the quality.''

Of the watchband, he said, ``It's more wearable and costs less.''

But Mr.~Trapani is resisting a shift to lower-price offerings, even though margins tend to be higher on less expensive
items.

``This isn't a business where you reduce prices to sell more,'' he said. ``This is totally wrong.''

With price cuts and more drastic style changes off the table, even Bulgari's most basic internal operations are changing,
like the workshop where its most expensive jewelry is made by hand.

Here, where loose rubies, emeralds and sapphires sit like pens and paper clips at a bank, goldsmiths do double-duty and
shine up their creations when polishers are out sick.

Overtime expenses, which are typical this time of year as the 21 goldsmiths rush to get one-of-a-kind necklaces and earrings
to stores in time for the holidays, have been nearly eliminated.

Of course, demand for the most expensive ornaments has not disappeared entirely. During a recent visit, three of the
craftsmen were busy finishing custom-ordered pieces, including cufflinks featuring Greek coins from the fifth century B.C.
and a pair of pendant earrings heavy with diamonds and sapphires.

``We won't change the game of life, thank God,'' said Nicola Bulgari, Mr.~Trapani's uncle and a vice chairman of the
company.

``It's part of the joy of life to wear jewelry, for the man and his ego. It is a world of fantasy and folly. Men will always
be in love with women and want to make them happy,'' he said.

Perhaps, but even Mr.~Bulgari, who at 67 remains active in designing the highest-end collections, is having to adapt to new
economic realities: he has stopped making additions to his collection of vintage American automobiles.

``If I need to sell them, I will,'' he said. He added that he was still buying shares in the company, which is publicly
traded. The family holds a controlling stake.

``It's a test for everybody,'' he said of the tight times. ``I know what they're selling at Bergdorf and Saks; they're
cutting numbers with an ax.''

He noted that Bulgari's perfume business was a bright spot. ``People are buying perfume like no tomorrow,'' he said. ``It's
a great consolation, it's not expensive, so you don't feel guilty.''

Giovanna Gambarelli would certainly agree.

A few yards from the workshop where the goldsmiths create custom pieces behind thick glass and tight security, Ms.
Gambarelli was recently shopping for bargains at Bulgari's little-known factory outlet in an industrial area on the edge of
Rome.

Sporting a Rolex watch and a Tiffany bracelet, Ms.~Gambarelli, 39, recalled how she had shopped three years ago at the Via
Condotti store. This year, eyeing watches marked with a little green label that signified the deepest markdowns, she said,
``If you don't want the new collection, you can choose anything here and get a 40 percent discount.''

\section{In Hard Times, Is Best Buy's Best Good Enough?}

AMY ADONIZ, general manager at the Best Buy flagship store, knows what her staff wants for Christmas: a case of Red Bull.

Two weeks before Black Friday, Ms.~Adoniz gave in to employees' requests and had a Red Bull vending machine installed at the
store, at 62nd Street and Broadway in Manhattan. Many in the sales staff of 140 are drama students, opera singers and actors
who may run themselves ragged selling electronics by day and performing at night. To keep them from getting hungry and
cranky over the long Thanksgiving weekend, Ms.~Adoniz let them wear slippers and Uggs boots to work, and had food delivered
three times a day.

Employees aren't the only ones being tended to this shopping season. To lure customers, Ms.~Adoniz waits for -- and on --
their dogs. ``We have a doggie water bowl with filtered water, and treats for them as well,'' she says.

With unemployment rising sharply, and consumer spending
plummeting\index{plummet}\hypertarget{plummet}{}\footnote{\textbf{plummet}:$[$\textprimstress pl\pwedge mit$]$. \textit{vi}. 垂直落下; 骤然
  失落\hyperlink{plummet}{\textasciicircum}}, Best Buy managers are bending over backward to attract shoppers and are
encouraged to put their personal stamp on the stores. For Ms.~Adoniz, that means stoking employees with caffeine and
carbohydrates\index{carbohydrate}\hypertarget{carbohydrate}{}\footnote{\textbf{carbohydrate}:$[$\textprimstress k\vara\textlengthmark b\schwa
  u\textprimstress haidreit$]$. \textit{n}. 【化】碳水化合物, 糖类\hyperlink{carbohydrate}{\textasciicircum}} and catering
to customers' pets.

It's an extraordinarily tough time for retailers. ``November is shaping up to be the worst month in retail since I've been
here 30 years,'' says Edward Schmults, C.E.O. of FAO Schwarz, the toy chain. ``Now I know how that little kid felt who
misbehaved all year and then wondered if Santa was going to show up in December.''

Next year could be even worse. Fitch Ratings forecasts that the United States economy will contract 1.2 percent in 2009,
with consumer spending falling 1.6 percent. ``The impact on retailers is almost tragic as the economy adjusts,'' Mr.
Schmults says.

And Best Buy, to limit the damage, is not just cutting prices. It is trimming inventory and advertising, promoting
higher-margin, private-label lines and pushing exclusive products, like the Blue Label series of notebook computers made for
Best Buy by Hewlett-Packard and Toshiba. It's also adding new services and products that specifically aim at women.

If the stock market and consumer spending hadn't plunged so precipitously, Best Buy, the nation's biggest electronics
retailer, with \$44 billion in annual revenue, might not have had to bother stocking up on delectables for dogs. The chain's
chief rival, Circuit City, recently filed for bankruptcy protection and is closing 155 stores. Tweeter, a high-end rival,
shut down this week, and Sharper Image's stores, which sold more exotic electronics, are liquidating. CompUSA closed most of
its stores last year.

But no retailer is immune from the drop in consumer confidence and spending, especially one that specializes in gadgets, not
groceries. Sales at Best Buy stores open more than a year were down 7.8 percent in October, compared with the same month
last year. The company will not release November figures until Dec. 16, but it's already clear that November was a brutal
month for electronics retailers. According to a report MasterCard Advisors released last week, sales of electronics and
appliances nationwide sank 25.2 percent in November, versus the same month last year.

Best Buy's stock price, which reached almost \$54 in November 2007, closed Friday at \$23.05, and its market capitalization
has shrunk to \$9.5 billion. Because of slumping sales, Fitch Ratings in mid-November downgraded the outlook on Best Buy's
\$2.7 billion in debt to negative, from stable.

Nevertheless, Karen Ghaffari, a managing director at Fitch, says she thinks Best Buy will weather the storm. Its
longstanding reputation for high-quality service helped it grab market share this year when Circuit City laid off many of
its highest-paid -- and most experienced -- sales workers, and shuttered stores.

``Best Buy is a very strong operator,'' Ms.~Ghaffari says, ``and long-term they should benefit from the difficulties being
experienced by the weaker competitors.''

That may well be so. But consumers' reluctance to spend is making Best Buy's investors
skittish\index{skittish}\hypertarget{skittish}{}\footnote{\textbf{skittish}:$[$\textprimstress skiti\esh$]$. \textit{adj}. playful, lively,
  or frivolous.易惊的(马等);羞怯的; 胆小的;(尤指女人) 轻浮的;不可靠的, 多变的;\hyperlink{skittish}{\textasciicircum}}.
Though analysts expect revenue to grow slightly next year as the company expands overseas, profit margins will come under
pressure from price-cutting, especially on televisions. ``Given the circumstances and uncertainty in what's coming here in
this market, we decline to comment,'' said a press officer at Gardner Lewis Asset Management, which owned almost four
million shares of Best Buy in June.

In an interview, Best Buy's president, Brian Dunn, discussed the challenges the company faced. ``The depth and speed with
which the economy stumbled was extraordinary,'' said Mr.~Dunn, who started as a salesman at the chain 23 years ago. ``I've
never seen anything like it. Our business was growing really nicely and then, all of a sudden, boom!''

BEST BUY'S winter holiday shopping season is crucial, as it is for every retailer. A good Christmas can make the difference
between a mediocre\index{mediocre}\hypertarget{mediocre}{}\footnote{\textbf{mediocre}:$[$\textsecstress mi\textlengthmark
  di\textprimstress\schwa uk\schwa ; \textprimstress mi\textlengthmark di\schwa uk\schwa$]$. \textit{adj}. average or
  ordinary in quality.中等的.\hyperlink{mediocre}{\textasciicircum}} year and a fantastic one. Ten percent of a retailer's
sales can come on Black Friday alone, and typically, almost 60 percent of Best Buy's profit comes from fourth-quarter sales.

Now that it's clear that fourth-quarter sales and profits will be down substantially from last year, the chain is scrambling
to cut costs. There will be fewer national TV commercials and more targeted e-mail crowing about low prices.

Best Buy stores are stocked with thousands of boxes of the hit video games Rock Band 2, Guitar Hero and Wii Fit, along with
myriad\index{myriad}\hypertarget{myriad}{}\footnote{\textbf{myriad}:$[$\textprimstress miri\schwa d$]$. \textit{adj}. innumerable.无数
  的.\hyperlink{myriad}{\textasciicircum}} camcorders, digital cameras, flat-screen TVs and GPS devices. Nevertheless, to
make sure that the company isn't stuck with mountains of unsold merchandise after Christmas, Best Buy is cutting inventory
levels to match reduced demand, Mr.~Dunn says. But the company will not say by how much.

``Suppliers are being flexible,'' Mr.~Dunn says. ``Apple, HP, Samsung and Sony have answered the bell nicely and worked with
us on inventory levels.''

To accommodate shoppers, Best Buy is offering more
lenient\index{lenient}\hypertarget{lenient}{}\footnote{\textbf{lenient}:$[$\textprimstress li\textlengthmark nj\schwa nt$]$. \textit{adj}.
  showing or characterized by mercy or tolerance.宽大的, 厚道的, 慈悲为怀的.\hyperlink{lenient}{\textasciicircum}}
financing. Customers who charge at least \$499 worth of merchandise on a store credit card don't have to pay interest for 18
months. ``We don't push it,'' Mr.~Dunn says, ``but customers are grabbing the 18-month financing options.'' Last year,
shoppers had to spend at least \$499 on one item to receive such financing. ``Now you can put whatever you want into your
cart to get it up to \$499,'' he says.

That strategy worked for Nadia Lora and her husband, Carlos, both 21. The couple work at Nunzio's Grill, a restaurant in
Vauxhall, N.J., where she is the manager and he is a cook. They were shopping at a Best Buy near the restaurant on the
Friday after Thanksgiving, and they bought a JVC camcorder and a Garmin Nuvi GPS system, purposely spending enough to hit
the \$499 financing threshold. Ms.~Lora said the Best Buy incentives allowed her to justify her purchases: ``I like that
they don't charge interest for stuff for months.''

IN this stressed-out holiday season, Best Buy is trying to be hip and friendly. The chain is the only retailer to have
exclusive rights to sell the new Guns N' Roses album, ``Chinese Democracy,'' in its stores and has hired Magic Johnson to
open stores in urban areas. Free
limousine\index{limousine}\hypertarget{limousine}{}\footnote{\textbf{limousine}:$[$\textprimstress limu(\textlengthmark
  )zi\textlengthmark n$]$. \textit{n}. any large and luxurious car, esp one that has a glass division between the driver and
  passengers.大型高级轿车.\hyperlink{limousine}{\textasciicircum}} rides and mini-camcorders were offered to 25 customers in
New York, Los Angeles, Boston, Miami and other major markets who wrote compelling, 250-word essays about why shopping at
Best Buy on the day after Thanksgiving was a meaningful ritual for their families.

Claudia Di Folco, 35, an actress and former television news reporter, was shopping at Best Buy two days before Thanksgiving.
She bought a \$299 Slingbox, which transfers whatever is playing on your home television onto a laptop, cellphone or PC, so
her husband could watch the New York Jets game during a trip to Rome. Ms.~Di Folco lives a few blocks from the Best Buy
store at 86th Street and Lexington Avenue on the Upper East Side and shops there often. ``They always have special sales, or
at least the big yellow signs make you think they do,'' she says.

On the day after Thanksgiving back at 62nd and Broadway, hundreds of electronics fans lined up. ``We had a fabulous day,''
says Ms.~Adoniz, 41, that store's manager, though she says she was less confident earlier in the week. ``With everything
happening with the economy, we didn't know if that was going to scare customers away.''

But when she arrived at 1:30 a.m. on Friday, 500 people were waiting. Customers had been outside since Thanksgiving morning:
they sat huddled in sleeping bags; the line went around the block to Central Park West and back. Ms.~Adoniz gave out coffee
and sales fliers.

Samsung employees played trivia contests with shoppers, doling out T-shirts, tote bags and other prizes. Ms.~Adoniz's fliers
detailed the store's so-called doorbuster sales -- 50-inch plasma televisions for \$799, laptops starting at \$329, GPS
devices for \$99, digital cameras for \$50. Prices have inched up since then, but, Ms.~Adoniz says, ``there is still a lot
of holiday traffic and a lot more online ordering.'' Laptops are particularly popular.

Among televisions, the best seller at her store was the 42-inch Dynex, the chain's private label; it sold for \$499. Margins
on private-label items are much higher than margins on name-brand electronics, so Best Buy is pushing Dynex as well as its
Insignia line of digital cameras, televisions and GPS devices.

``The TVs were flying out the door; they were huge,'' Ms.~Adoniz says.

The company hasn't released official figures for Black Friday, but analysts say sales were better than expected. In an
effort to keep customers buying, Best Buy aggressively promoted low prices on its Web site every day last week.

In a down economy, the biggest challenge for Best Buy may be from discounters that are chasing its core base of gadget-happy
consumers.

``Wal-Mart, Costco and Target have expanded their assortments,'' says Steven L. Martin, who manages Slater Capital
Management, a retail hedge fund. ``Five years ago if you said Wal-Mart would sell plasma TVs, no one would have believed
you.''

Best Buy also faces stiff competition from retailers like Amazon that do business exclusively online. The company is
fighting back by allowing shoppers to make purchases online and then pick them up at Best Buy stores, which eliminates
shipping costs. ``Out of this storm comes new operating models,'' Mr.~Dunn says. ``The ecosystem is going to change. We see
storefronts closing.''

For now, though, Best Buy has a potent weapon in its battle with the discounters and online sellers: its staff. Members of
Best Buy's sales staff, a k a ``Blue Shirts,'' go through a 20-hour training program, then spend two weeks shadowing an
experienced sales staff member around the floor. Historically, the Best Buy training program has been so strong, some people
in the industry say, that competitors often waited for Best Buy to let staff go after Christmas, and then snap them up.

Ms.~Di Folco, the actress, says: ``Most of the time, I find really informed people who can actually answer my questions.
It's like they seem to be electronic junkies versus kids wasting time at a part-time job they don't enjoy.''

Its sales force may give Best Buy a competitive advantage even in a holiday season when many customers are interested in
rock-bottom prices.

``The importance of the salesperson is directly related to the price of the product being sold,'' says Chris Denove, vice
president at J. D. Power \& Associates, the consumer research firm. ``If you're talking about toothpaste or pencils, the
salesperson is immaterial, but when you're talking about high-end electronics such as flat screen TVs, the salesperson can
be critical.''

Target, meanwhile, is going after the technical support business -- a big profit center for Best Buy -- and has hired Zip
Express, a company started by Chris Mauzy, a former Best Buy employee, to challenge the ``Geek Squad'' for which Best Buy is
known. For a fee, members of the Geek Squad will install your purchase and provide technical support, even on products not
bought at Best Buy. It's a huge profit center for the company.

Mr.~Mauzy, who left Best Buy to start Zip Express in October 2007, is introducing an electronics-installation service for
200 Target stores.

To further protect itself against inroads from the discounters, Best Buy is trying to make shopping more appealing to women.
Its Omega Wolves program, a focus group made up of 3,500 working women in the United States and London, has a page on
Facebook; Omegas socialize and give the chain feedback. Thanks to the Omegas, Ms.~Adoniz's store has what she calls ``nicer
fixtures,'' like wood-trimmed displays and lighter backdrops.

Ms.~Adoniz's store also aims to stock accessories with women in mind: fake leopard skin and red crocodile cases for
BlackBerrys and other gadgets from Liz Claiborne, Betsey Johnson, Dooney \& Bourke, Tumi and Steve Madden. Crystal Stroupe,
a personal shopper and an aspiring opera singer, spends much of her time at Best Buy keeping the accessories table neat and
pretty.

Ms.~Adoniz says the accessories table brings a lot of astonished looks, ``but we know the female shopper was an underserved
market.'' Best Buy says women are now spending more money at its stores than men, which has led Ms.~Adoniz and managers of
other stores to expand accessories aimed at women. Many Best Buy stores now carry items like blow-dryers, curling irons and
hair straighteners, as well as pink cameras and phones. ``We have a whole personal care section and it does very well,'' Ms.
Adoniz says.

The effort to appeal to women may ultimately help Best Buy distinguish itself from traditional electronics retailers, which
tend to market electronics to men.

``You can't assume that every expensive TV is going to be bought by a male,'' says Matthew J. Fassler, a retail analyst at
Goldman Sachs. ``Women need to be served as intently as men.''

THAT said, Best Buy's business is hard-core electronics, not blow-dryers; the company is betting that if a family buys just
one gift this December, it will involve electronic entertainment. ``When the customer gets into difficulty, they tend to
cocoon,'' Mr.~Dunn says. ``After 9/11, they invested in their homes and loved ones and experiences.''

Mr.~Dunn says he usually wins his office pool for predicting December results; this year, he's betting that cocooning drives
sales, but he acknowledges that ``it's too soon to tell'' how the holiday season will play out.

``As the economy becomes tougher, people think more carefully about whether they really need to buy an item,'' he says.
``The threshold for a considered purchase has moved down. Last year, it might have been \$500. This year, it might be \$300,
\$200 or even \$100 for some families.''

Enough for an iPod case and a Slingbox cable, but not much more.


\section{For New President, Fighter Jet Decision Poses a Test}
Two of President-elect Barack Obama's stated goals -- cutting wasteful spending and saving or creating millions of jobs --
are on a collision course in a looming decision over whether to keep building the F-22 fighter jet.

Air Force officials have told Congress that they are hoping to win a \$9 billion commitment to produce at least 60 F-22s
over a three-year period, which would expand the fleet to 243.

But the F-22, a stealthy, supersonic fighter that was designed during the cold war and has never been used in combat, has
many critics, and they include Robert M. Gates, who will remain Defense secretary in the Obama administration. Mr.~Gates has
questioned the relevancy of the F-22, and said the military should focus its resources more on fighting
insurgencies\index{insurgent}\hypertarget{insurgent}{}\footnote{\textbf{insurgent}:$[$in\textprimstress
  s\schwa\textlengthmark d\yogh\schwa nt$]$. \textit{adj}. rebellious or in revolt, as against a government in power or the
  civil authorities. 起义的, 造反的, 暴动的, 叛乱的.\hyperlink{insurgent}{\textasciicircum}} like those in Iraq and
Afghanistan.

Meanwhile, supporters of the F-22 program -- which has cost more than \$65 billion so far -- argue that Mr.~Obama should
extend its production, at least temporarily, to preserve thousands of jobs related to building the jets, which cost \$143
million each.

``To continue F-22 production would be to continue all the fundamental problems we've been having over the last 30 years,
where each new weapons system costs so much that we end up with a
dwindling\index{dwindle}\hypertarget{dwindle}{}\footnote{\textbf{dwindle}:$[$\textprimstress dwindl$]$. \textit{vi}. to grow
  or cause to grow less in size, intensity, or number; diminish or shrink gradually.减少, 缩小; 变
  瘦.\hyperlink{dwindle}{\textasciicircum}} inventory of planes, ships and tanks,'' said Winslow T. Wheeler, an analyst at
the Center for Defense Information, a nonprofit group in Washington.

``It's the first test of whether President Obama is going to go along with business as usual or instead will bring much
needed change to the Pentagon,'' he added.

Defense experts say his decision, expected early next year, could provide the first sign of whether the economic crisis
would force the military to make much harder choices about what kind of wars it should be prepared to fight.

So far, Mr.~Obama has been vague\index{vague}\hypertarget{vague}{}\footnote{\textbf{vague}:$[$vei$]$. \textit{adj}. (of statements,
  meaning, etc) not explicit; imprecise.含糊的, 暧昧的; 不明确的.\hyperlink{vague}{\textasciicircum}} about his defense
plans, saying only that he does not intend to cut the recent record spending levels while the nation is at war and that he
will review major weapons programs with Pentagon and Congressional leaders.

But nearly everyone expects defense spending to tighten over time, and that the military will no longer have enough money to
prepare for every contingency\index{contingency}\hypertarget{contingency}{}\footnote{\textbf{contingency}:$[$k\schwa
  n\textprimstress tind\yogh\schwa nsi$]$. \textit{n}. a possible but not very likely future event or condition;
  eventuality.意外， 意外事故.\hyperlink{contingency}{\textasciicircum}}.

As a result, Mr.~Obama's transition team is already being lobbied by military services seeking to preserve prized programs,
from the Army's plans for advanced combat gear to the ground-based missile defense system.

The F-22 program, which the Bush administration wanted to end, may survive only if something else is cut from the Pentagon
budget. That means the Obama administration's decision will set the tone for how tough-minded it will be in balancing
competing pressures.

Without further spending for the F-22, companies that supply critical components for it would begin shutting down soon.

The chairmen and ranking Republicans on both the House and Senate defense appropriations subcommittees recently wrote to
Mr.~Gates to voice their support for the F-22, cautioning that ``the last thing our nation needs is to terminate jobs in
this time of such economic uncertainty.''

Like many big weapons systems, the plane, which relies on 1,000 parts suppliers in 44 states, has strong support in
Congress, which recently provided up to \$140 million in bridge financing for some of the suppliers.

``I think we're going to keep the F-22 going, that's my gut\index{gut}\hypertarget{gut}{}\footnote{\textbf{gut}:$[$\pwedge
  t$]$. \textit{n}. the lower part of the alimentary canal; intestine.肠, [pl. ]内脏.[pl. ]勇气, 胆量, 能力, 厚
  脸.\hyperlink{gut}{\textasciicircum}} instinct,'' said Norman Dicks, a Democrat from Washington who also sits on the House
subcommittee that approves money for defense programs.

``But it's going to be a very tight budget environment,'' he said. ``We've still got the \$12 billion to \$15 billion a
month that we're spending on the war, we've got to
replenish\index{replenish}\hypertarget{replenish}{}\footnote{\textbf{replenish}:$[$ri\textprimstress pleni\esh$]$.
  \textit{n}. 补充\hyperlink{replenish}{\textasciicircum}} the troops and the equipment that has been used up, and we've
still got this whole need to modernize the Air Force, the Army and the Navy. And a lot of people are going to look at the
consequences of ending these programs on a further deterioration in the economy.''

The plane had far more support in the 1980s, when the Air Force envisioned buying up to 750 of the planes to dominate
dogfights with Soviet jets.

The F-22 can perform tactical operations at higher altitudes than other fighters, and it can cruise at supersonic speeds
without using telltale afterburners. With its stealthy skin that scatters radar detection signals, it can also sneak in and
destroy enemy surface-to-air missile defenses, clearing the way for bombers and other planes to follow.

Because of complications with some of the technologies, the plane ran into major delays and cost overruns that are typical
of many defense projects, and more than 20 years passed before it was ready for military use in 2005.

By then, the Pentagon's focus had shifted to the wars against Islamic insurgents, and many critics, including Mr.~Bush's
first Defense secretary, Donald H. Rumsfeld, and then Mr.~Gates, began slashing spending for the F-22, leading to unusually
bitter confrontations with Air Force officials.

Mr.~Gates, in particular, has questioned what he called ``a tendency toward what might be called next-war-itis -- the
propensity\index{propensity}\hypertarget{propensity}{}\footnote{\textbf{propensity}:$[$pr\schwa\textprimstress pensiti$]$.
  \textit{n}. a natural tendency or disposition.倾向, 爱好, 嗜好, 脾性(to, for).\hyperlink{propensity}{\textasciicircum}} of
much of the defense establishment to be in favor of what might be needed in a future conflict'' rather than the tanks and
armored troop transports needed now.

Mr.~Gates has pressed instead for more spending on heavily armored, mine-resistant troop transports and unmanned planes that
can conduct surveillance and carry out missile strikes on terrorists.

The Air Force said in a statement that it would be ``premature'' to talk publicly about its goals for the F-22 since
Mr.~Obama's team ``has not had the opportunity to establish a position.''

But some Air Force officials say they are still required under the national military strategy to prepare for larger wars as
well, no matter how remote the chances.

``Next-war-itis is a parallel to something called ostrich-itis, and that means you can't bury your head in the sand and
assume that the way things are now are the way they'll be across the board in the future,'' said one senior military
officer, who spoke on condition that he not be named because he was not authorized to discuss the matter.

He added that Russia and China are also selling surface-to-air missile defense systems to smaller nations, and planes like
the F-22 are needed ``to dissuade and deter other countries so we never have to fight.''

Air Force officials also have told Congress that they need more F-22s to create cost-efficient squadrons in important
locations and to provide pilot training. Another concern, they say, is that many of the F-15 Eagles, which have been the
lead fighter jets for 25 to 30 years, are wearing out from overuse and age, while another new model, the Joint Strike
Fighter, or F-35, is still several years away from full-scale production.

Two of Mr.~Gates's top advisers, Gordon England, the deputy secretary of Defense, and John J. Young Jr., the Pentagon's
under secretary for acquisition, want to cut off spending for the F-22 to free up money for the Joint Strike Fighter.

Though it cannot match the speed or evasiveness of the F-22, the joint fighter also has advanced stealth features. It is
meant to be less expensive and built in far greater numbers for use by the Navy, the Marine Corps and major allies as well
as the Air Force.

In the last several weeks, Mr.~Young has seemed to step up his campaign against the plane, telling reporters that the F-22
needs \$8 billion in upgrades, is expensive to maintain and has not lived up to all its performance promises.

And a House Armed Services subcommittee has held a hearing to chastise Mr.~Young for refusing to spend more than \$50
million of the \$140 million in bridge money that Congress had set aside for F-22 suppliers, thus increasing the pressure on
the Obama administration to decide quickly whether to keep the program alive.

Under a previous deal, the main contractor, Lockheed Martin, will be working through 2011 to assemble the planes that the
government has already ordered. But some of the delicate components take two to three years to produce, company officials
say.

So critical suppliers would start shutting down their lines if money was not provided soon for additional orders. And
several thousand of the 25,000 people whose jobs depend on the plane could be laid off over the next year if their companies
could not find replacement business.

Both Mr.~England and Mr.~Young will be departing with the Bush administration.

Mr.~Obama's transition team wants to complete its own assessment of the military threats and weapons programs before making
any recommendations.

``What Obama has said repeatedly is that he wants to hear from senior military people on the options,'' said F. Whitten
Peters, a former Air Force secretary who advised Mr.~Obama on defense issues during the campaign but is not on his
transition team. ``And at some point, rational minds can say, 'This is what we ought to do.' ''

\section{Whistle-Blowers in Chinese City Sent to Mental Hospital}
BEIJING -- Local officials in Shandong Province have apparently found a cost-effective way to deal with gadflies,
whistle-blowers and all manner of muckraking citizens who dare to challenge the authorities: dispatch them to the local
psychiatric hospital.

In an investigative report published Monday by a state-owned newspaper, public security officials in the city of Xintai in
Shandong Province were said to have been institutionalizing residents who persist in their personal campaigns to expose
corruption or the unfair seizure of their property. Some people said they were committed for up to two years, and several of
those interviewed said they were forcibly medicated.

The article, in The Beijing News, said most
inmates\index{inmate}\hypertarget{inmate}{}\footnote{\textbf{inmate}:$[$\textprimstress inmeit$]$. \textit{n}. 同居人(尤指同
  院病人、同狱犯人或住在同一救济院、收容所的人)\hyperlink{inmate}{\textasciicircum}} were released after they agreed to give
up their causes.

Sun Fawu, 57, a farmer seeking compensation for land spoiled by a coal-mining operation, said he was seized by local
authorities on his way to petition\index{petition}\hypertarget{petition}{}\footnote{\textbf{petition}:$[$pi\textprimstress
  ti\esh\schwa n$]$. \textit{n}. 请愿\hyperlink{petition}{\textasciicircum}} the central government in Beijing and taken to
the Xintai Mental Health Center in October.

During a 20-day stay, he said, he was lashed to a bed, forced to take pills and given injections that made him numb and
woozy. According to the paper, when he told the doctor he was a petitioner, not mentally ill, the doctor said: ``I don't
care if you're sick or not. As long as you are sent by the township government, I'll treat you as a mental patient.''

In an interview with the newspaper, the hospital's director, Wu Yuzhu, acknowledged that some of the 18 patients brought
there by the police in recent years were not deranged, but he said that he had no choice but to take them in. ``The hospital
also had its misgivings,'' he said.

Xintai officials do not see any shame in the
tactic\index{tactic}\hypertarget{tactic}{}\footnote{\textbf{tactic}:$[$\textprimstress t\ae ktik$]$.
  \textit{n}. 战术\hyperlink{tactic}{\textasciicircum}}, and they boasted that hospitalizing people they characterized as
troublemakers saved money that would have been spent chasing them to Beijing. There is another reason to stop petitioners
who seek redress\index{redress}\hypertarget{redress}{}\footnote{\textbf{redress}:$[$ri\textprimstress dres$]$.
  \textit{n}. 矫$[$纠, 修, 改$]$正,赔$[$补$]$偿, 补救\hyperlink{redress}{\textasciicircum}} from higher levels of
government: they can prove embarrassing to local officials, especially if they make it to Beijing.

The Xintai government Web site noted that provincial authorities had recently referred to Xintai as ``an advanced city in
building a safe Shandong.'' They said that from January to May this year, the number of petitioners who went over the heads
of local authorities was 274, a 4 percent drop from the same period in 2007. Although China is not known for the kind of
systematic\index{systematic}\hypertarget{systematic}{}\footnote{\textbf{systematic}:$[$\textsecstress
  sist\schwa\textprimstress m\ae tik$]$. \textit{adj}. 系统的\hyperlink{systematic}{\textasciicircum}} abuse of
psychiatry\index{psychiatry}\hypertarget{psychiatry}{}\footnote{\textbf{psychiatry}:$[$sai\textprimstress kai\schwa tri$]$.
  \textit{n}. 精神病学\hyperlink{psychiatry}{\textasciicircum}} that occurred in the Soviet Union, human rights advocates
say forced institutionalizations are not uncommon in smaller cities. Robin Munro, the research director of China Labor
Bulletin, a rights organization in Hong Kong, said such ``an kang'' wards -- Chinese for peace and health -- were a
convenient and effective means of dealing with pesky
dissidents\index{dissident}\hypertarget{dissident}{}\footnote{\textbf{dissident}:$[$\textprimstress disid\schwa nt$]$.
  \textit{n}. 持异议者\hyperlink{dissident}{\textasciicircum}}.

``Once a detainee has been officially diagnosed as dangerously mentally ill, they're immediately taken out of the criminal
justice system and they lose all legal rights,'' said Mr.~Munro, who has researched China's practice of psychiatric
detention\index{detention}\hypertarget{detention}{}\footnote{\textbf{detention}:$[$di\textprimstress ten\esh\schwa n$]$.
  \textit{n}. 拘留, 扣押, 监禁\hyperlink{detention}{\textasciicircum}}.

In recent years practitioners\index{practitioner}\hypertarget{practitioner}{}\footnote{\textbf{practitioner}:$[$pr\ae
k\textprimstress ti\esh\schwa n\schwa$]$. \textit{n}. 从业者\hyperlink{practitioner}{\textasciicircum}} of Falun Gong, the
banned spiritual movement, have complained of what they call coerced hospitalizations. One of China's best-known dissidents,
Wang Wanxing, spent 13 years in a police-run psychiatric institution under conditions he later described as abusive.

In one recent, well-publicized case, Wang Jingmei, the mother of a man convicted of killing six policemen in Shanghai, was
held incommunicado\index{incommunicado}\hypertarget{incommunicado}{}\footnote{\textbf{incommunicado}:$[$\textsecstress
ink\schwa\textsecstress mju\textlengthmark ni\textprimstress k\vara\textlengthmark d\schwa u$]$. \textit{adj}. 被禁止接触外界
的, 被单独监禁的\hyperlink{incommunicado}{\textasciicircum}} at a mental hospital for five months and released only days
before her son was executed in late November.

The article in The Beijing News about the hospitalizations in Xintai was notable for the attention it gained in China's
constrained state-run media. Such Communist Party stalwarts as People's Daily and the Xinhua news agency republished the
article, and it was picked up by scores of Web sites. At Sina.com, the country's most popular portal, the report ranked as
the fifth most-viewed news headline, and readers posted more than 23,000 comments by evening. The indignation expressed was
universal, with many clamoring\index{clamor}\hypertarget{clamor}{}\footnote{\textbf{clamor}:$[$\textprimstress kl\ae
m\schwa$]$. \textit{n}. 喧闹,叫嚷,大声的要求\hyperlink{clamor}{\textasciicircum}} for the dismissal of those involved.
``They're no different from animals,'' read one post. ``No, they're worse.''

By Monday evening, the Xintai city government was rejecting the report by The Beijing News as
reckless\index{reckless}\hypertarget{reckless}{}\footnote{\textbf{reckless}:$[$\textprimstress reklis$]$. \textit{adj}. 不注
意的; 粗心大意的\hyperlink{reckless}{\textasciicircum}} and
slanted\index{slant}\hypertarget{slant}{}\footnote{\textbf{slant}:$[$sl\vara\textlengthmark nt$]$. \textit{adj}. 倾斜的
\hyperlink{slant}{\textasciicircum}}. In a telephone interview broadcast on Shandong provincial television, an unidentified
municipal official suggested that those confined to the mental hospital had gone mad from their single-minded quest for
justice. ``There are some people who have been petitioning for years and become mentally aggravated,'' the official said.

Reached by phone on Monday, a hospital employee said Mr.~Wu, the hospital director who voiced his misgivings to The Beijing
News, was unavailable. The employee, Hu Peng, said that officials from the local government had taken him away for ``a
meeting'' earlier in the day.

Although he would not provide a reporter with contact information for the former patients, Mr.~Hu defended the
hospitalizations, saying that all those delivered by the Public Security Bureau were sick. He added that the hospital was
not authorized to provide a diagnosis to the patients, only to treat them. ``We definitely would not accept those without
mental problems,'' he said.

\section{House Passes Auto Rescue Plan}

WASHINGTON -- The House voted on Wednesday to approve a \$14 billion government rescue of the American automobile industry,
but the bailout plan, which would provide emergency loans to General Motors and Chrysler, was in jeopardy because of strong
Republican opposition in the Senate.

The House approved the rescue plan by 237 to 170, mostly along party lines, with 32 Republicans mainly from states heavily
dependent on the auto industry joining 205 Democrats in supporting the measure. Voting against were 150 Republicans and 20
Democrats.

The White House so far has failed to generate support among Senate Republicans, who have the power to kill the bill.

General Motors and Chrysler have said they cannot survive much longer without the federal aid, while Ford Motor Company,
which is in better shape than its competitors, has said it will not seek the emergency loans.

As an amendment to the auto rescue plan, the House approved a measure that would require banks receiving assistance from the
Treasury's \$700 billion economic stabilization program to detail new lending activity each quarter.

The White House chief of staff, Joshua B. Bolten, attended a lunch at the Capitol with Republican senators to persuade them
to back the auto rescue plan but met stiff resistance.

Some Republican senators said the automakers should be allowed to fail. Others said the proposed oversight of the rescue by
a so-called car czar was too weak. Senator George V. Voinovich, an Ohio Republican who is one of the few outspoken
Republican supporters of a taxpayer-backed rescue, emerged from the lunch sounding deeply pessimistic. Mr.~Voinovich said
that Senate Republicans had refused to participate in negotiations with the White House because of general opposition to an
auto bailout.

``The leadership did not want to participate because they felt whatever came out of the negotiations, they probably wouldn't
support,'' Mr.~Voinovich said. He said he still intended to vote for the plan.

The Republican leader, Senator Mitch McConnell of Kentucky, was noncommittal. The Republicans had a ``spirited'' discussion
about the auto rescue plan, he said, but it was too soon to take a stand because they had just received a final draft of the
bill.

``Everybody's still kind of poring through it, trying to figure out exactly what it does,'' Mr.~McConnell said. ``At this
particular juncture, I couldn't handicap for you the level of support that may exist in our conference. But we did begin a
conferencewide learning process during the course of the last hour.''

Even some auto-state lawmakers were unhappy with the bailout plan the White House helped to design. ``While I am fighting to
save Missouri auto jobs,'' said Senator Christopher S. Bond, Republican of Missouri, ``Congress is just putting off the
inevitable unless we force the companies to reform fundamentally, which this latest plan fails to do and is why I am
offering changes to make it work.''

A number of other Senate Republicans said they had every intention of scuttling a taxpayer-financed rescue for General
Motors and Chrysler.

Senator Richard C. Shelby of Alabama, the senior Republican on the banking committee, called the proposal ``a
travesty''\index{travesty}\hypertarget{travesty}{}\footnote{\textbf{travesty}:$[$\textprimstress tr\ae visti$]$. \textit{n}.
(对人或文学作品等的)滑稽模仿; 谐摹诗$[$文$]$; 拙劣的做法$[$演出$]$; 牵强附会; 歪曲.\hyperlink{travesty}{\textasciicircum}}
and said that he would
filibuster\index{filibuster}\hypertarget{filibuster}{}\footnote{\textbf{filibuster}:$[$\textprimstress filib\pwedge
st\schwa$]$. \textit{vt}. $[$美$]$(因发言冗长)故意阻挠议案的通过\hyperlink{filibuster}{\textasciicircum}} the bill. ``This
is an installment on a huge bailout that will come later,'' he said.

Others, while critical of the legislation, suggested there was hope of a compromise.

Senator Bob Corker, Republican of Tennessee, who was working to draft alternative legislation, said the proposal put forward
by the White House and Congressional Democrats provided only weak authority for the car czar, who would supervise the
sweeping reorganization plans that the automakers have agreed to carry out.

``I have a banking staffer who can carry out the responsibilities of this so-called czar,'' Mr.~Corker said. ``I mean it's a
liaison. This person has no power.''

Mr.~Corker said the bill put forward by the Bush administration and Democrats and approved by the House would entangle the
federal government in the operations of the auto companies for too long. Without substantial changes, he said, the
legislation was unlikely to win passage in the Senate.

``I didn't see anybody in the group who is willing to blink,'' he told reporters. An aide to the Senate majority leader,
Harry Reid of Nevada, said the Democrats were trying to negotiate a deal with Mr.~McConnell under which there would be
several votes on measures intended to aid the auto industry including, perhaps, alternative proposals by Mr.~Corker or other
Republicans.

Some Congressional Democrats speculated that if Senate Republicans were kill the rescue plan, the Treasury secretary, Henry
M. Paulson, Jr., would have no choice but to keep G.M. and Chrysler afloat, at least until the new Congress begins early
next month and wider Democratic majorities are sworn into office.

In the compromise measure that emerged from negotiations with the White House, House Democrats agreed to drop a provision to
force the automakers to end their legal challenges to state emissions standards, including a lawsuit in California.

In the broadest sense, the House and Senate bills provide an identical government rescue of the two most imperiled
automakers, G.M. and Chrysler, in the form of \$14 billion in emergency loans. In exchange for the loans, the auto
manufacturers would have to submit to strict government oversight and carry out sweeping reorganization plans.

G.M. has not said how it will respond if the federal loans are not forthcoming. It is spending more than \$2 billion in cash
each month, and is close to falling below the minimum level of cash needed to operate.

Without immediate federal assistance, G.M. would be in danger of not paying its suppliers, employees and creditors, and
could miss interest payments on its outstanding debt. Failure to pay creditors, for example, could result in legal actions
leading to a forced bankruptcy filing.

``I wouldn't like to speculate what would unfold, but suffice it to say the survival of the company as we know it would be
highly questionable if we don't get some bridge loan,'' G.M.'s vice chairman, Robert Lutz, said in an interview on Monday.

The bill would also give the government warrants to take an equity stake in the automakers. It would limit executive pay,
bar golden-parachute severance packages and prohibit the paying of shareholder dividends while the emergency government
loans were outstanding.

The bill would require the companies and their stakeholders, including creditors, labor unions and dealers to agree on
sweeping reorganization plans that would lead to long-term financial viability. If they failed to agree, the auto czar would
be able to impose a plan, and could also force the companies into bankruptcy if they failed to meet requirements.

The plan seeks to save the auto industry from what one senior White House official called ``30 years of slow suicide.''

The bill sets a March 31 deadline for the automakers to produce long-term viability plans, but it is not certain how the
auto czar would determine viability. Joel Kaplan, the deputy White House chief of staff, said that ``simply stated, it's
that the firm will have a positive value going forward when you take into account all of its costs.''

Those costs include health care, pensions, salaries and research and development on new technologies, and depending on how
they are accounted for, the companies -- or the auto czar -- could potentially tinker with the meaning of ``viable.''
Mr.~Kaplan said the White House goal was ``a bridge to either fundamental restructuring, or bankruptcy.''

The bill would require the automakers to seek permission from the auto czar for any business transaction of \$100 million or
more. Congressional Democrats said that provision was intended specifically to prevent the companies from taking any steps
that would result in American manufacturing jobs moving overseas.

But with overseas markets presenting better profit opportunities for the automakers these days, the Democrats' political
goal of preserving jobs, and the overarching goal of the rescue legislation -- to return the automakers to profitability --
could be at odds, with the companies discouraged from seeking the most profitable markets.

The House-approved auto bailout measure would also grant federal judges a cost-of-living increase and would provide federal
guarantees for financial deals that some major transit agencies are in danger of defaulting on in part because of the credit
crisis.

\section{It May Be Time to Think About Buying a House} 

Five or 10 years from now, when the financial crisis has ended and housing prices are up smartly once more, we will look in
the rearview mirror and realize that we missed a golden age for first-time home buyers.

Then, everyone who sat on their down payment savings accounts for a few years too long will kick themselves for not taking
advantage of what may turn out to be the buying opportunity of a lifetime for those who can qualify for a mortgage.

Unfortunately, we do not know when this golden age will begin, because we will be able to identify a bottom to the housing
market only with the benefit of
hindsight\index{hindsight}\hypertarget{hindsight}{}\footnote{\textbf{hindsight}:$[$\textprimstress haindsait$]$. \textit{n}.
(步枪的)表尺;后知之明, 事后的认识.\hyperlink{hindsight}{\textasciicircum}}. But as it does with the stock market, the moment
will probably arrive when everyone is feeling the most
pessimistic\index{pessimistic}\hypertarget{pessimistic}{}\footnote{\textbf{pessimistic}:$[$\textsecstress
pesi\textprimstress mistik$]$. \textit{adj}. 悲观的\hyperlink{pessimistic}{\textasciicircum}}.

That moment is certainly getting closer. Housing prices have fallen drastically from their peak levels in many areas of the
country. Rates on 30-year fixed-rate mortgages are already close to 5.5 percent, and this week there were suggestions that
the federal government might try to drive them down to 4.5 percent, a truly incredible figure to be able to lock in for
three decades.

Meanwhile, first-time home buyers have the same advantage they have always had, which is that they do not have to sell their
old place before buying a new one. That is an added advantage in areas where many available houses simply are not moving,
because the people trying to sell them will not be bidding against you.

If you're hoping for a recovery in the housing market, you ought to be cheering on the first-time home buyers. When they
purchase homes, their sellers are free to move on or move up, stimulating further sales.

But if you are a potential first-time buyer yourself, or lending or giving the down payment to one, you are probably as
frightened as you are tempted by all the ``For Sale'' signs that have become ``On Sale'' signs. So let's quickly review some
of the still-grim pricing data in certain areas -- and consider the reasoning offered up by first-time buyers who have
forged ahead anyhow.

As is always the case with real estate, much depends on location. One study, ``The Changing Prospects for Building Home
Equity,'' tries to predict where today's first-time buyers in the 100 biggest metropolitan areas may actually have less home
equity by 2012 as a result of continued price declines. The verdict was that buyers in 33 of the markets could see a decline
by 2012, including potential six-figure drops on an average home in the New York City, Los Angeles, San Francisco and
Seattle metropolitan areas.

This is obviously scary. (I've linked to the study, a joint effort of the Center for Economic and Policy Research and the
National Low Income Housing Coalition, from the version of this article at nytimes.com/yourmoney.) It's worth noting,
however, that these predictions came before the government made its most recent move to reduce borrowing costs.

Also, the price projections in the study are based, in part, on the fact that the ratio of purchase prices to annual rents
is still higher in many areas than the historical average, which is roughly 15 times rents. While past figures may well have
some predictive value, I have never been convinced that first-time buyers compare a home that they could own and one that
they would rent in purely or even primarily economic terms.

When Jaime and Michael Proman moved this fall to Minneapolis, his hometown, from New York City, they
craved\index{crave}\hypertarget{crave}{}\footnote{\textbf{crave}:$[$kreiv$]$.
  \textit{vt}. 渴望\hyperlink{crave}{\textasciicircum}} a different sort of life after two years together in a
450-square-foot studio apartment. ``We didn't want a sterile apartment feel,'' said Mr.~Proman, who is 28 (his wife is 26).
``We wanted something that was permanent and very much a reflection of us.''

The fact is, in many parts of the country there are few if any attractive rentals for people looking to put down roots and
enjoy the sort of amenities they may spot on cable television home improvement shows. Comparing a rental with a place that
you may own seems almost pointless in these situations, especially for those who are now grown up enough to want to make
their own decisions about d\'ecor without consulting the landlord.

Still, for anyone feeling the urge to buy, a number of practical considerations have changed in the last year or two. The
basics are back, like spending no more than 28 percent of your pretax income on mortgage payments, taxes and insurance. Even
if a lender does not hold you to this when you go in for preapproval, you should hold yourself to it.

You will also want to start now on any project to improve your credit score because it may take several months to get it
above the 720 level that qualifies you for many of the best mortgage rates.

John Ulzheimer, president of consumer education for credit.com, a consumer credit information and application site, suggests
starting to pay down and put away credit cards months before you apply for a loan. That is because the credit scoring system
could penalize you if you use a lot of credit each month, even if you always pay in full. Also, check your three credit
reports (it's free) at annualcreditreport.com and dispute errors.

While no one can easily predict the likelihood of losing a job, Friday's startling unemployment figures suggest the need for
caution if you think you might be vulnerable. A. C. Panella, who teaches communications at Pasadena City College in
California, waited until she had a tenure-track job before buying a home in the Highland Park section of Los Angeles with
her partner, Amy Goldman, a lawyer for a nonprofit organization. ``We could afford the mortgage payment on one salary, were
something to come up,'' Ms.~Panella, 31, said. ``It's really about being able to stay within our means.''

For many first-time home buyers, that philosophy stretches to the down payment, too. Ms.~Panella and her partner put down 20
percent when they bought their home in September, as did the Promans when they bought their home in the Lowry Hill
neighborhood of Minneapolis.

Alison Nowak, 29, put just 3 percent down on a Federal Housing Administration-backed loan last month when she and her
partner, Lacey Mamak, bought a \$149,900, 800-square-foot home several miles south of where the Promans live. ``Anything
that is an opportunity also has a bit of risk,'' she said. Her house was in foreclosure before a plumber bought it and fixed
it up. ``One way we mitigated\index{migigate}\hypertarget{migigate}{}\footnote{\textbf{migigate}:$[$\textprimstress
  mitieit$]$. \textit{vt}. 使镇静; 使缓和, 减轻(病情), 平息(怒气)\hyperlink{migigate}{\textasciicircum}} it was that we
bought a really tiny house in a very good neighborhood.''

One other strategy might be to buy new instead of used. Ian Shepherdson, chief United States economist for the research firm
High Frequency Economics, says he believes that a steep drop-off in inventory of new homes is coming soon, thanks to a rapid
decrease in home builder activity.

Since prices generally soften in the winter, it may make sense to start looking seriously once the mercury bottoms out. ``If
you look at new developments next spring, you may not have the choice you thought you would have or be in the bargaining
position you thought you would be,'' Mr.~Shepherdson said. Also, if you wait after June 30, you will miss out on a \$7,500
federal tax credit for income-eligible first-time home buyers that works like an interest-free loan.

Finally, allow yourself to consider how it would feel if you bought and then prices dropped another 10 or 15 percent. It
might not bother you if you plan to stick around. Plenty of people seem to be making a longer commitment to their homes.
According to a survey that the National Association of Realtors released last month, typical first-time buyers plan to stay
in their home 10 years, up from 7 last year.

Perhaps people are more aware that they will not be able to build equity as rapidly as others did in the real estate boom.
Or they simply have more confidence in hard, hometown assets now than in other markets.

``We wouldn't let another decline bother us,'' said Michael Proman. ``You can never time a bottom. This is a long-term
investment for us, and it truly is the best investment we have in our portfolio right now.''

\section{Japanese Companies Still Invest in Themselves}

SAKAI, Japan -- Despite the rapidly slowing economy, an army of
cranes\index{crane}\hypertarget{crane}{}\footnote{\textbf{crane}:$[$krein$]$. \textit{n}. 鹤,起重
  机.\hyperlink{crane}{\textasciicircum}} still moves busily above the archipelago of factories that Sharp is building in
this gritty\index{gritty}\hypertarget{gritty}{}\footnote{\textbf{gritty}:$[$\textprimstress riti$]$. \textit{adj}. 多砂的,
  粗砂质的, $[$俗$]$有牙尘的, 含沙的; 砂砾般的; 勇敢的, 坚韧不拔的\hyperlink{gritty}{\textasciicircum}} port.

The \$10 billion complex, row upon row of hangar-size buildings, will produce up to 13 million flat-panel LCD televisions a
year by 2010.

If consumer demand does not rebound by then -- and if prices for sets using liquid-crystal display do not stop falling --
industry analysts say the project could end up being little more than the world's most expensive industrial art
installation. But the Japanese television maker calls it something else: one of the keys to its survival, particularly in
hard times.

``We need to take a longer-term view,'' said Nobuyuki Sugano, an executive at Sharp. ``If other companies slow down
spending, we can stay ahead.''

Across the globe, companies are battening down the hatches -- reducing spending, laying off workers and pulling back on
apparent luxuries, like research and development and expansion. In the United States, many seemed to support letting the
American automobile industry collapse under the weight of its own
lethargy\index{lethargy}\hypertarget{lethargy}{}\footnote{\textbf{lethargy}:$[$\textprimstress le\texttheta\schwa d\yogh
  i$]$. \textit{n}. 嗜眠症 ; 沮丧; 冷淡; 不活泼\hyperlink{lethargy}{\textasciicircum}}.

Of course, Japanese companies are also cutting back -- on Wednesday, Sony announced it would eliminate 8,000 jobs. But,
armed with the lessons of their past, many Japanese companies are cutting back less than their competition, investing
instead for the day the downturn ends, however long that takes to happen.

``Unless our sales dry up completely, we have to continue investing,'' said Kumiko Makino, a spokeswoman for Sanyo Electric,
which has refused to cut investment in new battery and solar panel factories. ``If we stop, our rivals and competitors will
quickly catch up.''

That urgency stems from the bitter lessons of the
stagnant\index{stagnant}\hypertarget{stagnant}{}\footnote{\textbf{stagnant}:$[$\textprimstress st\ae n\schwa nt$]$.
  \textit{n}. 停滞\hyperlink{stagnant}{\textasciicircum}} 1990s. Low on cash, Japanese companies cut back on new factories
and development, only to lose ground to hungry Taiwanese and Korean competitors.

While it is too early for numbers to be available, many economists and industry analysts say Japanese companies have so far
maintained higher levels of investments in production, research and development than companies in other countries.

Instead of huge layoffs or cuts in operations, companies here are cutting part-time staff members. (Layoffs of full-time
workers remain taboo\index{taboo}\hypertarget{taboo}{}\footnote{\textbf{taboo}:$[$t\schwa\textprimstress
  bu\textlengthmark$]$. \textit{n adj}. 【宗】禁忌; 忌讳, 戒律;禁忌的, 忌讳的, 禁止的\hyperlink{taboo}{\textasciicircum}}.)
Companies are also delaying or canceling fewer new factories than elsewhere.

One reason is that Japanese companies have war chests of cash built up during Japan's recovery earlier this decade. Another
is that unlike in the United States, shareholders lack the power to demand that cash be paid out as dividends. Indeed, if
Japan's powerful manufacturing sector has a secret to its success, it may be this willingness to reinvest a big share of
profits back into new plants and research.

Japan's drive to build bigger, more advanced factories fueled an industrial construction boom that propelled the economic
recovery earlier this decade. It also equipped the nation with the most advanced factory production lines to try to defend
its technological lead over the rest of Asia.

Japanese innovation also helped keep American stores and showrooms stocked with ever cheaper and more sophisticated gadgets
and vehicles.

``Japan sees its future as more dependent on capex than Americans or Europeans do,'' said Robert Feldman, an economist at
Morgan Stanley in Japan, using the industry jargon for ``capital expenditure,'' investment in new factories and equipment.

Innovation grew from necessity, too. Mr.~Feldman noted that with Japan's shrinking population, companies are more likely to
try to fill the gaps by investing more heavily in labor-saving machinery, like robots.

To be sure, the global slowdown has hammered Japan's corporate profits and sent its \$5 trillion economy, the world's
largest after the United States, into recession. And economists say harder times lie ahead, with America's crucial Christmas
shopping season looking to be one of the weakest in memory.

That has led to spending cuts. Toyota, which earlier this month predicted its first annual earnings decline in nine years,
has said it will cut capital spending 5.4 percent this year. Blue-chip companies including Fujitsu and Canon have also
announced cuts in capital expenditures.

Meanwhile, Sony, which announced job cuts and that it was reducing its electronics investment by a third, has become the
General Motors of Japan. Creator of the Walkman and PlayStation, the company lost its reputation as an innovator to
competitors like Apple and Nintendo. At the same time, it is being challenged on price by rivals from China and South Korea
for cheaper goods.

Over all, government figures released last month reported that corporate spending on factories and other facilities fell 2
percent in the three months ending September from the previous quarter, for its third consecutive quarterly decline. The
declines were a major factor in Japan's sliding into recession.

Tetsufumi Yamakawa, chief Japan economist at Goldman Sachs, estimates that such investment will shrink 1.8 percent this year
and 2.1 percent in 2009 before growing slowly.

``The pace of the slowdown in capex has been much sharper than we expected,'' Mr.~Yamakawa said.

Still, Mr.~Yamakawa and other economists say they expect corporate Japan to keep outspending America on new factories, even
during the current downturn.

Last year Japan spent 16 percent of its gross domestic product on new factories and production, Mr.~Yamakawa said. While
that is down from Japan's high-growth 1980s, when it spent closer to 25 percent, the figure is still high when compared with
11 percent by the United States, he said.

But Japan also knows all too well the dangers of overcapacity. A crucial cause of the deflation, chronic price declines,
that racked Japan's economy in the 1990s was an oversupply of production capacity, which forced companies to keep cutting
prices. Also, electronics industry analysts warn that if the global consumption keeps falling, even Japanese companies will
eventually run out of cash.

``They can't keep this level of spending up forever,'' said Koya Tabata, an electronics analyst in Tokyo for Credit Suisse.
But Mr.~Tabata said that for now, corporate Japan continues to outspend Asian rivals, like Taiwan and South Korea.

Nowhere is that still formidable appetite for factory investment more apparent than along the shores of western Japan's
Osaka Bay. This former rust-belt region has seen a boom in construction of large electronics and television plants, earning
it the nickname Panel Bay.

Panasonic is building what it calls the world's largest plasma TV factory in Amagasaki, a \$2.9 billion plant that will
produce 12 million TVs a year when finished next year. Sanyo is also expanding two plants for lithium-ion batteries, the
type used in laptops and cellphones.

Nor has the army of busy construction cranes missed a beat at the largest of the Panel Bay projects, Sharp's complex on the
site of an abandoned steel furnace. Despite reducing its overall capital budget this year by 10 percent, to \$3.2 billion,
Sharp says it is not slowing construction of the complex, which will also make solar panels. Sharp expects global demand for
flat-panel TVs and solar panels to remain firm even during the global downturn, as global consumers replace their old tube
TVs and embrace renewable energy.

When opened, the complex is expected to employ 10,000 people and add \$11 billion a year in new economic activity. But there
are growing fears in the city of Sakai itself that the complex could go the way of the steel furnace that preceded it. Many
here are afraid the current economic downturn might end the city's brief revival before the plant even opens.

``Sharp tells us not to worry, so we remain hopeful,'' said Takayuki Kanemoto, manager of Sakai city hall's investment
promotion division. ``But we can't even tell anymore what will happen next week, much less in two years.''

\section{Senate Abandons Automaker Bailout Bid}

WASHINGTON -- The Senate on Thursday night abandoned efforts to fashion a government rescue of the American automobile
industry, as Senate Republicans refused to support a bill endorsed by the White House and Congressional Democrats.

The failure to reach agreement on Capitol Hill raised a specter of financial collapse for General Motors and Chrysler, which
say they may not be able to survive through this month.

After Senate Republicans balked at supporting a \$14 billion auto rescue plan approved by the House on Wednesday,
negotiators worked late into Thursday evening to broker a deal, but deadlocked over Republican demands for steep cuts in pay
and benefits by the United Automobile Workers union in 2009.

The failure in Congress to provide a financial lifeline for G.M. and Chrysler was a
bruising\index{bruise}\hypertarget{bruise}{}\footnote{\textbf{bruise}:$[$bru\textlengthmark z$]$. \textit{n vt}. 青肿,伤
  痕.\hyperlink{bruise}{\textasciicircum}} defeat for President Bush in the
waning\index{waning}\hypertarget{waning}{}\footnote{\textbf{waning}:$[$\textprimstress weini\engma$]$. \textit{adj}. (月亮)渐
  亏的, 逐渐减弱或变小的\hyperlink{waning}{\textasciicircum}} weeks of his term, and also for President-elect Barack Obama,
who earlier on Thursday urged Congress to act to avoid a further loss of jobs in an already deeply debilitated economy.

``It's over with,'' the Senate majority leader, Harry Reid of Nevada, said on the Senate floor, after it was clear that a
deal could not be reached. ``I dread\index{dread}\hypertarget{dread}{}\footnote{\textbf{dread}:$[$dred$]$.
  \textit{adj}. 恐惧,害怕\hyperlink{dread}{\textasciicircum}} looking at Wall Street tomorrow. It's not going to be a
pleasant sight.''

Mr.~Reid added: ``This is going to be a very, very bad Christmas for a lot of people as a result of what takes place here
tonight.''

The Republican leader, Senator Mitch McConnell of Kentucky, said: ``We have had before us this whole question of the
viability of the American automobile manufacturers. None of us want to see them go down, but very few of us had anything to
do with the dilemma\index{dilemma}\hypertarget{dilemma}{}\footnote{\textbf{dilemma}:$[$di\textprimstress
  lem\schwa\textsecstress dai-$]$. \textit{n}. 左右为难的状况, 窘境.\hyperlink{dilemma}{\textasciicircum}} that they have
created for themselves.''

Mr.~McConnell added: ``The administration negotiated in good faith with the Democratic majority a proposal that was simply
unacceptable to the vast majority of our side because we thought it frankly wouldn't work.''

Moments later, the Senate failed to win the 60 votes need to bring up the auto rescue plan for consideration. The Senate
voted 52 to 35 with 10 Republicans joining 40 Democrats and 2 independents in favor. The White House issued said it would
consider alternatives but offered no assurances.

``It's disappointing that Congress failed to act tonight,'' Tony Fratto, the deputy press secretary, said. ``We think the
legislation we negotiated provided an opportunity to use funds already appropriated for automakers, and presented the best
chance to avoid a disorderly bankruptcy while ensuring taxpayer funds only go to firms whose stakeholders were prepared to
make difficult decisions to become viable. We will evaluate our options in light of the breakdown in Congress.''

Immediately after the vote, the administration was already coming under pressure to act on its own to prop up G.M. and
Chrysler, an idea that administration officials have resisted for weeks.

House Speaker Nancy Pelosi and other lawmakers called on the administration to use the Treasury's bigger financial system
stabilization fund to but there may not be enough money left to do so. About \$15 billion remains of the initial \$350
billion disbursed by Congress and Treasury officials have said that money is needed as a backstop for existing programs.

Democrats also immediately sought to blame Republicans for the failure to aid Detroit, while a number of Republicans quickly
blamed the union. But on all sides the usual zest for political jousting seemed absent given the grim economic outlook.

``Senate Republicans' refusal to support the bipartisan legislation passed by the House and negotiated in good faith with
the White House, the Senate and the automakers is irresponsible, especially at a time of economic hardship,'' Ms.~Pelosi
said in a statement.

She added: ``The consequences of the Senate Republican' failure to act could be devastating to our economy, detrimental to
workers, and destructive to the American automobile industry unless the President immediately directs Secretary Paulson to
explore other short-term financial assistance options. Senator George V. Voinovich, Republican of Ohio, and a supporter of
the auto rescue efforts, said: ``I think it might be time for the president to step in.''

So far, the Federal Reserve also has shown no willingness to step in to aid the auto industry, but Democrats have argued
that it has the authority to do so and some said the central bank may have no choice but to prevent the automakers from
bankruptcy proceedings that could have ruinous ripple effects.

G.M. and Chrysler issued statements expressing disappointment. G.M. said: We will assess all of our options to continue our
restructuring and to obtain the means to weather the current economic crisis.'' Chrysler said it would: ``continue to pursue
a workable solution to help ensure the future viability of the company.''

Earlier in the day, G.M. confirmed that it had legal advisors -- including Harvey R. Miller of the firm Weil Gotshal \&
Manges --to consider a possible bankruptcy, which the company until now has said would be
cataclysmic\index{cataclysmic}\hypertarget{cataclysmic}{}\footnote{\textbf{cataclysmic}:$[$\textprimstress k\ae t\schwa
  kliz\schwa m$]$. \textit{n}. 地球表面上的巨变(如洪水, 地震等) ; 洪水, 泛滥 ; 政治或社会上的任何巨
  变 ; 渗出, 渗液; 猝变\hyperlink{cataclysmic}{\textasciicircum}} not just for G.M. but for Chrysler and Ford as well. The
rescue plan approved by the House on Wednesday by a vote of 237 to 170 would have extended \$14 billion in loans to the
troubled automakers and required them to submit to broad government oversight directed by a car czar to be named by
Mr.~Bush.

But even before the House vote, Senate Republicans voiced strong opposition to the plan, which was negotiated by Democrats
and the White House. At a luncheon with White House chief of staff, Joshua B. Bolten, they rebuffed his entreaties for
support.

On Thursday morning, Mr.~McConnell dealt a death blow to the House-passed bill, giving a speech on the Senate floor in which
he said that Republican senators would not support it largely because it was not tough enough.

``In the end it's greatest single flaw is that it promises taxpayer money today for reforms that may or may not come
tomorrow,'' Mr.~McConnell said.

Mr.~McConnell, however, held out slim hope for a compromise suggesting that Republicans could rally around a set of
proposals by Senator Bob Corker, Republican of Tennessee, who said that the bill did not set stiff enough requirements for
the automakers.

Mr.~Obama, whose transition team had consulted with Congressional Democrats and the Bush White House on the efforts to help
the automakers, used his opening remarks at a news conference in Chicago on Thursday to urge Congress to act.

``I believe our government should provide short-term assistance to the auto industry to avoid a collapse while holding the
companies accountable and protecting taxpayer interests,'' he said. But in Washington, there was little appetite among
Senate Republicans for yet another multibillion-dollar bailout of private companies. Still, with the Democrats and the White
House eager to reach a deal, Mr.~Corker's proposal became the subject of intense negotiations well into the evening.

Under his plan, the automakers would have been required by March 31 to slash their debt obligations by two-thirds -- an
enormous sum given that G.M. alone has more than \$60 billion in outstanding debt.

The automakers would also have been required to cut wages and benefits to match the average hourly wage and benefits of
Nissan, Toyota and Honda employees in the United States.

It was over this proposal that the talks ultimately deadlocked with Republicans demanding that the automakers meet that goal
by a certain date in 2009 and Democrats and the union urging a deadline in 2011 when the U.A.W. contract expires.

G.M. and Chrysler had already agreed to carry out sweeping reorganization plans in exchange for the help.

The negotiations over Mr.~Corker's proposals broke up about 8 p.m. and Mr.~Corker left to meet with Republican senators to
brief them on the developments. The Republicans emerged from their meeting an hour later having decided they would not agree
to a deal. Several of them blamed the autoworkers union.

``It sounds like the U.A.W. blew it up,'' said Senator David Vitter, Republican of Louisiana.

Senator Richard C. Shelby of Alabama, the senior Republican on the banking committee and a leading critic of the auto
bailout proposal, said: ``We're hoping that the Democrats will continue to negotiate but I think we have reached a point
that labor has got to give. If they want a bill they can get one.''

The last-ditch negotiations made for a dramatic scene on the first floor of the Capitol, where high-level lobbyists for G.M.
and Ford, as well as Stephen A. Feinberg, the reclusive founder of Cerberus Capital Management, the private equity firm that
owns 80 percent of Chrysler, gathered with senators and legislative staff in a conference room.

A Democratic aide said that there were no lobbyists present who represented Chrysler.

At times, various participants huddled in corners of the cavernous hallway outside the conference room, shielding their
documents and whispering into their cellphones, as a throng of reporters and photographers waited nearby. Some of the
lobbyists and banking committee staff members huddled by two towering windows, looking out on a frigid rain that had been
falling all day.

Markets reacted quickly in Asia. In Japan, the Nikkei 225 index extended mild morning losses after the proposal failed.

\section{Why is Steve Jobs Skipping MacWorld?}

Apple's true believers are being put to the test. Late Tuesday the company announced that Steve Jobs would not be giving the
keynote address at the annual Macworld Conference and Expo. Apple also said that Phil Schiller, its top marketing guy, would
be giving the keynote this year, and that this would be the last Macworld in which Apple would participate.

Jobs has battled pancreatic cancer and has been looking exceptionally thin since the summer. Rumors that he'd be skipping
the event had circulated for days. Still, the announcement itself was about as shocking as hearing that Barack Obama would
be skipping the
Inauguration\index{Inauguration}\hypertarget{Inauguration}{}\footnote{\textbf{Inauguration}:$[$i\textsecstress
  n\openo\textlengthmark ju\textprimstress rei\esh\schwa n$]$. \textit{n}. 就职典礼; $[$美$]$总统就职典礼; 开幕仪式, 落成
$[$成立$]$典礼; 开创\hyperlink{Inauguration}{\textasciicircum}} and sending Joe Biden in his stead.

Steve Dowling, an Apple spokesman, deflected any questions about Jobs's health. When asked if Jobs canceled because of
illness, Dowling said, ``Phil is giving the keynote because this is Apple's last year in the show and it doesn't make sense
for us to make a major investment in a trade show we will no longer be attending.'' Asked again about Jobs's health, Dowling
gave a similar answer, never using the word ``Jobs'' or anything related to the state of his health.

It's difficult to find a company of Apple's caliber whose fortunes are so closely tied to the health of its CEO. Apple is
Jobs and Jobs is Apple. Unless he makes a public appearance, it's likely that the news will continue to hammer Apple's
stock, which took a beating Monday after analysts downgraded it. (It dropped over 2.5\% within a few hours of the
announcement.) A report by the NPD Group, which tracks retail sales, showed that Apple store sales declined 1\% in November,
versus a year ago, even at a time when PC sales increased 2\%. Analysts, extrapolating to the pending post-holiday
Depression, when No One Will Buy Anything Ever Again, deemed this significant. If people stop buying stuff, that goes double
for expensive stuff. And Apple occupies the
premium\index{premium}\hypertarget{premium}{}\footnote{\textbf{premium}:$[$\textprimstress primj\schwa m$]$. \textit{adj}. 特
  佳的, 特级的\hyperlink{premium}{\textasciicircum}} space in the computing world. Jobs has famously and consistently
refused to dance the price-cutting limbo with PC makers. As recently as October he told analysts he wasn't ``tremendously
worried'' that recession-wary customers would flock to cheaper, \$300 PCs.

Apple fans had been hoping that Jobs would unveil a ``netbook'' at the upcoming Macworld the first week of January. Two
years ago, at the same conference, he announced the iPhone, which has become the hottest thing in the computer world. Tens
of millions of people will own one by the end of next year; before the recession hit, some analysts predicted that as many
as 45 million folks would buy one. (That figure may hold as Apple moves into Wal-Mart at the end of the month.) Even at the
current rate, 1 billion applications for the device could be downloaded by the middle of next year. That alone could
generate as much as \$1 billion in new revenues from applications; never mind how many more songs, movies and TV shows Apple
will sell from the iTunes store to all those new iPhone users.

Of course, Jobs has been staging his own launch events with greater frequency during the past few years. The successor to
the iPhone, the iPhone 3G, was unveiled this summer at a developers' conference. The faithful are praying that Tuesday's
announcement is exactly what Apple says it is, and not at all what it looks like. 

\section{Ford Family Values: Why the Automaker Wants to Go It Alone}

Last Thursday night, as General Motors and Chrysler representatives huddled with Senate leaders trying, in vain, to hammer
out a financial-aid deal, a representative for another big automaker sat in an adjacent room. That's just where Ford wanted
to be, near enough to have a voice but far enough removed to escape the ``cram down'' of equity, as Republican Senator Bob
Corker of Tennessee called the shareholder
dilution\index{dilution}\hypertarget{dilution}{}\footnote{\textbf{dilution}:$[$dai\textprimstress
  lju\textlengthmark\esh\schwa n\textsecstress di\textprimstress l-$]$. \textit{n}. the act of diluting or state of being
  diluted.稀释; 冲淡.\hyperlink{dilution}{\textasciicircum}} that the Senate leaders were crafting. While the White House is
now figuring out the best way to rush billions in much-needed bridge loans to the automakers, one thing seems almost
certain: Ford Motor Co.~will make sure that any deal leaves the Ford family's four-generation grip on the company
intact\index{intact}\hypertarget{intact}{}\footnote{\textbf{intact}:$[$in\textprimstress t\ae kt$]$. \textit{adj}. 未经触动
  的, 原封不动的, 完整无损的\hyperlink{intact}{\textasciicircum}}.

Alan Mulally, Ford CEO, has made it clear to Congress and the media that unlike GM and Chrysler, Ford is not seeking a
bridge loan to get through the current economic crisis. Instead, Ford asked for a backup line of credit that could be used
if the economic downturn continues for an extended period. ``We are more balanced. We are more efficient. We are more
global, and we are more focused. In short, we are on the right path to become a profitable, growing company,'' Mulally said
during his congressional testimony earlier this month. (See TIME's top 10 financial collapses of 2008.)

But Ford's go-it-alone strategy reflects more than just confidence in its own viability. Observers around Detroit suggest
that the Ford family's continuing control of the company has surely influenced the decision to not seek federal assistance.
``Any dilution of equity has to be an issue for the family, and also the loss of dividends,'' says Brad Coulter, a
specialist in bankruptcy and loan workouts with O'Keefe \& Associates of Bloomfield Hills, Mich. (Any dividend payment would
likely need the approval of a new ``car czar,'' which the White House might appoint if it moves to provide aid.) Alan Baum,
an analyst who follows the industry for the Planning Edge in Birmingham, Mich., agrees that the Ford family's control of the
auto giant was an issue. ``Sure it was,'' he says. Ford spokesman Oscar Suris denies that Ford's decision not to seek
federal assistance was influenced by such concerns. (See the 50 worst cars of all time.)

Should the White House provide funds from the Wall StreetCbailout fund (known as TARP) for a bridge loan, Ford would likely
gain some access to credit. Ford would also stand to benefit from United Auto Workers wage and benefit concessions in the
Senate negotiations, which the White House might look to duplicate as part of any assistance agreement. If GM and Chrysler
wind up in bankruptcy court early next year -- a distinct possibility, even if a bridge loan materializes; it is also
something the Bush Administration might push on the two automakers as a condition for any assistance now -- Ford would be
the only one of the Big Three to escape the court's restrictions, and the only one whose retail image would not be tarnished
by bankruptcy. Its market appeal, too, might even be strengthened should Ford be the only one of the Big Three not to get
taxpayer money.

Not that Ford's finances aren't stressed. Instead, its biggest advantage over its beleaguered rivals is that it benefited
greatly from a decision to mortgage all its assets more than two years ago, raising more than \$19 billion in cash and \$11
billion in credit lines. Even the company's famous blue oval logo was pledged as collateral for what Mulally has described
as ``the world's biggest mortgage.'' That cash gives Ford, and the Ford family, the
leeway\index{leeway}\hypertarget{leeway}{}\footnote{\textbf{leeway}:$[$\textprimstress li\textlengthmark wei$]$. \textit{n}.
  room for free movement within limits, as in action or expenditure. 余地; 可允许的误差; 机动时
  间.\hyperlink{leeway}{\textasciicircum}} to play the crisis differently than its Detroit neighbors.

The Ford family currently owns less than 3\% of the company's common shares, but it exerts control through its Class B
stock, which is reserved for family members and has been ever since the company first went public in its landmark IPO back
in 1956. The family shored up its control in 2000 through another well-timed transaction, which gave the company's
shareholders a onetime dividend of \$20 per share in cash or new stock of equal value. The payout amounted to about \$10
billion in cash dividends, but it also shored up the Ford family stake in the company via a distribution of additional B
shares, which have 16 votes to every one vote for ordinary common shares.

Two big pension funds, TIAA-CREF and the California Public Employees' Retirement System, did criticize the 2000 plan,
asserting that the structure of Ford's proposal unfairly enhanced the voting rights of class B shareholders at the expense
of stockholders. Nevertheless, Ford's voting shareholders quickly approved the transaction.

Long-term family-owned automakers also appear to have a competitive advantage over their publicly traded counterparts, which
are under intense pressure to show positive quarterly results. Some of the world's most stable automakers -- Germany's BMW,
France's Peugot and Japan's Toyota and Honda -- all operate under corporate structures in which the founding family has a
significant stake. The companies, which often need years to nurture new products, new technology and new markets, seem to
benefit from the longer term outlook that comes with family control.

And throughout the tortured Detroit bailout saga, that fact alone may be putting a small smile on the face of Ford's family
members.

\section{China Said to Be Blocking Web Sites}

HONG KONG -- The Chinese government has quietly begun preventing access again to Web sites that it had stopped blocking
during the Olympic Games in Beijing in August, Internet experts said on Tuesday.

Liu Jianchao, a spokesman for China's Foreign Ministry, said at his twice-weekly news conference on Tuesday in Beijing that
the Chinese government had a right to censor Web sites that violated the country's laws. He added that ``some Web sites,''
which he did not identify, had violated China's law against secession by suggesting that there were two Chinas -- a
reference to the Beijing government's longstanding position that mainland China and Taiwan form a single China.

``I hope that the Web sites in question will be able to self-regulate, and not do things that will violate Chinese law, and
for the sake of both sides, develop conditions for Web site cooperation,'' Mr.~Liu said, according to a transcript posted on
the Foreign Ministry's Web site.

Rebecca MacKinnon, a specialist in Internet issues at Hong Kong University, said that the Chinese authorities had recently
resumed blocking access to her blog from mainland computers. ``It does appear that in the last week a lot of things got
reblocked that were unblocked during the Olympics,'' she said, adding, ``I have not written about the two Chinas issue
arguably in the past year; it is not what I focus on.''
The government's action comes as the Chinese economy has slowed sharply this autumn. Chinese leaders have begun cautioning
about potential risks to social stability caused by high unemployment. Chinese officials have followed a pattern over the
years of censoring the Internet more tightly at times of economic or political stress.

Asiaweek, a Hong Kong-based publication, reported this week that the Chinese-language version of its Web site, as well as
those of the BBC, Voice of America and Ming Pao, a Hong Kong newspaper, had been blocked since early December.

On its Web site, the BBC reported that a number of foreign sites had been blocked and said it ``expressed disappointment at
the apparent reinstatement of the ban'' since the Olympics. But at the news conference, Mr.~Liu defended China's monitoring
of the Internet by saying that other countries also restricted access to some Web sites.

The Chinese government ``needs to do the required management of Web sites based on the law, just as what other countries are
doing,'' he said. In recent days, Britain and Australia have moved to limit distribution of child pornography over the
Internet. Germany requires that search engines not link to sites linked to Nazi activity.

But Ms.~MacKinnon noted that in contrast to other countries the Chinese government defines crime very broadly, imposes
censorship with little if any explanation and provides no process for operators of blocked Web sites to appeal censorship
decisions. She added that even when entire Web sites are not blocked, the Chinese government still sometimes limits certain
keyword searches.

\section{The Year of the Simpler Gadget}
THE National Bureau of Economic Research hardly stunned\index{stun}\hypertarget{stun}{}\footnote{\textbf{stun}:$[$st\pwedge
  n$]$. \textit{vt}. to render unconscious, as by a heavy blow or fall.打昏, 使晕
  眩.[美]胡桃\hyperlink{stun}{\textasciicircum}} the nation this month when it announced that the United States had been in
recession since December 2007.

And, as it turns out, the buyers of consumer electronics could very well have been a leading economic indicator. Over the
last year, they chose to buy two inexpensive and simple products, the Wii and the Flip, over competing gadgets bristling
with more features.

Nintendo has sold more than 30 million Wii game consoles since they were introduced two years ago. The machine is still
luring\index{lure}\hypertarget{lure}{}\footnote{\textbf{lure}:$[$lju\schwa$]$. \textit{vt}. to tempt or attract by the
  promise of some type of reward.引诱,诱惑.\hyperlink{lure}{\textasciicircum}} shoppers: lines of buyers still form on
Sunday mornings outside electronics stores. Best Buy put the Wii, not big-screen high-definition TVs, on the cover page of
its Sunday circular last week, in its bid to get resistant holiday shoppers into the store.

The machine is dimwittedly\index{dimwitted}\hypertarget{dimwitted}{}\footnote{\textbf{dimwitted}:$[$\textprimstress
  dimwitid$]$. \textit{adj}. 愚蠢的; 愚笨的\hyperlink{dimwitted}{\textasciicircum}} simple. The console itself is hardly
bigger than a DVD. It lacks the deep rich graphics, the
rumbling\index{rumble}\hypertarget{rumble}{}\footnote{\textbf{rumble}:$[$\textprimstress r\pwedge mbl$]$. \textit{n}. to
  make or cause to make a deep resonant sound.辘辘声; 隆隆声\hyperlink{rumble}{\textasciicircum}} sound and many of the
violent games of the Microsoft Xbox 360. But at \$250, it is outselling the more expensive Xbox 360 and the Sony PlayStation
3 combined by almost 2 to 1.

The \$130 Flip camcorder is also simple, and two to three times cheaper than camcorders made by Sony or JVC that have
optical zoom, an optical viewfinder and special effects. The original Flip didn't even have a headphone jack. Revenue at
Pure Digital Technologies, its manufacturer, grew 44,667 percent, the highest rate of any company in Silicon Valley, over
the last five years, according to Deloitte, the business services firm. Pure Digital Technologies says it has sold more than
1.5 million Flips since it unveiled the product line in 2007.

This shift in consumer preference to the cheaper electronic device could well be a reaction to the recession. But it isn't
the same as the consumer suddenly, and consciously, reaching for the house brand of creamed corn instead of the one with the
Jolly Green Giant on the label. It is not just the economics of a shopping-fatigued nation at work here. Consumers found the
simple devices, which don't need instruction manuals to set up and use, more appealing.

That shift in consumer preference could be
ominous\index{ominous}\hypertarget{ominous}{}\footnote{\textbf{ominous}:$[$\textprimstress\openo min\schwa s$]$.
  \textit{adj}. foreboding evil.不吉的; 不祥的.\hyperlink{ominous}{\textasciicircum}}. As the United States enters a
deflationary period, all kinds of companies will have to grapple with the consequences of falling prices. This is nothing
new for electronics makers. Every year, competition and the effects of Moore's Law forced prices down.

The one defense that seemed to work was to offer a new product at the same price as the old one -- but with more features.
The laptops got better graphics, the hard drives spun faster, the cameras picked up more detail, the memory cards held more.

Feature-itis was a disease, but it was better than the affliction known as consumer boredom.

Even the Flip is experiencing some feature creep. It has a popular model that shoots high-definition video. It's still the
smallest HD camcorder, but it has U.S.B. port rechargers and power adapters, fast forward and rewind and four times as much
memory as the original. Wii is still aimed at the market that Microsoft and Sony neglected: young children, older people and
others who never played video games. But it is selling add-ons like the Wii Fit, a souped-up bathroom scale that allows a
person to play skiing games, balance contests and musical play-alongs.

Apple, innovator of business models as much as it is an innovator of electronic
geegaws\index{geegaw}\hypertarget{geegaw}{}\footnote{\textbf{geegaw}:$[$\textprimstress d\yogh i\textlengthmark
  \openo\textlengthmark$]$. \textit{adj}. 虚华而无价值的\hyperlink{geegaw}{\textasciicircum}}, may have found a solution to
the problem of simple products becoming more complex. The Apple iPhone is one of the easiest-to-use devices ever created. At
\$300, plus a two-year contract that quickly pushes the real price to \$1,800, it is hardly in the
thrift\index{thrift}\hypertarget{thrift}{}\footnote{\textbf{thrift}:$[$\texttheta rift$]$. \textit{n}. wisdom and caution in
the management of money. 节约, 节俭; $[$美$]$繁荣, 兴旺, 健壮\hyperlink{thrift}{\textasciicircum}} class with the Wii and the
Flip. But it is one of the most popular consumer electronics devices of 2008. Apple is expected to sell more than 14 million
of them this year, and it is already the best-selling handset in the United States, according to the market researchers at
the NPD Group.

AS much as it is part of the distinct trend toward the simple, the iPhone is also part of a trend to make a device
versatile\index{versatile}\hypertarget{versatile}{}\footnote{\textbf{versatile}:$[$\textprimstress v\schwa\textlengthmark
  s\schwa tail$]$. \textit{adj}. 多才多艺的\hyperlink{versatile}{\textasciicircum}}. It is a pretty thing, with a sleek
touchscreen that does away with a keyboard. But it is also a hand-held game machine and a musical instrument that plays
cowbells or imitates an ocarina. It's clearly an entertainment device, one that can identify the song playing in a movie or
find friends on a map.

While it is not clear that mainstream electronics manufacturers have caught on, some scrappy start-ups have noticed its
utility. One of them, Sonos, has turned the iPhone into a pretty nifty remote control for managing music on Sonos's
whole-house entertainment system. (The application can be downloaded free from the Apple AppStore.) The iPhone taps into a
home's wireless network to control the wireless entertainment system in multiple rooms.

John MacFarlane, the Sonos chief executive, says creation of the software that makes the iPhone a Sonos controller lifted
the company's sales by 20 percent in November. ``In this economy,'' he noted.

The company gave up some revenue -- a regular Sonos controller is about \$300 -- but the new device exposed the
entertainment system to a new audience and thus expanded the market.

Sonos isn't interested in anything other than music, but a versatile little device that you never let out of your reach
could also manage burglar\index{burglar}\hypertarget{burglar}{}\footnote{\textbf{burglar}:$[$\textprimstress
  b\schwa\textlengthmark l\schwa$]$. \textit{n}. (夜间闯入室内的)夜盗, 窃贼\hyperlink{burglar}{\textasciicircum}} alarms
and heating and cooling systems. ``I think that is the universal remote control of the future,'' Mr.~MacFarland said. ``And
that's the direction we are headed.''

Right along with stingier consumers.


\pagebreak
\printindex

\end{CJK*}
\end{document}
