% LaTeX resume using res.cls
\documentclass[margin,12pt]{res}

\usepackage{config}

%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion



\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf \textsc{Jason Wu}}

% \begin{center}
% \makebox[.5\textwidth][s]{\textsc{Wu Xiaochun}}
% \end{center}

% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{\textsf{\small 10 Parkway Forest Dr. North York, ON M2J 1L3}}
 % \moveleft.5\hoffset\centerline{North York, ON M2J 1L3}
 \moveleft.5\hoffset\centerline{\textsf{\small Tel: (647) 918-9825  Email: \hyperlink{mailto:wuxch2000@gmail.com}{wuxch2000@gmail.com}}}

\begin{resume}
 
\section{\textsc{Objective}}  A position in the field of software development with special 
                interests in telecom or business applications programming, 
                information processing, and Internet technology. 

\section{\textsc{Skill}} 
                C(+5 years), Java(+2 years), C++(+2 years), Database(+2 years Oracle),\\
                Object-Oriented Analysis (OOA),  Object-Oriented Design (OOD), UML\\
                Emacs with Lisp, Tex.

\section{\textsc{Knowledge}} 
\begin{itemize}
    \item Telecom Networks and Technologies
    \item Next Generation Network (NGN), Softswitch
    \item IP Multimedia Subsystem (IMS) of 3GPP
    \item SIP, H.323, H.248 (MGCP) and other related protocols
    \item Internet Knowledge, XML, HTML and related
    \item Project Management Knowledge
    \item Capability Maturity Model (CMM)
\end{itemize}
 
\section{\textsc{Experience}} 
\mytitle{Software Development Leader} \mydate{July 2006 - August 2011}\\
Network Division of ZTE Corporation, China

    \begin{itemize} \itemsep -2pt %reduce space between items
    \item Analysis SIP protocol for ZTE softswitch device\footnote{ZTE is
        one the top 5 largest Telecom equipment and network solution provider in the world
        with more than 30 thousands employees. ZTE Softswitch is a core device of Next
        Generation Network (NGN) which support over million users. And it is one of the
        most successful products of ZTE, as occupies the largest market share in China.
        Even in world Telecom market, our product is also a major device provider.}
    \item Design the inner architecture for protocol module using UML language
    \item Implement protocol module using C language in VxWorks real-time OS
    \item Analysis Operation, Maintenance, Monitoring (OMM) requirements for ZTE softswitch
    \item Database design for OMM
    \item Database tables and procedures development for Oracle Dababase
    \item OMM implement using Java language in Solaris and Linux OS
    \item Guiding junior developer
    \end{itemize}
 
    \mytitle{System Analysis and Design Engineer} \mydate{April 2003 - July 2006}\\
    Network Division of ZTE Corporation, China
     \begin{itemize}  \itemsep -2pt %reduce space between items
     \item System analysis and design for new ZTE VoIP Gateway\footnote{This is ZTE's first type of
         VoIP gateway for telecommunication market which supports up to 7200 lines concurrently,
         integrated in grogram controlled switch. }
     \item Implement stack module of Gateway
     \item Analysis user requirements and protocol
     \item Development Language: C, Java
     \item Environment: Solaris, RMX, Oracle
     \end{itemize} 

    \mytitle{Software Development Engineer} \mydate{April 1999 - April 2003}\\
    Network Division of ZTE Corporation, China
      \begin{itemize}
       \item Develop H.323 protocol module\footnote{This module
           is the core part of ZTE VoIP Gateway which is aimed to enterprise market. ZTE
           VoIP Gateway supports 120 lines concurrently.}
       \item Development Language: C
       \item Environment: Windows NT, Sybase
       \end{itemize} 

\section{\textsc{Education}} 
                \mytitle{Master of Science, Instrument Science Engineering}  \mydate{April 1999}\\
                Southeast University, Nanjing, China \\
                Concentration: Computer Science \\

                \mytitle{Bachelor of Science, Electrical Engineering} \mydate{July 1996}\\
                Nanchang University, Nanchang, China \\
                Concentration: Electrical Machine \\
 
\end{resume}
\end{document}
