\documentclass[12pt,a4paper,onecolumn]{article}
\title{Digest of The New York Times}
\author{The New York Times}
\include{wuxch_config}
\makeindex
\begin{document}
\begin{CJK*}{GBK}{song}
\date{}
\maketitle
\tableofcontents
\pagebreak
\section{More Readers Picking Up Electronic Books}

Could book lovers finally be willing to switch from pages to pixels?

For a decade, consumers mostly ignored electronic book devices, which were often hard to use and
offered few popular items to read. But this year, in part because of the popularity of Amazon.com's
wireless Kindle device, the e-book has started to take hold.

The \$359 Kindle, which is slim, white and about the size of a trade paperback, was introduced a
year ago. Although Amazon will not disclose sales figures, the Kindle has at least lived up to its
name by creating broad interest in electronic books. Now it is out of stock and unavailable until
February. Analysts credit Oprah Winfrey, who praised the Kindle on her talk show in October.

The shortage is providing an opening for Sony, which embarked on an intense publicity campaign for
its Reader device during the gift-buying season. The stepped-up competition may represent a coming
of age for the entire idea of reading longer texts on a portable digital device.

``The perception is that e-books have been around for 10 years and haven't done anything,'' said
Steve Haber, president of Sony's digital reading division. ``But it's happening now. This is really
starting to take off.''

Sony's efforts have been overshadowed by Amazon's. But this month it began a promotional blitz in
airports, train stations and bookstores, with the ambitious goal of personally demonstrating the
Reader to two million people by the end of the year.

The company's latest model, the Reader 700, is a \$400 device with a light and a touch screen that
allows users to annotate what they are reading. Mr.~Haber said Sony's sales had tripled this holiday
season over last, in part because the device is now available in the Target, Borders and Sam's Club
chains. He said Sony had sold more than 300,000 devices since the debut of the original Reader in
2006.

It is difficult to quantify the success of the Kindle, since Amazon will not disclose how many it
has sold and analysts' estimates vary widely. Peter Hildick-Smith, president of the Codex Group, a
book market research company, said he believed Amazon had sold as many as 260,000 units through the
beginning of October, before Ms.~Winfrey's endorsement. Others say the number could be as high as a
million.

Many Kindle buyers appear to be outside the usual gadget-hound demographic. Almost as many women as
men are buying it, Mr.~Hildick-Smith said, and the device is most popular among 55- to 64-year-olds.

So far, publishers like HarperCollins, Random House and Simon \& Schuster say that sales of e-books
for any device -- including simple laptop downloads -- constitute less than 1 percent of total book
sales. But there are signs of momentum. The publishers say sales of e-books have tripled or
quadrupled in the last year.

Amazon's Kindle version of ``The Story of Edgar Sawtelle '' by David Wroblewski, a best seller
recommended by Ms.~Winfrey's book club, now represents 23 percent of total Amazon sales of the book,
according to Brian Murray, chief executive of HarperCollins Publishers Worldwide.

Even authors who were once wary of selling their work in bits and bytes are coming around. After
some initial hesitation, authors like Danielle Steel and John Grisham are soon expected to add their
titles to the e-book catalog, their agents say.

``E-books will become the go-to-first format for an ever-expanding group of readers who are newly
discovering how much they enjoy reading books on a screen,'' said Markus Dohle, chief executive of
Random House, the world's largest publisher of e-books.

Nobody knows how much consumer habits will shift. Some of the most committed bibliophiles maintain
an almost fetishistic devotion to the physical book. But the technology may have more appeal for
particular kinds of people, like those who are the heaviest readers.

At Harlequin Enterprises, the Toronto-based publisher of bodice-ripping romances, Malle Vallik,
director for digital content and interactivity, said she expected sales of digital versions of the
company's books someday to match or potentially outstrip sales in print.

Harlequin, which publishes 120 books a month, makes all of its new titles available digitally, and
has even started publishing digital-only short stories that it sells for \$2.99 each, including an
erotica collection called Spice Briefs.

Perhaps the most overlooked boost to e-books this year -- and a challenge to some of the standard
thinking about them -- came from Apple's do-it-all gadget, the iPhone. Several software programs for
reading e-books have been created for the device, and at least two of them, Stanza from LexCycle and
the eReader from Fictionwise, have been downloaded more than 600,000 times.

Both of these companies say they are now tailoring their software for other kinds of smartphones,
including BlackBerrys. Another company, Scroll Motion, announced this week that it would begin
selling e-books for the iPhone from major publishers like Simon \& Schuster and Penguin.

Publishers say these iPhone applications are already starting to generate nearly as many digital
book sales as the Sony Reader, though they still trail sales of books in the Kindle format.

Meanwhile, the quest to build the perfect e-book reader continues. Amazon and Sony are expected to
introduce new versions of their readers in 2009. Adherents expect the new Kindle will have a sleeker
design and a better microprocessor, allowing snappier page-turning.

Mr.~Haber of Sony said future versions of the Reader will have wireless capability, a feature that
has helped make the Kindle so appealing. This means that the device does not have to be plugged into
a computer to download books, newspapers and magazines.

Other competitors are on the way. Investors have put more than \$200 million into Plastic Logic, a
company in Mountain View, Calif., The company says that next year it will begin testing a flexible
8.5-by-11-inch reading device that is thinner and lighter than existing ones. Plastic Logic plans to
begin selling it in 2010.

Along the same lines, Polymer Vision, based in the Netherlands, demonstrated a device the size of a
BlackBerry that has a five-inch rolled-up screen that can be unfurled for reading. There are also
less ambitious but cheaper readers on the market or expected soon, including the eSlick Reader from
Foxit Software, arriving next month at an introductory price of \$230.

E Ink, the company in Cambridge, Mass., that has developed the screen technology for many of these
companies, says it is testing color screens and hopes to introduce them by 2010.

Many book lovers are quite happy with today's devices. MaryAnne van Hengel, 51, a graphic designer
in Croton-on-Hudson, N.Y., once railed against e-readers at a meeting of her book club. But she
embraced the Kindle her husband gave her this fall shortly after Ms.~Winfrey endorsed it.

Ms.~Van Hengel now has several books on the device, including a Nora Roberts novel and Doris Kearns
Goodwin's ``Team of Rivals.'' She said the Kindle had spurred her to buy more books than she
normally would in print.

``I may be shy bringing the Kindle to the book club because so many of the women were so against the
technology, and I said I was too,'' Ms.~Van Hengel said. ``And here I am in love with it.''

\section{Don't Starve a Cold of Exercise}

YOU have what seems to be a really bad cold. You are coughing and sneezing, and it is hard to
breathe.

Should you work out?

And if you do, should you push yourself as hard as ever or take it easy? Will exercise have no
effect, or make you feel better or worse?

It is a question, surprisingly enough, that stumps many exercise physiologists and infectious
disease specialists.

``That question has not been actually studied,'' said Dr.~Aaron E.~Glatt, a spokesman for the
Infectious Diseases Society and the president of New Island Hospital in Bethpage, N.Y.

Many avid\index{avid}\hypertarget{avid}{}\footnote{\textbf{avid}:$[$\textprimstress\ae vid$]$.
\textit{adj}. 渴望的; 贪婪的\hyperlink{avid}{\textasciicircum}} exercisers make up their own rules,
and it seems that many of them, like Dr.~Michael Joyner, an exercise researcher at the Mayo Clinic
who is a swimmer and runner, decide to keep exercising if they possibly can.

``I can tell you that unless I am really wiped out, I still work out but maybe scale back a bit,''
Dr.~Joyner said. ``I think that would be the answer from most relatively hard-core, old-school
types.

``If I have an obvious fever and muscle aches,'' he continued, ``I do very little or take a day or
two off, but I really have to be in a bad way to skip more than that.''

Dr.~Bill Schaffner, chairman of the department of preventive medicine at Vanderbilt University and a
member of the board of directors of the Infectious Diseases Society, said he was unaware of any
studies that addressed the issue.

Dr.~Schaffner described himself as a jogger who runs a few miles most days and goes to a gym for
resistance training. And, he said, he continues his workouts when he has a cold.

Exercise, he said, makes him feel better. He speculates that perhaps it is because his blood vessels
are dilated\index{dilate}\hypertarget{dilate}{}\footnote{\textbf{dilate}:$[$dai\textprimstress
leit$]$. \textit{vi vt}. 膨胀\hyperlink{dilate}{\textasciicircum}} when he exercises.

``I think exercise pushes me along a route to recovery,'' Dr.~Schaffner said. ``Of course, I
recognize that I might have been on a route to recovery anyway. But I can't think of a reason why
exercise would affect you adversely.''

It turns out that, even though they were unaware of them, the strategies of people like
Dr.~Schaffner and Dr.~Joyner are actually supported by two little-known studies that were published
a decade ago in the journal Medicine \& Science in Sports \& Exercise. Results from the studies were
so much in favor of exercise that the researchers themselves were surprised.

The studies began, said Leonard Kaminsky, an exercise physiologist at Ball State University, when a
trainer at the university, Thomas Weidner, wondered what he should tell athletes when they got
colds.

The first question was: Does a cold affect your ability to exercise? To address that, the
researchers recruited 24 men and 21 women ages 18 to 29 and of varying levels of fitness who agreed
to be deliberately infected with a rhinovirus, which is responsible for about a third of all colds.
Another group of 10 young men and women served as controls; they were not infected.

At the start of the study, the investigators tested all of the subjects, assessing their lung
functions and exercise capacity. Then a cold virus was dropped into the noses of 45 of the subjects,
and all caught head colds. Two days later, when their cold symptoms were at their worst, the
subjects exercised by running on treadmills at moderate and intense levels. The researchers reported
that having a cold had no effect on either lung function or exercise capacity.

``I was surprised their lung function wasn't
impaired\index{impair}\hypertarget{impair}{}\footnote{\textbf{impair}:$[$im\textprimstress
p\epsi\schwa$]$. \textit{vt}. 损害\hyperlink{impair}{\textasciicircum}},'' Dr.~Kaminsky said. ``I
was surprised their overall exercise performance wasn't impaired, even though they were reporting
feeling fatigued.''

He said he also tested the subjects at different points in the exercise sessions, from moderate to
intense effort, and found that their colds had no effect on their
metabolic\index{metabolic}\hypertarget{metabolic}{}\footnote{\textbf{metabolic}:$[$\textsecstress
met\schwa\textprimstress b\openo lik$]$. \textit{adj}. 新陈代谢的
\hyperlink{metabolic}{\textasciicircum}} responses.

Another question was: Does exercising when you have a cold affect your symptoms and recovery time?

Once again, Dr, Kaminsky and his colleagues infected volunteers with a rhinovirus. This time, the
subjects were 34 young men and women who were randomly assigned to a group that would exercise with
their colds and 16 others who were assigned to rest.

The group that exercised ran on treadmills for 40 minutes every other day at moderate levels of 70
percent of their maximum heart rates.

Every 12 hours, all the subjects in the study completed questionnaires about their symptoms and
physical activity. The researchers collected the subjects' used facial tissues, weighing them to
assess their cold symptoms.

The investigators found no difference in symptoms between the group that exercised and the one that
rested. And there was no difference in the time it took to recover from the colds. But when the
exercisers assessed their symptoms, Dr.~Kaminsky said, ``people said they felt O.K. and, in some
cases, they actually felt better.''

Now, Dr.~Kaminsky said, he and others at Ball State encourage people to exercise when they have
colds, at least if they have the type producing symptoms like runny noses and sneezing. He is more
cautious about other types of colds that produce fevers or symptoms below the neck such as chest
congestion. Exercising with a head cold is not an issue for athletes, Dr.~Kaminsky said, because
most of them want to train no matter what. ``If anything they tend to push too much,'' he said.

Dr.~Kaminsky also runs a fitness program at the university, dealing with regular exercisers. When he
tells them it is all right to exercise when they have a cold, many are ``a little suspicious,'' he
said. Often, they want to back off a little, lowering the intensity of their efforts.

``We tell them that's O.K. if it's for a short period of time,'' Dr.~Kaminsky said. ``But what you
have to be cautious of, where I see it as more of an issue, is with people who are trying to build
that exercise habit. They've got all these barriers anyway.''

AND too often taking time off because of a cold is the start of falling away from the program
entirely.

Dr.~Kaminsky, who runs and works out on elliptical cross trainers and does resistance training,
takes the studies' findings to heart. Now when he has a cold, he continues to work out.

``It did give me the personal assurance that it was a good thing to do,'' he said.

\section{Contradictions in China, and the Rise of a Billionaire Family}

GUJIA VILLAGE, China -- In the 1950s, the Liu family of southwest China's Sichuan Province was so
short of food, they sent one of their youngest sons to be raised by another family.

Today, however, they are one of China's richest families.

Rising from public scorn during the Cultural Revolution, the four Liu brothers managed to turn a
small quail-breeding farm into China's largest private company, later splitting it into four.

``The difficulties we went through in the early years made us strong,'' says 60-year-old Liu
Yongxing, a former factory worker whom Forbes lists as the wealthiest person in China, with a
fortune estimated at \$3 billion.

The Lius are China's first-generation billionaires, born into a world of Mao suits, food rations,
price controls and Communist slogans. And the story of how they made their fortune is considered one
of the guiding myths of China's Communist party, a symbol of this country's transformation over the
last 30 years, since its unlikely embrace of capitalism. But their story also betrays the
contradictions of modern China -- a country where the average factory worker makes less than \$50 a
week.

``The puzzle is not why the Liu brothers succeeded, but why there are not more like them in China,''
says Huang Yasheng, who teaches at the Sloan School of Management at the Massachusetts Institute of
Technology and is an expert on Chinese
entrepreneurs\index{entrepreneur}\hypertarget{entrepreneur}{}\footnote{\textbf{entrepreneur}:$[$\textsecstress\openo
ntr\schwa pr\schwa\textprimstress n\schwa\textlengthmark$]$. \textit{n}. 企业家
\hyperlink{entrepreneur}{\textasciicircum}}. ``Rural China represents a vast pool of entrepreneurial
capabilities and substantial business opportunities.''

As the global economy enters its first drastic downturn since China opened to the world, analysts
say this country is searching for a more sustainable path to growth.

Waning foreign demand threatens to stall its economic miracle and Beijing's leaders are trying to
cope with the undersides of growth, like rising inequality and environmental degradation.

``The old game has started collapsing,'' says Xu Xiaonian, a professor of economics at the China
Europe International Business School in Shanghai, referring to China's inefficient export-oriented
economic model, which can be
prone\index{prone}\hypertarget{prone}{}\footnote{\textbf{prone}:$[$pr\schwa un$]$. \textit{adj}.
lying flat or face downwards; prostrate.易于,俯伏的,面向下的\hyperlink{prone}{\textasciicircum}} to
overheat. ``We are now in a transition period. We need to find new ways to do things.''

The hope among economists is that China's next path to riches will inspire an even larger and more
innovative group of entrepreneurs, and tap more of this nation's impoverished rural areas.

For the Liu family, the journey from there to here was seemingly impossible.

Their road to riches is documented in a small museum they built here in Gujia village, on the
grounds of their first feed mill, where photographs show the brothers examining supplies and posing
with Chinese and world leaders, like Jiang Zemin, Bill Clinton, Tony Blair and Jacques Chirac.

They also built a memorial about 200 miles east of here in the hometown of their hero, Deng
Xiaoping, the former Chinese leader who is considered the architect of China's economic reforms.

Like many Chinese entrepreneurs, the Lius trace their fortunes back to December 1978, when Mr.~Deng
presided over the Third Plenary session of the Communist Party. In a critical speech to the party's
elite\index{elite}\hypertarget{elite}{}\footnote{\textbf{elite}:$[$ei\textprimstress
li\textlengthmark t$]$. \textit{n}. 精华,精锐,中坚分子\hyperlink{elite}{\textasciicircum}}, he
boldly called for more trade with the outside world and said he favored market-oriented reforms.
These policies would later come to be called ``socialism with Chinese characteristics.''

``It is one of the most substantive speeches I've ever read by a Chinese leader,'' says Robert
Lawrence Kuhn, who just published a book about China's economic reforms. ``Point five said the
government would allow some to get rich first. This was radical.''

After decades of isolation and outright hostility to capitalism, China suddenly began loosening
state controls over the economy and encouraging its citizens to get rich. What followed was three
decades of roaring growth and a export-oriented wealth boom that the World Bank says has lifted 400
million people out of poverty.

Not long before the extraordinary Communist Party meeting in 1978, the four Liu brothers -- Yongyan,
Yongxing, Yuxin and Yonghao -- say they were toiling on farms or in state-owned factories here in
southwest China, scorned because of their ``counter-revolutionary'' family background: they were the
descendants of wealthy landlords.

During the decade-long Cultural Revolution, which ended in 1976, their father was condemned to a
``re-education'' camp. Their mother was officially denounced.

But in 1978, three of Liu brothers won admission to local colleges, and soon they began plotting to
make it rich.

At the time, the quiet one, Yongyan, 33, was studying engineering. Yongxing, 30, was good at fixing
radios; and the
extrovert\index{extrovert}\hypertarget{extrovert}{}\footnote{\textbf{extrovert}:$[$\textprimstress
ekstr\schwa uv\schwa\textlengthmark t$]$. \textit{n adj}. 外向的,外向
\hyperlink{extrovert}{\textasciicircum}}, Yonghao, 27, was teaching at a technical school.

They had each inherited their father's interest in science and technology.

Yuxin, who had been sent away from home as a child, was a 28-year-old farmer in Gujia village. But
he also teamed up with his brothers to plot a new course.

Their first venture, an electronics company, failed almost immediately, they say, largely because a
Communist Party official deemed it too ``capitalistic.'' Individuals at the time could not own
factories or operate in the electronics business. Chinese were encouraged to become ``socialist
entrepreneurs'' not capitalists, which was still a bad word.

Not many Chinese, though, knew the difference. Soon after, the brothers pooled \$125 and began
raising quails\index{quail}\hypertarget{quail}{}\footnote{\textbf{quail}:$[$kweil$]$. \textit{n}. 鹌
鹑\hyperlink{quail}{\textasciicircum}} here in Gujia.

At the time, Gujia was one of the region's most impoverished villages, located 17 miles northeast of
Chengdu, the provincial capital. It had no electricity or running water and its houses were small
huts constructed with mud and grass. But conditions were good enough to raise quail.

``If you raise quail, you don't need much feed,'' says Liu Yongxing, explaining their choice.
``Quails are small. And we didn't have much land or money.''

Suddenly other villagers began raising quail too, and customers in bigger towns lined up to buy
quail eggs. Gujia became the quail-breeding capital of China. And the Liu brothers thrived.

Before long they were among the first in the region to be honored by local Party officials as
``10,000 RMB men,'' model socialist entrepreneurs who accumulated Chinese currency or renminbi.

``If you did business during the Cultural Revolution, you were the evil capitalist and you would be
paraded through the street and people would throw garbage at your head,'' said Gao Peineng, 53, the
former village chief of Gujia and a longtime friend of the Liu brothers. ``But in 1982, the
government began honoring what they called the ``advanced wealth maker.'' They would ride you in a
truck with red flowers and a gold medal.''

Liu Yongxing says there were hard times too, like the time they shipped thousands of quail eggs to a
buyer, only to have his check bounce, practically bankrupting the family.

But early market chaos gave way to big opportunities.

With agriculture designated as one of the first areas open to market reform, the Liu brothers
quickly branched out into the animal feed business.

At a time when many farmers simply fed their animals garbage or scraps, the brothers copied the new
feed production techniques of the Charoen Pokphand Group of Thailand, one of China's first big
foreign investors.

The Lius then convinced farmers that buying their feed would make animals grow much faster. They
grabbed market share by pricing their feed much lower than Charoen Pokphand. With meat consumption
in China soaring, demand for feed skyrocketed.

Between 1978 and 1990, grain output in China rose by more than 30 percent.

``The Liu brothers are very smart and grasped the opportunity early,'' says Wan Zhaojun, dean of the
Sichuan Animal Husbandry Institute. ``Living standards were improving dramatically; meat consumption
was going up. This was the golden time for the feed business and they were right there.''

Their success was validated by the Communist Party in 1994, when Song Jian, a government science
official, visited their feed mill and declared that ``the future of China's economic reforms will
rely on these socialist entrepreneurs.''

Soon after, they adopted a new name: the Hope Group.

The visit was an early sign that government officials were the ultimate
arbiters\index{arbiter}\hypertarget{arbiter}{}\footnote{\textbf{arbiter}:$[$\textprimstress\vara\textlengthmark
bit\schwa$]$. \textit{n}. a person empowered to judge in a dispute; referee; arbitrator.仲裁人, 公断
人.\hyperlink{arbiter}{\textasciicircum}} of success, and while the Liu brothers give credit today
to the market reforms, they acknowledge in their speeches and their museums that the Party also
played a role in their success.

``By 1984, almost all the Sichuan government officials came to our farms,'' says Liu Yongxing. ``It
was like a big advertisement for us.''

After rapidly expanding in Sichuan, home to the world's biggest pig population, they built feed
mills all over the country.

By 1992, the Hope Group was so large the Liu brothers decided to split it into four companies, along
geographical lines -- East Hope, West Hope, New Hope and Continental Hope, allowing each brother to
pursue his own interest, and diversifying the family holdings.

Yongxing moved to Shanghai and invested in aluminum, power plants and finance. Yonghao, who runs New
Hope was listed in October at No. 4 on the list of China's richest, with a net worth of \$2.2
billion and holdings in real estate, feed and banking. Chen Yuxin (his adopted family's name) runs
West Hope, with the original feed operation in Sichuan and a five-star hotel and retail properties
in Chengdu. And Yongyan has a feed and electronics business. The Lius' only sister, Liu Yonghong,
handles all the accounting for the family. Even with billions of dollars, family members and friends
say the Liu brothers are
frugal\index{frugal}\hypertarget{frugal}{}\footnote{\textbf{frugal}:$[$\textprimstress
fru\textlengthmark \schwa l$]$. \textit{adj}. practising economy; living without waste; thrifty.节省
的; 俭朴的; 量少的, 花钱少的.\hyperlink{frugal}{\textasciicircum}} and modest. Liu Yongxing flies
economy class (even though he's the richest man in China) and Chen Yuxin doesn't have a personal
assistant.

They insist, like many Chinese entrepreneurs, that they do not show off or
indulge\index{indulge}\hypertarget{indulge}{}\footnote{\textbf{indulge}:$[$in\textprimstress
d\pwedge ld\yogh$]$. \textit{vt}. to yield to or gratify (a whim or desire for).沉迷; 放纵(感情、欲望
等); 纵情享受.\hyperlink{indulge}{\textasciicircum}} in extravagant luxuries.

``It's ridiculous to show off your wealth,'' says Liu Yongxing, sitting in his Shanghai office
wearing casual clothes and sipping tea.

The next generation of the family consists of four daughters and one son, Shawn Liu, the only child
of Liu Yongxing.

Educated in the United States, at the University of Southern California, and married to a woman from
Texas, Shawn, 33, is preparing to take over from his father. Two of the founders' daughters work
with their fathers, helping manage the companies, while another two live in the United States and
have no role in the company.

``My goal is somehow to bring the company out to have an international presence,'' says Shawn. ``If
not international, at least southeast Asia. We are now looking at opportunities.''

\section{What to Do When the Patient Says, 'Please Don't Tell Mom'}

Some years ago, in the candor of the exam room, a seventh-grade boy told me that he didn't really
have friends at school, and that he sometimes found himself being picked on. I gave him the
pediatric\index{pediatric}\hypertarget{pediatric}{}\footnote{\textbf{pediatric}:$[$\textsecstress
pi\textlengthmark di\textprimstress\ae trik$]$. \textit{adj}. 儿科的
\hyperlink{pediatric}{\textasciicircum}} line on
bullying\index{bully}\hypertarget{bully}{}\footnote{\textbf{bully}:$[$\textprimstress buli$]$.
\textit{vt}. 恐吓,威逼\hyperlink{bully}{\textasciicircum}}: it shouldn't be tolerated, and there are
things schools can do about it. Let's talk to your parents, let's have your parents talk to the
school; adult interventions can change the equation.

And he was horrified. He shook his head
vehemently\index{vehement}\hypertarget{vehement}{}\footnote{\textbf{vehement}:$[$\textprimstress
vi\textlengthmark im\schwa nt$]$. \textit{adj}. 激烈的; 猛烈的
\hyperlink{vehement}{\textasciicircum}} and asked me please not to interfere, and above all not to
say a word to his mother, who was out in the waiting room because I had asked her to give us some
privacy.

He wouldn't have told me this at all, he said, except he thought our conversation was private. The
situation at school wasn't all that bad; he could handle it. He wasn't in any danger, wasn't getting
hurt, he was just a little lonely. His parents, he said, thought that he was fine, that he had lots
of friends, and he wanted to keep it that way.

When treating older
adolescents\index{adolescent}\hypertarget{adolescent}{}\footnote{\textbf{adolescent}:$[$\textsecstress\ae
d\schwa u\textprimstress lesnt$]$. \textit{adj n}. 少年\hyperlink{adolescent}{\textasciicircum}},
pediatricians routinely offer confidentiality on many issues, starting with sex and substances. But
middle-schoolers are on the border -- old enough to be asked some of the same questions, but young
enough that it can be less clear what should stay confidential.

At my own eighth-grade son's pediatric checkup last year, I of course left the room, because I
didn't want to embarrass him or inhibit him, and because I wanted his pediatrician to have the
opportunity to hear anything he wanted to say. (I am reporting this with my son's explicit
permission.) But as I waited, I thought of that seventh grader, and of the other middle-schoolers
who have told me things that left me agonizing about the
ethics\index{ethic}\hypertarget{ethic}{}\footnote{\textbf{ethic}:$[$\textprimstress e\texttheta
ik$]$. \textit{n}. 道德规范,伦理\hyperlink{ethic}{\textasciicircum}} and the wisdom of
confidentiality in this age group.

I'm not talking about the child who tells you something that makes it clear he's in danger. Those
are the ``easy'' ones (though in another sense they can be tremendously difficult), and I've had my
share: The 13-year-old girl who is frightened of a much older guy who sometimes seems to follow her
home. The 14-year-old boy who has been thinking about dying a lot ever since his grandmother died.
The seventh grader who is being beaten up on the playground. No matter the age, when I feel the
child is actually in danger, I explain that I have to let the parents know.

But as I talked to my colleagues -- including my son's pediatrician, Dr.~Herbert Lazarus -- we all
kept coming up with ambiguous cases. Because you do value the child's trust, and you don't want to
lose it.

I'm not talking about the child who tells you he shared a beer with his friends one day after
school. Most sensible parents, I think, know that once they're out of the exam room we're going to
review sex, drugs and rock 'n' roll with their children, and most sensible parents, I think, are
grateful. And many middle-school children seem grateful for the opportunity to mention that yes,
they have been in situations where people are drinking.

``They'll preface it with 'My mom's not going to know about this, right?' '' said Dr.~Lazarus, who
is also a clinical associate professor of pediatrics at New York University. ``I'm going to talk as
much as I can about why this is not good, and all we know about alcohol and marijuana. There are
enough studies out there that show how bad this is for brain development.''

But what about if it's more than a beer? One of my colleagues had a story: a 13-year-old girl who
was drinking and stealing from her parents' liquor cabinet. ``She did admit that to me,'' the
pediatrician said. ``She was doing it by herself, not a good sign, not social drinking.''

The child did not want her mother to know, and the pediatrician, who had known her since infancy,
negotiated a compromise: the doctor would advise the mother that the girl needed counseling, and as
long as she went to counseling, and discussed the drinking and her underlying issues with the
counselor, the pediatrician would not tell her mother about the liquor.

But even though it worked out, even though she continued seeing the patient regularly, the
pediatrician still felt less than completely comfortable. ``I did personally feel bad,'' she said,
``because if I were the mother, I would want to know, and I actually did tell the mother just to
keep a closer eye on her without going into the details.'' So what about the child who trusts you
with the information that he's being picked on, or that all is not well at home? You want to keep
that child's trust -- all the more so if the child isn't talking to the parents, because you want to
be available for more confidences if things grow worse.

``The balance changes in part based on what the level of the health risks are, how mature that young
person is, how much parental oversight they're receiving,'' said Dr.~S.~Jean Emans, chief of
adolescent medicine at Children's Hospital Boston.

Experts say the middle-school years are particularly challenging. ``It's a fine balance because it's
developmentally appropriate for kids to want to develop some autonomy and it's the time when they
should be developing at least in part a private and confidential relationship with a physician,''
said Dr.~Carol A. Ford, director of the adolescent medicine program at the University of North
Carolina, Chapel Hill.

``Middle school is really when you see a lot of variation in pubertal development and cognitive
development and social development,'' Dr.~Ford went on. ``A 12-year-old who looks like an
18-year-old -- you can't assume they think like an 18-year-old. You can't assume their skills of
negotiating the world are related to their physical maturity.''

Or as Dr.~Emans put it: ``You do have to make tough choices. There isn't a little book where you
look up, 'O.K., this can stay confidential and this can't.' ''

So what did I do with the seventh grader who had told me he didn't have friends at school? Well, I
asked him a bunch of questions, and I decided that he wasn't feeling suicidal (or homicidal) and
that the situation in his school didn't threaten his physical safety. I urged him to talk to his
parents, especially if things grew worse -- and I scheduled an appointment for him to come back and
check in with me.

But with his mother, I limited myself to one of those ``generic'' comments: this is an age when he
really needs you to be involved in his life, to talk about how things are going at school.

``Your role as a physician is different than your role as a mother,'' Dr.~Ford said. ``If you lose
the trust of the kid, you've lost a lot; they won't tell you what's going on in the future, and
that's not in the best interests of the kid or the parent.''

If I had been his mother, I would have wanted to know. But I was his doctor, and he wanted it kept
confidential.

\section{Apple Drops Anticopying Measures in iTunes}

SAN FRANCISCO -- In moves that will help shape the online future of the music business, Apple said
on Tuesday that it would remove anticopying restrictions on all of the songs in its popular iTunes
store and allow record companies to set a range of prices for them.

Beginning this week, three of the four major music labels -- Sony Music Entertainment, Universal
Music Group and Warner Music Group -- will begin selling music through iTunes without digital rights
management software, or D.R.M., which controls the copying and use of digital files. The fourth,
EMI, is already doing so.

In return, Apple, whose dominance in online music sales gives it powerful leverage, agreed to a
longstanding demand of the music labels and said it would move away from its insistence on pricing
all individual song downloads on iTunes at 99 cents.

Instead, the majority of songs in the store will drop to 69 cents beginning in April, while the
biggest hits and newest songs will go for \$1.29. Others that are moderately popular will remain at
99 cents.

The music companies are hoping that their eagerly awaited compromise with Apple will give a lift to
digital downloads. They will be able to make more money on their best-selling songs and increase the
appeal of older ones.

And with the copying restrictions removed, people will be able to freely shift the songs they buy on
iTunes among all of their computers, phones and other digital devices, potentially changing the way
they listen to music.

Technologically sophisticated fans of digital music complain that D.R.M. imposes unfair restrictions
on what they can do with the tracks they have bought. For example, the protected files from iTunes
do not work on portable players made by companies other than Apple.

``I think the writing was on the wall, both for Apple and the labels, that basically consumers were
not going to put up with D.R.M. anymore,'' said Tim Bajarin, an analyst with Creative Strategies, a
market research firm. ``This is good news for customers across the board.''

Music industry watchers widely applauded the move and said it could help digital music sales, which
have shown signs of slowing down just five years after Apple first introduced iTunes.

In particular, the lower price for some songs could get consumers ``to buy deeper into the catalog,
and expand their relationship with digital music,'' said Russ Crupnick, an analyst with the NPD
Group.

The music industry could really use a lift. Sales of CDs fell 20 percent last year from 2007. About
2.4 billion songs were purchased on iTunes in the last year, aided by Apple's expansion into
international markets. But that was not nearly enough to make up for losses in traditional retail
stores.

Industry pundits have long pointed to D.R.M. as one culprit for the music companies' woes, saying it
was a drag on sales because it turned off some customers, while doing little to slow piracy on
file-sharing networks.

Apple has been campaigning against D.R.M. at least since February 2007, when Apple's chief
executive, Steven P. Jobs, wrote an open letter criticizing the technology. Later that year, Apple
reached a deal with EMI, the smallest of the four major record companies, to offer music without the
copying restrictions.

But it could never reach the same agreement with EMI's larger rivals. Sony, Warner and Universal
allowed other online music services, like Amazon's MP3 Store, to sell unprotected music, but they
withheld it from Apple. Their goal, say industry analysts, was to try to strengthen online rivals to
iTunes, which they viewed as having a dangerous level of control over their business.

``Apple definitely wanted to remove D.R.M. from music, but the record labels would not allow them to
renegotiate their licensing agreements, because they wanted to help competitors succeed against
Apple in the market,'' said Bill Rosenblatt, president of GiantSteps Media Technology Strategies, a
consulting firm.

Apple, for its part, has appeared to resist variable pricing, fearing that it would amount to a
price increase for the most popular tracks on iTunes, which constitute the bulk of the sales on the
service. It has also said the consistent 99-cent price made things simpler for buyers.

It is not clear what broke the impasse, but the deteriorating economy may have put some pressure on
the music companies. ``For the major labels, it was clearly time for them to accelerate becoming
digital music companies in a macroeconomic environment that is downright frightening,'' said Greg
Scholl, chief executive of The Orchard, a digital distributor of music from independent labels.

The compromise gives the recording industry new leverage over their online music sales, Mr.~Scholl
added. They can start to sell new tracks at the higher price and then gradually drop prices to keep
sales moving. Labels could also experiment with bundled packages of songs and even special editions
at higher prices.

``They aren't going to get a huge amount of money from this new arrangement, but in an
ailing\index{ailing}\hypertarget{ailing}{}\footnote{\textbf{ailing}:$[$\textprimstress
eili\engma$]$. \textit{adj}. unwell or unsuccessful.害病的, 不舒服
的.\hyperlink{ailing}{\textasciicircum}} music industry, anything that can provide more money will
be better than the status quo,'' said Harry Wang, the director of mobile product research at the
consulting company Parks Associates.

Apple said customers would be able to pay a one-time fee to strip copying restrictions from all of
the music they have already bought on iTunes. The price is 30 cents a song or 30 percent of the
album price. ITunes customers can achieve the same effect by burning all of their music to a CD and
then reimporting the music to iTunes, although this reduces sound quality somewhat.

The company also said that its popular iPhone would be able to download songs from iTunes over
wireless data networks like AT\&T's. Previously, iPhone owners had to either attach the phone to a
computer or connect to a local Wi-Fi network.

Apple reported these changes to iTunes at its keynote presentation at the annual Macworld conference
in San Francisco, given by Philip Schiller, Apple's senior vice president of worldwide marketing.
Mr.~Jobs was not present at the event, after disclosing earlier this week that he was suffering from
a treatable hormone problem that had resulted in significant weight loss over the last year.

\section{China Criticizes Google and Others on Pornography}

HONG KONG -- The Chinese government broadened its recent effort to limit pornography on the Internet
by criticizing 19 Internet companies by name on Monday, including the two market leaders in China,
Google and Baidu.

A statement posted on a government-run news site said the Ministry of Public Security and six other
government agencies would work together ``to purify the Internet's cultural environment and protect
the healthy development of minors.'' A similar statement had been issued on Dec. 5, but attracted
little attention.

Monday's statement went a step further in saying that 19 companies had failed to do enough to stop
the spread of pornography. Early Monday evening, the names of the companies were also posted on the
same official Web site, along with a terse statement of why each company was on the list.

The entry for Google simply said: ``Searching for images results in an enormous number of
vulgar\index{vulgar}\hypertarget{vulgar}{}\footnote{\textbf{vulgar}:$[$\textprimstress v\pwedge
l\schwa$]$. \textit{adj}. marked by lack of taste, culture, delicacy, manners, etc.庸俗的, 粗俗的,
低级的.\hyperlink{vulgar}{\textasciicircum}}, pornographic sites. Google, receiving notice, did not
undertake any effective measures.''

A Google spokeswoman, Jin Cui, said on Monday evening that the company was not aware of any new
regulations or restrictions on the Internet in China.

In a statement issued on Tuesday morning in China, the company said: ``Google has clear policies to
protect freedom of expression while not allowing illegal content on our sites in China and elsewhere
around the world. As a search engine, Google does not control the content of the billions of pages
in our index.''

The government list of offending Internet companies had a similarly phrased criticism of Baidu, the
market leader among Internet search engines in China. A spokeswoman answering the phones at Baidu's
press office on Monday afternoon said that only one of her colleagues was authorized to discuss the
issue but was not available.

The companies
chastised\index{chastise}\hypertarget{chastise}{}\footnote{\textbf{chastise}:$[$t\esh\ae
s\textprimstress taiz$]$. \textit{vt}. 惩戒, 责打\hyperlink{chastise}{\textasciicircum}} on Monday
appeared to be those particularly active in offering search engines or hosting blogs and chat
forums.

Rebecca MacKinnon, an assistant professor of media studies at the University of Hong Kong who
specializes on China's Internet controls, said that the criticisms issued Monday represented the
latest in a long series of Internet crackdowns in China and that they did not appear to represent a
long-term policy shift.

The State Administration of Radio, Film and Television, which has separate regulatory authority in
China to regulate video on the Internet, conducted a separate crackdown last March on businesses
that made pornographic videos available. That crackdown included shutting down the Internet
operations of one of the most popular video-sharing services, Tudou, for a full day as a warning.

Many Chinese, particularly the young, have become much less conservative about public discussions of
sex and the commercialization of sex over the past three decades, as the country opened up to the
West and shifted toward a more market-oriented economy. The authorities have periodically tried to
limit the spread of prostitution and pornography, with little sign of success.

Ms.~MacKinnon said that while restrictions on Internet pornography fluctuated, political expression
was consistently limited on the Internet. ``The same mechanisms used to censor porn are used to
censor anything else people want to censor,'' she said.

\section{For Pittsburgh, There's Life After Steel}

PITTSBURGH -- This is what life in one American city looks like after an industrial collapse:

Unemployment here is 5.5 percent, far below the national average. While housing prices sank nearly
everywhere in the last year, they rose here. Wages are also up. Foreclosures are comparatively
uncommon.

A generation ago, the steel industry that built Pittsburgh and still dominated its economy entered
its death throes. In the early 1980s, the city was being talked about the way Detroit is now. Its
very survival was in question.

Deindustrialization in Pittsburgh was a protracted and painful experience. Yet it set the stage for
an economy that is the envy of many recession-plagued communities, particularly those where the
automobile industry is struggling for its life.

``If people are looking for hope, it's here,'' said Sabina Deitrick, an urban studies expert at the
University of Pittsburgh. ``You can have a decent economy over a long period of restructuring.''

Pittsburgh's transition has been proceeding for decades in fits and starts, benefiting some areas
much more than others. A development plan begun in the 1980s successfully used the local
universities to pour state funds into technology research. Entrepreneurship bloomed in computer
software and biotechnology.

Nowadays, two of the biggest sectors of the local economy are education and health care, among the
most resistant to downturns. Prominent companies are doing well. Westinghouse Electric says it will
hire hundreds of engineers in the next few years to build nuclear reactors. And commercial
construction, plunging in most places, is still thriving here partly because of big projects like a
casino and an arena for the Penguins hockey team.

The question is whether Pittsburgh can serve as a model for Detroit and other cities in the
industrial Midwest as they grapple with large-scale cutbacks in the automotive industry. Even with
the federal government's \$17.4 billion bailout, General Motors, Chrysler and Ford are expected to
continue shrinking.

The unemployment rate in Michigan, already close to 10 percent, will undoubtedly rise further. State
and federal officials will have to increase the number of retraining programs, and develop a
postindustrial policy that ensures there is something for the graduates to do. That will take
patience and money, two commodities in short supply.

About 4 percent of Michigan workers make cars and parts, with many more employed in related fields.
Few regions are as dependent on a single heavy industry. But the history of Pittsburgh, where steel
workers fell from as much as 10 percent of the work force in 1980 to less than 1 percent today,
offers proof that revitalization is possible.

Housing prices in Pittsburgh were up 2.2 percent for the year ending September 2008 despite a slight
drop in the latest quarter, according to the government's House Price Index. That compares with a 4
percent drop for the United States as a whole.

One reason Pittsburgh looks better in the
bust\index{bust}\hypertarget{bust}{}\footnote{\textbf{bust}:$[$b\pwedge st$]$. \textit{n;vi,vt}. the
chest of a human being, esp a woman's bosom,半身塑像或画像 (妇女的)胸部;to burst or break,打破, 打
碎.\hyperlink{bust}{\textasciicircum}} is because it never experienced the real estate-propelled
boom. That might have been a cause for complaint among local homeowners who missed out on the
soaring values in California and Florida in the first half of the decade, but these days they can
only be grateful.

The big local bank, PNC, was resolutely unadventurous during the housing frenzy. It just acquired
Cleveland-based National City, which made too many bad loans. That will solidify Pittsburgh's
standing as one of the country's major banking centers.

Yet the semisweet spot that Pittsburgh finds itself in today was never inevitable. As recently as
2000, it had a higher unemployment rate than Detroit or Cleveland. Just as Michigan has
traditionally put all its chips on the auto industry, it took Pittsburgh a long time to come to
terms with the end of the steel era.

``The emphasis was on fighting the presumed causes of the decline by getting rid of low-cost foreign
imports or providing more subsidies,'' said Harold D. Miller of Future Strategies, a consultancy.
``The assumption was that steel will come back and we'll go back to the way we were.''

There were moments when the rebirth of steel seemed plausible, if not imminent. Ryan Campbell grew
up in the shadow of the great Homestead Works, now the site of a vibrant shopping mall. When he
graduated from college in 2001, steel effortlessly drew him in.

Mr.~Campbell took a job at a small specialty mill as a foreman. He loved it -- the huge cranes
delicately pouring pots of molten fire, the camaraderie on the production line, the proud heritage
of making something tangible -- but soon realized he could never make a career there.

Overburdened with retiree pension and health care costs, competing against both imports and modern
minimills, the steel industry was convulsing again. An initial round of layoffs at Mr.~Campbell's
mill was followed by a second, then a third. Benefits were cut, product lines dropped. None of this
chopping seemed to make the mill more viable.

``I need to go paddle on a different boat,'' Mr.~Campbell told himself.

He posted a r\'esum\'e online and was promptly sought out by recruiters for Medrad Inc., a health
care company founded by an emergency room doctor in 1964 in Pittsburgh. Now a division of the German
pharmaceutical giant Bayer, Medrad is still based in Pittsburgh. This year it opened its fourth
plant in the area, this one for making sterile disposable syringes. Mr.~Campbell, 31, is a
production manager.

Career transitions could hardly be more painless, but Mr.~Campbell has sympathy for his former
colleagues, who stayed until they were terminated. (His exit agreement precludes him from naming the
factory where he worked.) Some of them were so determined to remain that they transferred into
lesser posts at reduced pay.

Others would be laid off, work in a grocery store or wait tables, and then go back when business
picked up a bit, Mr.~Campbell said. It was a rational thing to do: The mill would pay perhaps \$17
an hour, much more than a restaurant or store.

Mark Conkle considers himself a retraining success, too, but his experience demonstrates how
difficult it will be for many laid-off autoworkers to match their factory income.

Mr.~Conkle worked for 15 years for Ross-Mould special treatin Washington, southwest of Pittsburgh,
as a unionized production machinist. He was making \$23 an hour when he was laid off in 2005.

Some laid-off colleagues went directly to machine shops for \$10 or \$11 an hour. Mr.~Conkle took
the harder route of retraining, enrolling in a 16-month technical program. His unemployment benefits
and his wife Amanda's job as a postal carrier carried the family through.

Last February, Mr.~Conkle, 40, was hired as a maintenance specialist at the Monongahela Valley
Hospital, a 226-bed hospital that is the third largest employer in Washington County and is still
growing. He makes \$15 an hour, and in this economy is happy to have it. ``You've got to take a job,
no matter what it's paying,'' he said. ``Companies know it.''

The forces buffeting the larger economy are beginning to touch Pittsburgh. Sony recently announced
the closing of its Westmoreland County plant near Pittsburgh, its last surviving television
manufacturing factory in the United States. The plant had already been cut to 560 workers from 3,000
a few years ago. And Alcoa, the giant aluminum maker based in Pittsburgh, said Tuesday it was
cutting 13,500 jobs, or 13 percent of its work force.

Even health care is affected. The Medrad plant recently imposed a hiring ``pause.'' Intended to
employ 500 workers, the factory has only about 95.

``Folks who are laid off should be given a chance to remake their lives,'' said Barney Oursler,
co-director of the Mon Valley Unemployed Committee. ``But even if they make huge sacrifices and show
a lot of perseverance and
gumption\index{gumption}\hypertarget{gumption}{}\footnote{\textbf{gumption}:$[$\textprimstress
\pwedge mp\esh\schwa n$]$. \textit{n}. common sense or resourcefulness.好的判断力,丰富的常识
\hyperlink{gumption}{\textasciicircum}}, there are never enough good jobs.''

Particularly now. Pittsburgh had the luxury of reshaping and redefining itself in an era when the
rest of the United States economy was relatively strong. Unemployed steel workers could leave for
the booming Sun Belt, helping the city and region shrink to a more manageable size.

With the entire country reeling, that escape valve is closed.

A few weeks ago, Bill Shever was laid off from his job in a metal sidings plant in Valencia, north
of Pittsburgh. He would willingly relocate, but has not heard of any place where skilled labor is in
demand.

``Times are tough all over,'' said Mr.~Shever, 47. ``I might as well stick it out here.'' He said
there were two specialty steel companies that seemed to be holding their own, and he would try them
first.

\section{It Hurts, but Is It Worth It?}

WHEN Jessi Stensland, a professional
triathlete\index{triathlete}\hypertarget{triathlete}{}\footnote{\textbf{triathlete}:$[$trai\textprimstress\ae\texttheta
li\textlengthmark t$]$. \textit{n}. 三项全能运动员\hyperlink{triathlete}{\textasciicircum}}, enters
the Athletes' Performance training center in Tempe, Ariz., she usually goes through the door labeled
``Work'' and into the wing of the building filled with
treadmills\index{treadmill}\hypertarget{treadmill}{}\footnote{\textbf{treadmill}:$[$\textprimstress
tredmil$]$. \textit{n}. 脚踏车\hyperlink{treadmill}{\textasciicircum}}, elliptical trainers and free
weights.

But once a week, Ms.~Stensland, 22, carries her gym-worn body through a door labeled ``Rest.'' As
soothing music plays, she lies face down between two sheets
atop\index{atop}\hypertarget{atop}{}\footnote{\textbf{atop}:$[$\schwa\textprimstress t\openo p$]$.
\textit{prep}. on top; at the top.\hyperlink{atop}{\textasciicircum}} a cushioned massage table to
await her treatment.

But the session that usually follows is far from a
coddling\index{coddle}\hypertarget{coddle}{}\footnote{\textbf{coddle}:$[$\textprimstress k\openo
dl$]$. \textit{vt}. to treat with indulgence.悉心照料, 娇惯.\hyperlink{coddle}{\textasciicircum}}.

Ms.~Stensland's muscles and
tendons\index{tendon}\hypertarget{tendon}{}\footnote{\textbf{tendon}:$[$\textprimstress tend\schwa
n$]$. \textit{n}. 腱\hyperlink{tendon}{\textasciicircum}} may be
kneaded\index{knead}\hypertarget{knead}{}\footnote{\textbf{knead}:$[$ni\textlengthmark d$]$.
\textit{vt}. to work and press (a soft substance, such as bread dough) into a uniform mixture with
the hands.揉,捏;按摩\hyperlink{knead}{\textasciicircum}},
pummeled\index{pummel}\hypertarget{pummel}{}\footnote{\textbf{pummel}:$[$\textprimstress p\pwedge
m\schwa l$]$. \textit{vt}. (尤指用拳头)连续打\hyperlink{pummel}{\textasciicircum}},
poked\index{poke}\hypertarget{poke}{}\footnote{\textbf{poke}:$[$p\schwa uk$]$. \textit{n, vt vi}. 袋,
囊;夹, 皮夹;(鱼的)鳔; (羊颈部的)袋状肿大;to jab or prod, as with the elbow, the finger, a stick,
etc,戳, 刺; 拨弄;\hyperlink{poke}{\textasciicircum}} or
scraped\index{scrape}\hypertarget{scrape}{}\footnote{\textbf{scrape}:$[$skreip$]$. \textit{vt vi}.
to move (a rough or sharp object) across (a surface), esp to smooth or clean.刮,
擦.\hyperlink{scrape}{\textasciicircum}}. Thumbs and elbows may be forcefully pushed into pressure
points on her body. Clear plastic instruments, some the thickness of a pencil eraser, are used to
deeply penetrate soft tissue that may be tender and tight.

Once the session is over, Jeremy Hassler, the on-site soft tissue specialist, often hears a similar
quip\index{quip}\hypertarget{quip}{}\footnote{\textbf{quip}:$[$kwip$]$. \textit{n vi vt}. 嘲弄, 挖苦
话\hyperlink{quip}{\textasciicircum}} as subjects rise from the table. ``Thanks.'' And then, after a
pause, ``I think.''

So-called sports massages have become a common
facet\index{facet}\hypertarget{facet}{}\footnote{\textbf{facet}:$[$\textprimstress f\ae sit$]$.
\textit{n}. 方面,磨光面\hyperlink{facet}{\textasciicircum}} of training for professional athletes of
all kinds. And because of their increasing presence on spa menus (beside facial exfoliations, body
wraps and hot stone treatments) and at health clubs (down the hall from Pilates, step aerobics and
yoga classes), this sometimes painful procedure -- which can cost \$45 to \$150 an hour -- appears
to be gaining in popularity among a growing segment of amateur athletes.

``It hurts,'' said Tara McGinness Murdock, a runner in Lookout Mountain, Tenn., who recently used
deep-tissue massage while training for a marathon. ``But, as crazy as this sounds, it's a good
hurt.''

But as more amateur athletes have chosen sports massages in an effort to improve performance and
avoid injury, they have been confronted by an increasingly varied combination of massage styles
under this heading.

Asking about the predominant techniques used in the advertised sports massage can be enlightening,
said Terri Schneider, an ultra-endurance athlete and coach.

``If it's all Swedish massage, then it will probably be less of the kind of deep-tissue work that's
beneficial for athletes while training,'' she said. But even exclusive use of the deep-tissue
approach has limitations, as many massage therapists have numerous techniques at their disposal.

Sports massage, Mr.~Hassler explained, has become something of an umbrella term.

Light pressure Swedish-style sports massages (which are often less intense) are typically used to
prime muscle tissue before a heavy bout of exertion or to flush the system after a race or sporting
event.

Deeper, more intense work, not unlike the massage therapy one might normally associate with
rehabilitation from an injury, is undertaken at fitness centers as a weekly general maintenance
measure, often as part of a broader training plan.

Categorically, a deep-tissue sports massage is part of a training philosophy that hinges on the
belief that a succession of heavy workouts can take an athlete only so far. Additionally, what is
(or isn't) accomplished in so-called down time is also significant.

In other words, rather than working out ad nauseam, setting aside time for the body to bounce back
has some intrinsic benefit. But advocates of deep-tissue work contend that such treatments take this
thinking a step further: they don't just allow the body proper time for recovery, they also actually
accelerate the rebuilding process.

Using a technique known as Augmented Soft Tissue Mobilization, for instance, Mr.~Hassler's goal is
to facilitate muscle regeneration. ``We are intentionally inflaming the tissue to kick-start the
body's own natural healing cycle,'' he said. He also uses active release, which breaks up fascial
adhesions (connective tissue buildup created by exertion) to lengthen muscles and better prepare
them for continued high intensity training.

Despite the anecdotal evidence from athletes and massage therapists, hard data that soundly
quantifies the extent of this phenomenon is hard to come by. In broad terms, however, according to
the American Massage Therapy Association, about 20 to 22 percent of the United States population
reported receiving some form of massage in the previous 12 months, compared with 8 percent in 1997.

Ron Precht, spokesman for the association, estimated that these types of massages that are directed
at athletes have been growing in popularity in this country for 10 to 15 years. Colleen Casey,
massage director at ZUM, a boutique health club in downtown Seattle, said she averaged 30 sports
massages a month in 2007. So far in 2008, she has averaged 40 a month.

All the while, research has uncovered varying results.

For instance, a study in the October issue of the British Journal of Sports Medicine found that
cyclists who received massages after intensive pedaling showed improved performance.

But a study in a 2005 edition of the Journal of Athletic Training found that while subjects who
received a 10-minute arm massage three hours after exercise had about a 30-percent reduction in
muscle soreness and swelling, there was no change in muscle strength or function. Furthermore, a
study in the September issue of the Clinical Journal of Sport Medicine by Dr.~Thomas Best of Ohio
State University assessed that, of 27 studies reviewed that tested sports massages after exercise,
only ``moderate evidence'' as to their effectiveness was found. The problem, in part, involved the
inability to create an objective environment for measurement.

``Massage therapists use different amounts of pressure, so there's tremendous variability,'' said
Dr.~Best, who conducted a related study to try to address this very problem.

That trial, reported on in the July edition of Medicine \& Science in Sports \& Exercise, used a
mechanical device to deliver a massage with consistent pressure. When this treatment was delivered
to the legs of rabbits after exercise, they showed a significant increase in muscle recovery and
reduced inflammation as opposed to rabbits that received no massage. ``The machine gave us a basis
to see how much force was supplied,'' Dr.~Best said.

To the trained eye of a massage therapist, it is not difficult to identify the problem areas of
different athletes. ``Usually, all I have to do is look at your body and I can tell what type of
athlete you are,'' said Muriel Hattori, a massage therapist at the Spa at Sawgrass in Ponte Vedra
Beach, Fla.

Beyond the physiology of how a massage alters the state of an athlete's body, some massage
therapists try to identify measured improvements to performance. ``I tell serious golfers that I may
be able to add 20 yards to their golf swing,'' Ms.~Hattori said. She boasted of helping one marathon
runner shave eight minutes off a previous best time after the woman visited her once a week for
about six to eight weeks as part of her training.

Ms.~Hattori typically starts with two Swedish techniques: effleurage (smooth, long strokes) and
petrisage (a kneading motion). After that, she may use Shiatsu, a Japanese method involving pressure
from fingers and palms.

At times, should Ms.~Hattori need more leverage, she will have her subjects lie on the floor so that
she can put almost the entire weight of her body on a specific area. She is adamant that not every
treatment she doles out to elite athletes requires some measure of pain.

``A really good therapist knows exactly when to pull back,'' she said.

\section{For BlackBerry, Obama's Devotion Is Priceless}

This week, Michael Phelps signed a deal worth more than \$1 million to advertise Mazda in China.
Jerry Seinfeld earned a reported \$10 million to appear in Microsoft's recent television campaign.

But the person who may be the biggest
celebrity\index{celebrity}\hypertarget{celebrity}{}\footnote{\textbf{celebrity}:$[$si\textprimstress
lebriti$]$. \textit{n}. (尤指娱乐界的)名人,名流.\hyperlink{celebrity}{\textasciicircum}}
pitchman\index{pitchman}\hypertarget{pitchman}{}\footnote{\textbf{pitchman}:$[$\textprimstress
pit\esh m\schwa n$]$. \textit{n}. (N. Amer. informal)a person delivering a sales pitch
\hyperlink{pitchman}{\textasciicircum}} in the world is not earning a penny for his work.

President-elect Barack Obama has repeatedly said how much his BlackBerry means to him and how he is
dreading the prospect of being forced to give it up, because of legal and security concerns, once he
takes office.

``I'm still clinging to my BlackBerry,'' Mr.~Obama said Wednesday in an interview with CNBC and The
New York Times. ``They're going to pry it out of my hands.''

What could the ``BlackBerry president'' charge for his plugs of the device if he were not a public
servant? More than \$25 million, marketing experts say, and maybe as much as \$50 million.

``This would be almost the biggest endorsement deal in the history of endorsements,'' said Doug
Shabelman, the president of Burns Entertainment, which arranges deals between celebrities and
companies. ``He's consistently seen using it and consistently in the news arguing -- and arguing
with issues of national security and global welfare -- how he absolutely needs this to function on a
daily basis.''

Mr.~Obama is an ideal marketing representative, other agents say -- popular, constantly in the news
and explicit about his attachment to the product.

``You always want the celebrity to be a good fit with your brand, and is anybody considered a better
communicator right now than Barack Obama, or a better networker?'' said Fran Kelly, the chief
executive of the advertising agency Arnold Worldwide, who estimated that an endorsement by Mr.~Obama
would be worth \$25 million. ``It couldn't have a better spokesperson.''

Mr.~Shabelman put the value even higher, at \$50 million or more, because the endorsement is
worldwide.

``The worth to a company to have the president always talking about a BlackBerry and how it
absolutely is a necessity to keep in touch with reality?'' he said. ``Think about how far the
company has come if they're able to say, 'The president has to have this to keep in touch.' ''

The maker of the BlackBerry, Research in Motion, recently introduced advertising campaigns and
products like the touch-screen Storm that are meant to position BlackBerry as not just a business
device but a consumer product like the iPhone. The company, which declined to comment on Mr.~Obama's
enthusiasm for its product, also struck a sponsorship deal with John Mayer, a popular guitarist but
hardly the leader of the free world.

``The most powerful man in the country is saying, at this moment, basically, I can't live without
mine,'' Lori Sale, the head of artist marketing at the agency Paradigm, which pairs actors like
Adrien Brody and Katherine Heigl with advertisers. ``It represents their now complete and final
crossover to a device that people adore.''

Ms.~Sale said that Mr.~Obama had essentially participated in what is called a satellite media tour
for BlackBerry by discussing the product with reporters. Just a single day of a media tour, ``with
the most A-list of A-list of A-list, would probably be 10 to 15 million dollars,'' she said.

That he is not paid to promote BlackBerry is even better for R.I.M. ``What makes it even more
valuable than that is how authentic it is,'' she said.

Mr.~Kelly said the endorsement went both ways: while Mr.~Obama was doing a lot for BlackBerry,
BlackBerry had helped Mr.~Obama's image by making his message seem more relevant.

``The BlackBerry anecdotes are a huge part of Obama's brand reputation,'' he said. ``It positions
him as one of us: he's got friends and family and people to communicate with us, just like all of
us. And it positions him as a next-generation politician.''

Inevitably, perhaps, marketing executives dream about creating an ad featuring the president-elect,
something Gene Liebel, a partner in the Brooklyn agency Huge, said would be a ``fantasy
assignment.''

Asked what tagline he might use for the campaign, Mr.~Liebel repeated one his employees had thought
up: ``If Blagojevich can pick my replacement, I can pick my device.''

R. Vann Graves, the chief creative officer of the UniWorld Group, suggested a campaign showing
Mr.~Obama in the Oval Office. ``In the foreground, you have the desk, but instead of having the
proverbial red phone, you have a red BlackBerry,'' Mr.~Graves said, with the tagline ``Shot
Caller.''

Matt Reinhard, the executive creative director of DDB Los Angeles, suggested Apple try to steal
Mr.~Obama away from BlackBerry as a spokesman for the iPhone.

The message could be, ``It's time for change,'' Mr.~Reinhard said.

\section{Bush's Last Press Conference: Full of Disappointment}

In the current Administration's waning days, Americans have struggled to find a single word that
would encapsulate history's judgment on the two-term presidency of George W. Bush. The left has
offered \emph{disastrous} , citing the damage they see inflicted on the country by Bush's foreign
policy and economic stewardship. The right has countered with \emph{secure}, arguing that another
9/11 was prevented by Bush's taking the fight to terrorists at home and abroad. But in what the
White House says will be his final press conference on Monday, President Bush himself provided the
word everyone has been looking for: \emph{disappointment}.

The President used the word in one sense or another more than a dozen times in the course of his
parting exchange with the White House media corps. But it was the quality, rather than the quantity,
of its use that was most telling. The more he uttered \emph{disappointment}, the more fraught it
sounded, until it was delivered not just with his signature shoulder-hunching emphasis but with a
kind of protestation that seemed to carry the full weight of his historic fall from nearly 90\%
approval ratings after 9/11 to his current tally of less than 30\%, a record low. (Read ``The Bush
Presidency, Eight Years Later.'')

Bush was asked yet again if he thought he had made any mistakes. As he has done since John Dickerson
first asked him that question four years ago, the President ran for the safety of history. ``There
is no such thing as short-term history,'' he said, and he laid out his familiar assertion that his
presidency will look different to historians than it does in its current historically unpopular
state.

Bush then broke with his own tradition and weighed in on some mistakes. The ``Mission Accomplished''
banner brandished during his aircraft-carrier appearance two months after the invasion of Iraq gave
the wrong impression about his and his Administration's assessment of progress in the war, he said.
He then referred obliquely to mistakes in some of his own ``rhetoric''; Bush has said that his vow
to catch Osama bin Laden ``dead or alive'' and his challenge to America's adversaries to ``bring 'em
on,'' among other cavalier comments, were unhelpful, and that is presumably what he was hinting at
here.

But Bush quickly moved on to things he wasn't sure he would count as mistakes; instead, he labeled
them ``disappointments.'' Among things Bush found disappointing: the abuse of prisoners at Abu
Ghraib, the failed response to Hurricane Katrina and the fact that there were no weapons of mass
destruction in Iraq after all. As the press conference continued, Bush kept coming back to the word.
On the political environment in the capital, he said, ``I am disappointed by the tone in Washington,
D.C.'' He even predicted that Barack Obama will on occasion feel the same way. ``There'll be
disappointments, I promise you,'' he said. ``He'll be disappointed. Sometimes the biggest
disappointments will come from your so-called friends.''

Even during the press conference, Bush appeared to recognize that he was overusing the word. While
looking back at parts of his presidency that had fallen short, the President asserted that he wasn't
feeling sorry for himself, and that to do so would be unseemly. He raised the most recent crisis to
hit the country -- the economic crisis -- and said he scorned the idea of the ``burden of office.''
``Why'd the financial collapse have to happen on my watch?'' he mocked. ``It's just pathetic, isn't
it, self-pity?'' (Read ``Bush's Last Days: The Lamest Duck.'')

In the end, though, there's a difference between self-pity and self-reflection, and it's not clear
that Bush has made the distinction. True, he deserves credit for speaking so bluntly about so many
of the things that went wrong during his presidency. And he is clearly working hard to understand
what he might have done differently: he laid out in detail how he had reflected on whether or not he
should have landed Air Force One in Louisiana after Hurricane Katrina, and argued passionately that
in retrospect, he made the right decision in not burdening local officials with his presence.

But there is no shortage of observers, some of them historians, who are willing to point out where
Bush's presidency went wrong. His over-reliance on a cadre of ideological advisers who steered him
in the wrong direction is often the first error cited by critics. Vice President Dick Cheney's
dominance led Bush to many of the decisions he now qualifies as disappointments, as did Donald
Rumsfeld's bullying leadership at the Pentagon. Bush's own ideological inclinations against
regulation certainly contributed to the financial crisis. And his inexperience in foreign affairs
made him unrealistic about what freedom and democracy actually mean in much of the rest of the
world.

But Bush, by his own admission, is still struggling to get a handle on where he went wrong. Asked a
follow-up question about why Washington had remained so partisan despite his promise eight years ago
to be a ``uniter, not a divider,'' Bush said, ``I don't know,'' and suggested asking others. Even
his reaching for the safety of history reflects a kind of myopia. In that sense, Bush's final press
conference was most revealing for what it showed about his inability to accept responsibility for
his presidency. The difference between Bush's mistakes and his disappointments may just be that he
hasn't yet taken ownership of the latter. But the American people have no difficulty connecting the
failures on Bush's watch with the President's mistakes, which is why \emph{disappointment} is the
word they were looking for.

\section{Bush's Last Days: The Lamest Duck}

We have ``only one President at a time,'' Barack Obama said in his debut press conference as
President-elect. Normally, that would be a safe assumption -- but we're learning not to assume
anything as the charcoal-dreary economic winter approaches. By mid-November, with the financial
crisis growing worse by the day, it had become obvious that one President was no longer enough (at
least not the President we had). So, in the days before Thanksgiving, Obama began to move -- if not
to take charge outright, then at least to preview what things will be like when he does take over in
January. He became a more public presence, taking questions from the press three days in a row. He
named his economic team. He promised an enormous stimulus package that would somehow create 2.5
million new jobs, and began to maneuver the new Congress toward having the bill ready for him to
sign -- in a dramatic ceremony, no doubt -- as soon as he assumes office.

That we have slightly more than one President for the moment is mostly a consequence of the
extraordinary economic times. Even if George Washington were the incumbent, the markets would want
to know what John Adams was planning to do after his Inauguration. And yet this final humiliation
seems particularly appropriate for George W. Bush. At the end of a presidency of stupefying
ineptitude, he has become the lamest of all possible ducks. (See TIME's best pictures of Barack
Obama.)

It is in the nature of mainstream journalism to attempt to be kind to Presidents when they are
coming and going but to be fiercely skeptical in between. I've been feeling sorry for Bush lately, a
feeling partly induced by recent fictional depictions of the President as an amiable lunkhead in
Oliver Stone's W. and in Curtis Sittenfeld's terrific novel American Wife. There was a photo in the
New York Times that seemed to sum up his current circumstance: Bush in Peru, dressed in an alpaca
poncho, standing alone just after the photo op at the Asia Pacific Economic Cooperation forum, with
various Asian leaders departing the stage, none of them making eye contact with him. Bush has that
forlorn what-the-hell-happened? expression on his face, the one that has marked his presidency at
difficult times. You never want to see the President of the United States looking like that.

So I've been searching for valedictory encomiums. His position on immigration was admirable and
courageous; he was right about the Dubai Ports deal and about free trade in general. He spoke well,
in the abstract, about the importance of freedom. He is an impeccable classicist when it comes to
baseball. And that just about does it for me. I'd add the bracing moment of Bush with the bullhorn
in the ruins of the World Trade Center, but that was neutered in my memory by his ridiculous,
preening appearance in a flight suit on the deck of the aircraft carrier beneath the ``Mission
Accomplished'' sign. The flight-suit image is one of the two defining moments of the Bush failure.
The other is the photo of Bush staring out the window of Air Force One, helplessly viewing the
destruction wrought by Hurricane Katrina. This is a presidency that has wobbled between those two
poles -- overweening arrogance and paralytic incompetence.(President Bush in the Middle East.)

The latter has held sway these past few months as the economy has crumbled. It is too early to rate
the performance of Bush's economic team, but we have more than enough evidence to say, definitively,
that at a moment when there was a vast national need for reassurance, the President himself was a
cipher. Yes, he's a lame duck with an Antarctic approval rating -- but can you imagine Bill Clinton
going so gently into the night? There are substantive gestures available to a President that do not
involve the use of force or photo ops. For example, Bush could have boosted the public spirit -- and
the auto industry -- by announcing that he was scrapping the entire federal automotive fleet,
including the presidential limousine, and replacing it with hybrids made in Detroit. He could have
jump-started -- and he still could -- the Obama plan by releasing funds for a green-jobs program to
insulate public buildings. He could start funding the transit projects already approved by Congress.

In the end, though, it will not be the creative paralysis that defines Bush. It will be his
intellectual laziness, at home and abroad. Bush never understood, or cared about, the delicate
balance between freedom and regulation that was necessary to make markets work. He never understood,
or cared about, the delicate balance between freedom and equity that was necessary to maintain the
strong middle class required for both prosperity and democracy. He never considered the complexities
of the cultures he was invading. He never understood that faith, unaccompanied by rigorous
skepticism, is a recipe for myopia and foolishness. He is less than President now, and that is
appropriate. He was never very much of one.

\section{For Obama, Rare Chance for Bold Start on Big }

WASHINGTON -- President-elect Barack Obama is well on his way to finding the silver lining in the
economic storm he is inheriting.

The two-year, \$825 billion economic recovery plan taking shape in Congress includes billions of
dollars for renewable energy and a national electricity grid to distribute it, lower taxes for all
Americans but the affluent, computerized medical records and modernized schools. These are all down
payments on Mr.~Obama's ambitious campaign promises, affording him an opportunity few new presidents
have had. Not since Franklin D. Roosevelt at the depths of the Great Depression has a president
entered office with a bipartisan green light to spend and cut taxes so much.

The House and Senate are putting their stamp on the product -- shaving the cost on some proposals
like the power grid and rejecting a few, notably Mr.~Obama's call to give businesses a \$3,000 tax
credit for every new hire. But to a remarkable degree, the package reads like an Obama campaign
checklist, though he never put a comprehensive stimulus blueprint on paper but instead publicly and
privately promoted his priorities.

While intended for two years, the recovery plan, at \$825 billion, is nearly the size of the federal
government's annual discretionary budget for almost everything other than Social Security, Medicare
and Medicaid.

By comparison, Bill Clinton came into office in 1993 seeking just \$16 billion for an economic
stimulus. A Congress controlled by deficit-conscious Democrats refused to give it to him.

Mr.~Obama is moving on other fronts to make good on promises quickly, aware that any president's
first year is typically the most productive, and that his popularity at his inaugural could well be
at its peak.

Working with a Congress controlled by his party, he expects soon after taking office on Tuesday to
sign laws expanding a program of health care for low-income children and taking aim at pay
discrimination against women. Mr.~Obama is also expected to use his executive authority to quickly
revive federal financing for embryonic stem-cell research.

With new authority from Congress to spend the second half of a \$700 billion bailout program,
Mr.~Obama plans to do more than the Bush administration to press financial institutions to help
struggling homeowners avert foreclosure and rekindle credit to individuals and businesses.

``He is going to have a strong message for the bankers,'' his senior adviser David Axelrod said
Sunday on ``This Week'' on ABC. ``We want to see credit flowing again. We don't want them to sit on
any money that they get from taxpayers.''

Democrats expect the stimulus package to be on Mr.~Obama's desk by Feb. 13. ``First, it's going to
play a significant role in turning the economy around,'' said Rahm Emanuel, who will be White House
chief of staff and has been lobbying his former colleagues in Congress for the Obama agenda.

But beyond its stimulating effect, Mr.~Emanuel said, the package will advance ``every one of the
policy goals'' Mr.~Obama laid out in his domestic agenda for change in the campaign: energy
independence, reducing health care costs, improving education and helping low-wage and middle-income
workers.

For example, he cited Mr.~Obama's promise to spur hospitals' and doctors' use of information
technology to improve care and cut costs. The Obama team is expecting more than \$20 billion in the
final legislation toward the estimated \$50 billion cost of wiring providers nationwide. ``We're
halfway toward a goal that's been debated for 10 to 15 years,'' Mr.~Emanuel said.

Yet challenges across the board threaten the big expectations Mr.~Obama has stoked.

Money has not been the only hurdle for many of his priorities. The medical technology initiative,
for instance, must overcome significant privacy concerns that civil libertarians, patients' groups
and others have.

Also, for all the attention to Mr.~Obama's initiatives, more than half of the roughly \$550 billion
in two-year spending -- roughly \$275 billion more is for tax cuts -- would simply preserve the jobs
of teachers, firefighters, public health workers and other local government employees by sending
relief to the states, said Scott Lilly, a former senior Congressional aide who is now at the Center
for American Progress, a liberal research group.

As big as the package will be, some liberals and conservative economists fear it is not enough,
which would endanger what is now Mr.~Obama's foremost promise: to get the economy moving again.
``One of the big problems is that the overall economy is weaker than a package of this size can
adequately address,'' Mr.~Lilly said.

Once the economy does start to recover, long-term financing will be in question for Mr.~Obama's
energy, education and health initiatives as he and Congress turn to reducing budget deficits.

Antipoverty groups are concerned about the future of proposals to expand tax breaks to workers who
pay payroll taxes but are too poor to owe income taxes, and to extend Medicaid to workers without
health care coverage who lose their jobs. Advocates worry that some of the proposals least likely to
be made permanent are those that are most beneficial to low-income families.

Still, advocates say they are pleased that Mr.~Obama is keeping a promise to help change
Depression-era rules on unemployment compensation to provide aid to more low-wage and part-time
workers who lose jobs. The relief to states gives them incentives to make the changes.

Environmental groups say they are thrilled by the initial subsidies for clean energy development and
for jobs to weatherize homes and public buildings. ``We're looking at this as something to build on,
instead of looking at it as we've had to do in the past as, What bad things do we have to stop?''
said David Willett, national spokesman for the Sierra Club. ``And that's a good change.''

Dan Weiss, an environmentalist at the Center for American Progress predicted that the recovery plan
``will turbocharge energy efficiency and renewable energy technologies.''

Assuming that the projected jobs are created, said Melinda Pierce, chief lobbyist for the Sierra
Club, ``there will be continued commitment'' by private and public entities.

Even the more traditional stimulus spending, like that for job-providing road construction, has a
twist reflecting the Obama agenda. The roughly \$30 billion for road and bridge building will favor
repairs over new construction, Democrats say. Repairs can be addressed faster, getting money into
the economy quickly. But they are also the choice of environmentalists and the National Association
of Realtors, which together oppose new roadways that promote urban sprawl and fuel consumption.

Education from preschool through college is also shaping up as a big winner, with \$141.6 billion in
the House bill. Supporters promote the job-creating potential of education spending not just for the
short-term, insofar as it is a down payment on Mr.~Obama's promise to stem ``the dropout crisis''
and help young Americans become productive taxpayers.

``The down payment actually builds a lot of the proposed 'education house,' '' said Bob Wise, the
former West Virginia governor who is now president of the Alliance for Excellent Education. ``This
economic stimulus package shows that as we shift from an industrial to an information economy,
education is the new currency.''

Mr.~Wise cited a recent study that said that cutting dropout rates in half, for about \$5 billion a
year, would produce \$45 billion in new tax revenues and savings on expenses like welfare and
incarcerations.

Similarly, Democrats are trumpeting the economic impact of other provisions that depart from
standard stimulus spending on things like road construction and jobless aid.

For example, Mr.~Obama is likely to get at least \$6 billion of the \$10 billion he sought toward
his campaign promise of universal broadband service to extend Internet access to rural areas and
other regions lacking high-speed service. Each \$1 investment, Democrats say, returns \$10 to the
economy through increased productivity.


\section{China TV Network Apologizes for Fire}

BEIJING -- China's national television network on Tuesday blamed an illegal fireworks display by its
employees for igniting a blaze that destroyed a futuristic luxury hotel and theater here.

In a statement posted on its Web site, the network, China Central Television, said the illegal
pyrotechnics on Monday, the final night of the Lunar New Year celebrations, were staged too close to
the unfinished Mandarin Oriental Hotel, which is part of the network's headquarters complex. The
network apologized for ``the severe damage the fire caused to the country's property.''

Xinhua, the official news agency, reported Tuesday that one firefighter had died from smoke
inhalation and that six firefighters and a construction worker had been injured.

The apology was a rare gesture of contrition by the powerful state-owned network.

While the cause of the fire seemed clear, many questions remained about why a building being
constructed with fireproof materials was so quickly and thoroughly engulfed by flames.

During a news conference on Tuesday, Luo Yuan, a spokesman for the Beijing Municipal Fire Brigade,
said strong winds, toxic fumes and a lack of working sprinklers hampered efforts to extinguish the
fire, which began on the building's roof and spread to the lower floors.

After examining photographs of the blaze, Jonathan Barnett, a fire protection engineer in New York
who has studied numerous skyscraper fires, said it appeared that the flames were fed by insulating
foam panels along the facade. Although such material is combustible, in a finished building the foam
is sandwiched between fireproof materials like wall board and glass.

``It may have been an issue of the construction not being complete,'' Mr.~Barnett said.

Jill Kluge, a spokeswoman for the Mandarin Oriental Hotel Group, said company investigators had yet
to be allowed on the site. Messages left at the offices of Rem Koolhaas and Arup, an engineering
firm involved in the building's construction, were not answered on Tuesday.

Beijing residents who wanted to see the smoking shell of the hotel had a harder time on Tuesday
finding images of the fire on the Internet, on television or in the city's newspapers.

There were no pictures on the front page of The Beijing News. On Tuesday morning, the home page of
Xinhua featured a photo from another event: a stampede in South Korea that left four people dead.
Throughout the day, CCTV's brief bulletins about the blaze omitted images of the burning tower. By
evening, the newscast skipped the story entirely.

Even before the flames had been put out early Tuesday, pictures of the burning hotel had been
removed from most of the main Internet portals serving China. In the afternoon, the story had been
largely buried, although by the evening, news of the fire was accessible on the Xinhua and CCTV Web
sites.

The network's unusual public apology and the media's skittish approach to covering the fire
suggested that the authorities were struggling with how to deal with a delicate event in the age of
cellphone cameras and YouTube.

A directive sent out by propaganda officials, which found its way to the Internet after it was
leaked, made it clear that the authorities were eager to reduce public attention to the blaze, a
colossal embarrassment that many people believe augurs poorly for the new year. ``No photos, no
video clips, no in-depth reports,'' read the memo, which instructed all media outlets to use only
Xinhua dispatches. ``The news should be put on news areas only, and the comments posting areas
should be closed.''

The Beijing Youth Daily's report, for one, was anchored by a list of the officials who rushed to the
scene, including the mayor of Beijing, the head of CCTV and the director of the Communist Party's
propaganda department.

The government could not entirely shut down coverage. In fact, many bloggers boasted that it was
citizens, armed with cellphone cameras and camcorders, who provided the first images and accounts
shortly after the fire began.

Photos were traded by means of cellphones and e-mail messages. One video circulated on the Internet
showed how the fire began after a shell from the fireworks landed on the hotel roof.

Wang Xiaofeng, a popular blogger, could not help noting that CCTV employees had accidentally created
one of the biggest stories of the year and then failed to cover it. ``They didn't feel the urgency
to report the news, even though the fire was up to their eyebrows,'' he wrote. ``In this case of
breaking news, the official media has been defeated by the citizen media.''

Even if they lamented the death of a firefighter, other bloggers were almost gleeful over the
network's misfortune. Some said they were happy to see the demise of a building that had come to
symbolize the government's Olympian extravagance. Others noted with self-satisfaction that the
charred structure was also intended to house recording studios for CCTV.

With tongue-in-cheek humor, another writer, Chaindrive, tried to find a silver lining in the fire.
The rebuilding effort, he said, would mean more jobs for unemployed migrants, more money spent on
construction materials and a lift for the economy.

``Businesses will have new customers and our government officials will have new opportunities to
take bribes,'' he wrote. ``To make up the loss, we taxpayers will pay more, but our G.D.P. will go
up and society will move forward in harmony.''

\section{Congress Reaches Deal on Stimulus Plan}

WASHINGTON -- Senate and House leaders announced Wednesday evening that they had reached agreement
on a \$789 billion economic stimulus bill, clearing the way for final Congressional action and
President Obama's signature, perhaps by the end of the week.

``The differences between the House and Senate versions, we've resolved,'' Senator Harry Reid of
Nevada, the Democratic majority leader, said in a Capitol news conference. The differences were
resolved by a lot of intense ``give and take,'' Mr.~Reid said, ``and if you don't mind my saying so,
that's an understatement.''

Hours later, House Speaker Nancy Pelosi emerged from a meeting of negotiators and said, ``We have
come to an agreement with the Senate.''

The accord reached in the early evening came after an awkward, if temporary, delay. Ms.~Pelosi was
not present at the late-afternoon news conference presided over by Mr.~Reid, even though he praised
her effusively for her role in the talks and spoke as though the deal was already iron clad.

Even after Mr.~Reid's announcement, House Democrats reportedly held out for some changes important
to them, including more money for school renovations.

By early evening, Senate and House leaders were seated at a conference table, and a short time later
Ms.~Pelosi emerged and said that the accord was indeed final. Assuming that there are no other
last-minute stumbling blocks, the path seemed clear for final Congressional action and President
Obama's signature on a package intended to pull the country out of the worst recession in years.

Before Mr.~Reid's slightly premature statement that an accord was final, negotiations had been going
on all day, following extensive talks on Tuesday night, to close the gap between the Senate and
House versions. In the end, the package that Mr.~Reid said had been agreed upon would pare back
Democrats' proposed spending on education and health programs in favor of tax cuts that were needed
to win Republican votes in the Senate.

Senator Susan Collins of Maine, a centrist Republican whose role has been crucial, said the final
package includes \$150 billion in spending on infrastructure, including transportation facilities,
and considerable tax relief. Moreover, she said, it includes significant money to aid state
governments.

Ms.~Collins also seemed to think that all of the wrinkles had been ironed out before they actually
were. ``This was a good-faith effort on both the House and the Senate's part, and it shows that,
working together, we can indeed accomplish great things,'' she said.

Senator Joseph I. Lieberman, independent of Connecticut, was another who initially thought the
agreement was more final than it was. ``Without a great spirit of compromise from the White House,
the House and the Senate, we would not be able to announce this agreement today,'' he said.

Despite intense lobbying by governors, the final deal slashed \$35 billion from a proposed state
fiscal stabilization fund, eliminated \$16 billion in aid for school construction and sharply
curtailed health care subsidies for the unemployed.

In driving down the total cost of the stimulus bill -- from \$838 billion approved by the Senate and
\$820 billion by the House -- legislators also sharply reduced proposed tax incentives for buyers of
homes and cars that held huge public appeal. Senator Collins said getting the final number to under
\$800 billion was more than symbolic; it meant ``a fiscally responsible number,'' she said.

But the final bill retained a \$70 billion tax cut that would spare millions of middle-class
Americans from paying the alternative minimum tax in 2009, which some Democrats decried as wasting a
large chunk of the bill on something that would do little to lift the economy and that Congress
would have approved regardless of the recession.

In announcing the agreement, Mr.~Reid credited the efforts of Speaker Pelosi, who he said had been
indispensable in resolving differences between the two chambers of Congress.

After huddling in the office of Ms.~Pelosi on Tuesday until nearly midnight, top White House
officials and Congressional leaders had all but ironed out the differences between the House and
Senate versions of the recovery package by noon on Wednesday.

``I think we are way down the road from where we started and I don't think there is that much more
of a distance to travel until we are able to have it put together,'' said Senator Ben Nelson,
Democrat of Nebraska who is a leader of a bipartisan group of senators whose support is so crucial
that they effectively hold veto power over the final legislation.

Even trimmed to \$789 billion, the recovery measure will be the most expansive unleashing of the
government's fiscal firepower to fight a recession in modern history. And yet it seemed almost
trifling compared with the potential price tag of \$2.5 trillion for the rescue plan for the
financial system announced on Tuesday by Treasury Secretary Timothy F. Geithner.

Even before the last touches were put to the bill, the emerging deal infuriated some Democrats who
said that President Obama and Congressional leaders had been too quick to give up on Democratic
priorities. Some critics also suggested that the final figure was too small to be effective because
of the grave condition of the American economy.

``I am not happy with it,'' said Senator Tom Harkin, Democrat of Iowa. ``You are not looking at a
happy camper. I mean, they took a lot of stuff out of education. They took it out of health, school
construction and they put it more into tax issues.''

Mr.~Harkin said he was particularly frustrated by the money being spent on fixing the alternative
minimum tax. ``It's about 9 percent of the whole bill,'' he said, ``which we were going to do later
this year in a tax bill. Why is it in there? It has nothing to do with stimulus. It has nothing to
do with recovery. This makes no sense whatsoever.''

But even as Congressional leaders and top White House officials went through the package with a
carving knife, it was clear that the three Republicans who agreed to support the bill in the Senate
wielded extraordinary power, and along with conservative Democrats in their coalition, had put a
firm stamp on the stimulus package.

For instance, even as negotiators accepted many of the Senate's reduced spending provisions, they
were careful to maintain an additional \$6.5 billion for medical research that was inserted at the
insistence of Senator Arlen Specter, Republican of Pennsylvania, who is a cancer survivor.

Republican opponents of the stimulus measure continued to criticize it on Wednesday as a bloated and
ill-designed spending bonanza by Democrats that would not help lift the economy out of recession but
would plunge future generations of Americans deeper into debt.

``Yesterday the Senate cast one of the most expensive votes in history,'' the Republican leader,
Senator Mitch McConnell of Kentucky, said. ``Americans are wondering how we're going to pay for all
this. Judging by the market reaction to Secretary Geithner's announcement yesterday and the
newspaper editorials this morning, it's clear that everyone is looking for a little more detail.''

In hammering out a final agreement, the negotiators not only had to settle on overall dollar amounts
for the various provisions but in some cases had to resolve bitter disagreements over the formulas
that would be used to divide some of the largest categories of money to be directed to state and
local governments.

The stimulus plan includes \$87 billion in federal aid to states for rising Medicaid costs, and
powerful blocs of lawmakers, largely divided between urban and rural states, had been fighting over
whether to divvy up the funds according to the traditional Medicaid reimbursement formulas or to
give extra help to states with high unemployment.

\section{A County in China Sees Its Fortunes in Tea Leaves Until a Bubbls}

MENGHAI, China -- Saudi Arabia has its oil. South Africa has its diamonds. And here in China's
temperate southwest, prosperity has come from the scrubby green tea trees that blanket the mountains
of fabled Menghai County.

Over the past decade, as the nation went wild for the region's brand of tea, known as Pu'er, farmers
bought minivans, manufacturers became millionaires and Chinese citizens plowed their savings into
black bricks of compacted Pu'er.

But that was before the collapse of the tea market turned thousands of farmers and dealers into
paupers and provided the nation with a very pungent lesson about gullibility, greed and the perils
of the speculative bubble. ``Most of us are ruined,'' said Fu Wei, 43, one of the few tea traders to
survive the implosion of the Pu'er market. ``A lot of people behaved like idiots.''

A pleasantly aromatic beverage that promoters claim reduces cholesterol and cures hangovers, Pu'er
became the darling of the sipping classes in recent years as this nation's nouveaux riches embraced
a distinctly Chinese way to display their wealth, and invest their savings. From 1999 to 2007, the
price of Pu'er, a fermented brew invented by Tang Dynasty traders, increased tenfold, to a high of
\$150 a pound for the finest aged Pu'er, before tumbling far below its preboom levels.

For tens of thousands of wholesalers, farmers and other Chinese citizens who poured their money into
compressed disks of tea leaves, the crash of the Pu'er market has been nothing short of disastrous.
Many investors were led to believe that Pu'er prices could only go up.

``The saying around here was 'It's better to save Pu'er than to save money,' '' said Wang Ruoyu, a
longtime dealer in Xishuangbanna, the lush, tea-growing region of Yunnan Province that abuts the
Burmese border. ``Everyone thought they were going to get rich.''

Fermented tea was hardly the only caffeinated investment frenzy that swept China during its boom
years. The urban middle class speculated mainly in stock and real estate, pushing prices to
stratospheric levels before exports slumped, growth slowed and hundreds of billions of dollars in
paper profits disappeared over the past year.

In the mountainous Pu'er belt of Yunnan, a cabal of manipulative buyers cornered the tea market and
drove prices to record levels, giving some farmers and county traders a taste of the country's
bubble -- and its bitter aftermath.

At least a third of the 3,000 tea manufacturers and merchants have called it quits in recent months.
Farmers have begun replacing newly planted tea trees with more nourishing -- and now, more lucrative
-- staples like corn and rice. Here in Menghai, the newly opened six-story emporium built to house
hundreds of buyers and bundlers is a very lonely place.

``Very few of us survived,'' said Mr.~Fu, 43, among the few tea traders brave enough to open a
business in the complex, which is nearly empty. He sat in the concrete hull of his shop, which he
cannot afford to complete, and cobwebs covered his shelf of treasured Pu'er cakes.

All around him, sitting on unsold sacks of tea, were idled farmers and merchants who bided their
time playing cards, chain smoking and, of course, drinking endless cups of tea.

The rise and fall of Pu'er partly reflects the lack of investment opportunities and government
oversight in rural Yunnan, as well as the abundance of cash among connoisseurs in the big cities.

Wu Xiduan, secretary general of the China Tea Marketing Association, said many na\"{i}ve investors
had been taken in by the frenzied atmosphere, largely whipped up by out-of-town wholesalers who
promoted Pu'er as drinkable gold and then bought up as much as they could, sometimes paying up to 30
percent more than in the previous year.

He said that as farmers planted more tea, production doubled from 2006 to 2007, to 100,000 tons. In
the final free-for-all months, some producers shipped their tea to Yunnan from other provinces,
labeled it Pu'er, and then enjoyed huge markups.

When values hit absurd levels last spring, the buyers unloaded their stocks and disappeared.

``The market was sensationalized on purpose,'' Mr.~Wu said, speaking in a telephone interview from
Beijing.

With its near-mythic aura, Pu'er is well suited for hucksterism. A favorite of emperors and imbued
with vague medicinal powers, Pu'er was supposedly invented by eighth-century horseback traders who
compressed the tea leaves into cakes for easier transport. Unlike other types of tea, which are
consumed not long after harvest, Pu'er tastes better with age. Prized vintages from the 19th century
have sold for thousands of dollars a wedge.

Over the past decade, the industry has been shaped in ways that mirror the Western fetishization of
wine. Sellers charge a premium for batches picked from older plants or, even better, from ``wild
tea'' trees that have survived the deforestation that scars much of the region. Enthusiasts talk
about oxidation levels, loose-leaf versus compacted and whether the tea was harvested in the spring
or the summer. (Spring tea, many believe, is more flavorful.)

But with no empirical way to establish a tea's provenance, many buyers are easily duped.

``If you study Pu'er your whole life, you still can't recognize the differences in the teas,'' said
Mr.~Wang, the tea buyer. ``I tell people to just buy what tastes good and don't worry about anything
else.''

Among those most bruised by the crash are the farmers of Menghai County. Many had never experienced
the kind of prosperity common in China's cities. Villagers built two-story brick homes, equipped
them with televisions and refrigerators and sent their children to schools in the district capital.
Flush with cash, scores of elderly residents made their first trips to Beijing.

``Everyone was wearing designer labels,'' said Zhelu, 22, a farmer who is a member of the region's
Hani minority and uses only one name. ``A lot of people bought cars, but now we can't afford gas so
we just park them.''

Last week, dozens of vibrantly dressed women from Xinlu sat on the side of the highway hawking their
excess tea. There were few takers. The going rate, about \$3 a pound for medium-grade Pu'er, was
less than a tenth of the peak price. The women said that during the boom years, tea traders from
Guangdong Province would come to their village and buy up everyone's harvest. But last year, they
simply stopped showing up.

Back at Menghai's forlorn ``tea city,'' Chen Li was surrounded by what he said was \$580,000 worth
of product he bought before the crash. As he served an amber-hued seven-year-old variety, he
described the manic days before Pu'er went bust. Out-of-towners packed hotels and restaurants. Local
banks, besieged by customers, were forced to halve the maximum withdrawal limit.

``People had to stand in line for four or five hours to get the money from the bank, and you could
often see people quarreling,'' he said. ``Even pedicab drivers were carrying tea samples and looking
for clients on the street.''

A trader who jumped into the business three years ago, Mr.~Chen survives by offsetting his losses
with profits from a restaurant his family owns in Alabama. He also happens to be one of the few
optimists in town. Now that so many farmers have stopped picking tea, he is confident that prices
will eventually rebound. As for the mounds of unsold tea that nearly enveloped him?

``The best thing about Pu'er,'' he said with a showman's smile, ``is that the longer you keep it,
the more valuable it gets.''



\section{China Detains Building Chief in TV Complex Blaze}

BEIJING -- In a spate of arrests announced Thursday, Beijing officials put the blame for a Monday
fire that destroyed part of the government's spectacular new media complex squarely on the shoulders
of the state-run television network.

The police detained 12 people, including the chief of construction for the new headquarters of China
Central Television, or CCTV, and eight employees of the firm the broadcaster hired to put on an
illegal fireworks show that the authorities said ignited the blaze.

The fire gutted a nearly completed 520-foot-high futuristic hotel that was part of CCTV's new \$1.1
billion headquarters, sometimes described as an architectural symbol of China's rising power. One
firefighter died, and seven people were injured.

Many questions remain about the fire, including how fireworks could have ignited such an inferno and
why the flames seemed to spread unchecked through a modern tower, designed by a world-renowned
architect, that would presumably have been outfitted with state-of-the-art fire retardant systems.

The blaze, for which CCTV officials have publicly apologized, highlighted the clash between old and
new in a city trying to blend ancient traditions with breathtaking development. Monday was the
Lantern Festival, the final night of China's Lunar New Year celebrations, when huge fusillades of
fireworks blanketed the city for hours.

Perhaps nowhere else are people as crazy about firecrackers as in China, where gunpowder was first
invented and more than four-fifths of the world's fireworks are produced. Weddings, funerals and
holidays are all commemorated with deafening booms, flashes of light and billowing clouds of black
smoke.

But the devastating fire on Monday has added fuel to a long-running debate about whether fireworks
should be allowed in the center of cities like Beijing, where the risk of injury, death or
calamitous destruction of property is comparatively great.

In a letter to Beijing authorities published this week, Pan Shiyi, one of Beijing's best-known
developers, said that fireworks displays by citizens might be suitable for rural cultures, but not
for a dense, modern city like Beijing.

``This is a huge lesson, as well as huge loss,'' Mr.~Pan wrote Wednesday in a blog. ``In a city as
big as Beijing, we really shouldn't be allowed to set off fireworks.''

Citing safety, noise and pollution concerns, Beijing banned fireworks within the city center from
1993 to 2005, and nearly 300 other cities also instituted bans. The safety argument was compelling.
From 1985 to 2005, China averaged 467 deaths a year from fireworks accidents. In contrast, in the
United States, with nearly a quarter of China's population, only 11 people died in fireworks
accidents in 2006.

But the prohibitions provoked an angry reaction among urban residents, who complained that a
2,000-year-old tradition was dying out and that the Lunar Festival held no delight without
fireworks. So after 12 years, Beijing and about 200 other cities relaxed the restrictions, allowing
fireworks to be set off in downtown areas on selected holidays.

Days after the blaze, the charred hulk of the tower still attracted onlookers and created
bottlenecks on the Third Ring Road, a major Beijing artery.

Zhang Xin, a 26-year-office worker who waited Wednesday on the corner of the CCTV complex for a
ride, said setting off fireworks was a dangerous, increasingly outdated custom that should be
prohibited downtown. ``Every year, something like this happens,'' he said.

Wu Huangqin, 20, said the government should organize its own fireworks displays and tighten controls
over fireworks celebrations by citizens. ``Everyone was so happy when we could set off fireworks
again after the ban,'' she said Wednesday. ``If we stop completely, we'll have no feeling of the
holiday.''

According to media reports, the fireworks that ignited Monday's blaze were not supposed to be
available to the public, and CCTV lacked the government permit required to set them off.

\section{Obama's Special Envoy Arrives in Afghanistan}

KABUL, Afghanistan -- President Barack Obama's special envoy to Afghanistan and Pakistan arrived in
Afghanistan on Thursday, the United States Embassy here said, one day after a coordinated series of
Taliban suicide attacks in Kabul underscored the deteriorating security in the capital and across
the country.

Security forces in Kabul remained on high alert Thursday, not only in preparation for the arrival of
the envoy, Richard C. Holbrooke, but also because a Taliban spokesman claimed eight bombers remained
at large in the city and were still ``looking for a chance.''

The spokesman described Wednesday's attacks as retaliation for the mistreatment and torture of
Taliban prisoners.

The suicide bombers and Taliban gunmen struck government buildings at three sites in Kabul on
Wednesday, killing at least 20 people and wounding 57. It was a complex and highly organized attack
that demonstrated the ease with which the insurgents could penetrate even a heavily fortified place
like Kabul.

At the Justice Ministry, five Taliban guerrillas armed with explosives and Kalashnikov rifles killed
two guards, stormed inside and took control of the building for more than an hour. Frightened
employees, including the justice minister, barricaded themselves in their offices while the armed
men stalked the halls for victims. At least 10 people were killed, including two who were shot in
the cross-fire between government forces and the insurgents, security officials said.

In addition to the eight bombers who struck the Justice Ministry, Taliban militants also attacked
the Education Ministry and the directorate for prisons. All eight attackers at the three sites were
killed, the Interior Ministry said.

Afterward, security forces carried the mangled bodies of the attackers out of the Justice Ministry
building and, in a sign of deep disrespect of Muslim tradition, dumped the bodies unceremoniously on
the concrete forecourt.

Earlier Thursday, Mr.~Holbrooke met with a former Pakistani prime minister and opposition leader,
Nawaz Sharif, in the Pakistani city of Lahore. His tour of the region was part of a ground-up review
of American policy in Afghanistan and Pakistan ordered by Mr.~Obama, who met with Defense Secretary
Robert M. Gates on Wednesday to discuss plans to bolster American force levels here.

The brazen nature of the Taliban attacks was certain to influence the debate among administration
officials over the strength of the militants, who control much of the countryside and have steadily
encroached on Kabul.

The attacks also highlighted the fluid and murky nature of the insurgents' ties with terrorist
networks in Pakistan's tribal areas, which Mr.~Holbrooke visited briefly on Wednesday under
Pakistani military escort.

One senior official in Washington said initial intelligence indicated that Wednesday's attack was
probably planned or supported by the Pakistan-based network of Jalaluddin Haqqani.

Mr.~Haqqani's group was also implicated in the attack on the Indian Embassy in Kabul last summer and
might have had the assistance of members of Pakistan's intelligence agency in that operation,
American officials have said.

The attacks on Wednesday were the most audacious since the embassy assault. And in an eerie echo of
the attacks in Mumbai, India, in November, which Indian and American intelligence officials say have
been traced to a Pakistani militant group, the Taliban gunmen on Wednesday sent three messages to
Pakistan seeking the ``blessing of their mastermind,'' said Amrullah Saleh, director of the Afghan
national intelligence service.

Moments later, they began ``indiscriminate killing'' inside the Justice Ministry, Mr.~Saleh said.
Officials said 21 people had been detained, but it was not clear what linked them to the attacks.

The multiple coordinated strikes cloaked Kabul, a dusty and chaotic city of four million, in panic
for the entire day. Miles of Kabul’s principal thoroughfares were blocked off, as police officers
and soldiers rushed to reinforce scores of checkpoints.

Hours later, there were fears that other bombers were still roaming Kabul. In addition to the eight
bombers who struck the Justice Ministry, the Education Ministry and the directorate for prisons.

Across the city, many streets were empty as residents were too scared to go outside. The attacks
clearly unnerved Afghan officials.

``The enemy still has the capability to bring this amount of weapons and explosives inside the city
of Kabul and find their way to government institutions,'' said Hanif Atmar, the interior minister.
He promised new and strict security measures that would be ``uncomfortable'' for residents, but
necessary. Many parts of the capital are already sectioned off for security, and foreign embassies
sit behind layers of checkpoints and blast walls.

The most confidence-shaking attack, at the Justice Ministry, began about 10 a.m., when five Taliban
fighters took over three of the building's four floors. The ministry is in the heart of the capital,
a few hundred yards from the presidential palace.

Employees locked their doors and dived for cover inside their offices. There was ``chaos on all four
floors,'' said Habib Mushakhas, a senior ministry official, after the police rushed him out of the
building. ``I heard an explosion, then a firefight. There was a lot of blood in the corridors. I saw
one dead body.''

A little more than an hour after the attack, security forces counterattacked. Scores of soldiers and
police officers rushed into the building and scaled ladders onto upper floors. More than 20 shots
were fired. Soon after, ambulances took several police officers and soldiers away, their feet
hanging off of stretchers poking out the open doors. It was not clear whether they were wounded or
dead.

Eventually, the police and soldiers retook enough of the building to begin evacuating dozens of
survivors. Then they rushed children out from the kindergarten classroom inside the ministry.

The police also began removing civilian bodies. By early afternoon they said they felt confident
that they had defeated the gunmen, and they called an impromptu news conference in the Justice
Ministry's forecourt.

But minutes later they realized that one Taliban attacker was still inside, and a handful of
different security forces -- the police, the Afghan Army and national intelligence officers -- went
searching for him. A nervous commander barked into his radio, ``Try to recognize each other, and
don't shoot our own guys.''

A radio call came from a commander inside the building. ``We've cornered him,'' he said. ``Could you
order us to shoot? We are worried because we think there are children and other civilians around.''

Two commanders outside talked. ``What should we do?'' one said. ``Shoot him!'' said the other.

Moments passed, and the commander inside the building said: ``There's nobody here. We should
attack.''

``Attack!'' came the response from a commander outside.

About 60 shots were fired over the next 20 minutes. Finally, the last gunman was dead. But so, too,
were two more civilians whose bodies were brought outside and laid on stretchers. Security officials
later said two hostages were killed in the cross-fire as government forces killed the last gunman.

All of the gunmen had worn suicide-bomb vests, but none of the vests had detonated. The government
forces had defused and stripped them from the bodies, which bore large gashes and bullet holes, or
had arms ripped partly from shattered shoulders.

As security forces fought to take back control of the Justice Ministry, a single Taliban suicide
bomber was killed as he tried to attack the Education Ministry.

Across town, two more Taliban bombers killed and wounded more people at the Prisons Department. One
bomber blew himself up at a security checkpoint in front of the prisons building, while witnesses
said the other bomber used the distraction to run inside.

Gholam Farouk Wafa, a 35-year-old policeman, said he was attending a training class inside with 60
other policemen when they saw a clean-shaven man with a large backpack come to the door. One of the
policemen fired two shots at him, and the man fled upstairs, where he detonated his bomb, Mr.~Wafa
said.

Reporting was contributed by Lynsey Addario, Abdul Waheed Wafa and Sangar Rahimi from Kabul; Taimoor
Shah from Kandahar, Afghanistan; David E. Sanger and Eric Schmitt from Washington; and Mark McDonald
from Hong Kong.

\section{To Fix Detroit, Obama Is Said to Drop Plan for 'Car Cza'}

DETROIT -- President Obama has dropped the idea of appointing a single, powerful ``car czar'' to
oversee the revamping of General Motors and Chrysler and will instead keep the politically delicate
task in the hands of his most senior economic advisers, a top administration official said Sunday
night.

Mr.~Obama is designating the Treasury secretary, Timothy F. Geithner, and the chairman of the
National Economic Council, Lawrence H. Summers, to oversee a presidential panel on the auto
industry. Mr.~Geithner will also supervise the \$17.4 billion in loan agreements already in place
with G.M. and Chrysler, said the official, who insisted on anonymity.

The official also said that Ron Bloom, a restructuring expert who has advised the labor unions in
the troubled steel and airline industries, would be named a senior adviser to Treasury on the auto
crisis.

The unexpected shift comes as G.M. and Chrysler race to complete broad restructuring plans they must
file with the Treasury by Tuesday. The companies' plans are required to show progress in cutting
long-term costs as a condition for keeping their loans.

The administration official said the president was reserving for himself any decision on the
viability of G.M. and Chrysler, both of which came close to bankruptcy before receiving federal aid
two months ago.

One of President Obama's top advisers said Sunday that the administration had not ruled out a
government-backed bankruptcy as a means to overhaul the automakers.

``We're going to need a restructuring of these companies,'' the adviser, David Axelrod, said on
``Meet the Press'' on NBC. He added that a turnaround of the companies would ``require sacrifice not
just from the auto workers but also from creditors, from shareholders and the executives who run the
company.''

The automakers had been expecting the appointment of a car czar to break the logjam of negotiations
with the United Auto Workers over the finances of a retiree health care trust, and with bondholders
about reducing the companies' debt.

Mr.~Bloom is known for bringing his Wall Street experience as an investment banker to an advisory
role as the ``in-house'' banker for the steel workers' union. With the auto union locking horns with
bondholders in the G.M. revamping deliberations, Mr.~Bloom appears to bring credibility with both
the union and the debtors. Mr.~Bloom could not be reached for comment Sunday night.

Another senior administration official said that Mr.~Obama had considered appointing a car czar, and
among those considered for the job was the private equity executive Steven Rattner. It was not clear
why the administration changed course or whether Mr.~Rattner would have a role on the task force.

The panel, called the Presidential Task Force on Autos, will draw officials from several agencies
including the departments of Treasury, labor, transportation, commerce and energy, according to the
administration official.

Many members of the task force have already been working closely with G.M. and Chrysler on the
viability plans they are preparing for the government.

G.M. and Chrysler are both expected to request more loans to stay solvent during what is shaping up
as another miserable year for auto sales.

Chrysler's chairman, Robert L. Nardelli, has said his company needs another \$3 billion in addition
to the \$4 billion loan it received in January.

G.M. originally asked for \$18 billion in aid in December. G.M. has borrowed \$9.4 billion so far
and is scheduled to receive another \$4 billion, if the Treasury is satisfied with its revamping
plan.

G.M. said in a statement that it welcomed the new task force and that it looked forward to sharing
its plan ``to restore our company to viability and to meet the requirements of its loan
agreements.''

Representatives of Chrysler could not be reached for comment on Sunday night.

The administration official who disclosed the change in Mr.~Obama's plans for oversight of the auto
industry said the group would review the companies' submissions for a week or two before responding
publicly. Until then, the auto makers are expected to continue talks with the union and other
stakeholders.

On Sunday afternoon, G.M. and the U.A.W. resumed discussions in Detroit about reducing the company's
labor costs, a person with direct knowledge of the talks said. This person, who spoke on condition
of anonymity because the discussions are private, characterized the talks Sunday evening as
``intense'' but did not indicate that an agreement was imminent.

The U.A.W. had walked away from the bargaining table late Friday as the two sides clashed over how
to cover retiree health care costs.

U.A.W. leaders in December agreed to help the automakers by delaying when the companies are required
to make multibillion-dollar payments into a new trust fund designed to pay for retiree health
coverage.

The Ford Motor Company is not taking federal aid, and therefore does not need to submit plans for
approval. But Ford, which lost \$14.6 billion in 2008, the most in its history, is expected to ask
the U.A.W. for whatever concessions are granted to G.M. and Chrysler.

Both G.M. and Chrysler are likely to outline deep cuts in jobs, plants and models in their
restructuring plans. One G.M. executive said the automaker is proposing a much smaller company with
fewer brands and far fewer people.

G.M. and Chrysler recently extended buyout and early retirement offers to nearly all of their 90,600
hourly workers as they try to eliminate factory jobs and replace older workers making about \$28 an
hour with new hires who can be paid half as much.

G.M. announced plans last week to cut 10,000 white-collar jobs worldwide, including 3,400 in the
United States. It said that salaries for those who remain on staff would be cut by as much as 10
percent through at least the end of 2009.

Over all, automakers are expected to sell between 10 million and 11 million vehicles in the United
States this year, far below the 16.2 million they sold in 2007. G.M. said last week that the
two-year drop is roughly equal to the capacity of 24 assembly plants.

\section{Former eBay Chief Tries New Bit's Political.}

SAN FRANCISCO -- Meg Whitman, a former chief executive of eBay, once said that running the Internet
auction site was like being the mayor of a large city, with the mix of politics, competing
constituencies and widespread resistance to change.

Now Ms.~Whitman, 52, says she is ready to be the governor of California, a state nearly paralyzed by
its political and fiscal problems. But with her legacy at eBay not clear cut, she is trying to
define her experience in the most favorable terms as she explores a run for the Republican
nomination in 2010.

``I'm pretty convinced that the next governor of California is going to have to plant herself in
Sacramento 24/7, 365 days a year,'' Ms.~Whitman said in a recent interview. ``It's going to require
listening, understanding policy alternatives, and building collaboration and relationships that
allow the state to move forward. It's another eBay.''

Ms.~Whitman joined eBay in 1998 when it had 30 employees and \$4 million in revenue and was mainly
known as an online swap meet for gewgaws and bric-a-brac like Beanie Babies. By the time she left
last year, eBay was a Fortune 500 business with 15,000 employees and \$8 billion in sales.

The story of how Ms.~Whitman helped make eBay the largest e-commerce site on the Web -- and turned
herself into a business celebrity who appeared on the cover of many magazines -- is filled with long
hours, hard work and the constant wooing of mom-and-pop businesses.

Ms.~Whitman said she ``couldn't be prouder'' of her track record, in particular ``the ecosystem of
entrepreneurs that eBay enabled to build their own businesses.''

But in the past two years, eBay has been mired in a pronounced slowdown in growth and a painful
transition. Buyers have fled the online marketplace, which many say is compromised by forgeries,
disreputable sellers and an unpredictable buying experience, and the company's stock has lost
two-thirds of its value.

``For a long period of time, eBay generated revenue growth by raising fees on sellers,'' said Scot
Wingo, the founder of Channel Advisor, which helps small businesses sell on the Internet. ``Now
everyone is starting to realize that was unsustainable.''

Ms.~Whitman also led eBay's 2005 purchase of the Internet calling service Skype, in part based on
the belief that eBay buyers and sellers would want to talk to each other to close deals. Most did
not, and less than two years later, eBay acknowledged the mistake and wrote off more than half of
the \$2.6 billion purchase price.

Mr.~Wingo said Ms.~Whitman's successor, John J.~Donahoe, caught ``the brunt of the blame, but a lot
of sellers blame Meg as well.''

``There is enough venom to go around for everybody,'' he said.

Ms.~Whitman, who announced on Feb.~9 that she had formed an exploratory campaign committee, said she
was motivated to run by her love for California and a reluctance to see it ``spiral downward.'' But
some former colleagues suggest that she may be unprepared for the glare of the political stage,
saying she took her public setbacks very personally, including her unsuccessful candidacy for the
top job at Disney after Michael Eisner left in 2005.

Ms.~Whitman dismisses that concern and says any negative attention would be harder on her husband,
Dr.~Griffith Harsh, a brain surgeon at Stanford, and their two sons, ages 20 and 23. She said that
as an adviser to the 2008 presidential campaigns of Mitt Romney and, later, Senator John McCain of
Arizona, the Republican nominee, she was fully aware of the perils of politics.

``I don't think you get into this game unless you have a very thick skin and can take it,'' she
said. ``It's just the nature of the industry, if you will, and I'm as prepared as anyone can be.''

Ms.~Whitman predicted that her campaign could cost \$150 million, much of it coming from her own
fortune. (Forbes most recently estimated it at \$1.4 billion.)

On the Republican side, Ms.~Whitman would face a considerable challenge from the state insurance
commissioner, Steve Poizner, one of the few in his party to win statewide office recently. Like her,
Mr.~Poizner has deep Silicon Valley pockets. A former congressman, Tom Campbell, is also a likely
contender for the nomination to succeed the Republican incumbent, Gov. Arnold Schwarzenegger, who is
barred by term limits from running again.

There are several big names on the Democratic side, including Attorney General Jerry Brown, Mayors
Gavin Newsom of San Francisco and Antonio R. Villaraigosa of Los Angeles, and perhaps even Senator
Dianne Feinstein, who has not ruled out a bid.

But analysts are not counting Ms.~Whitman out. They point out that she has plenty of money and is
running in a primary that so far lacks an ideological conservative, which allows her to remain close
to the political center and more palatable to independents and Democrats in the general election.

Bill Whalen, a researcher for the Hoover Institution, said Ms.~Whitman would also benefit in a
general election from her support for abortion rights, a traditional wedge issue in California
elections that Democrats have used against Republicans.

``It could defang the abortion issue and force Democrats to come up with a different playbook to go
after her,'' said Mr.~Whalen, who was a speechwriter for former Gov. Pete Wilson, a Republican.

Ms.~Whitman can expect varying levels of support from her former colleagues in Silicon Valley.
Pierre Omidyar, the billionaire founder of eBay and a contributor to many Democratic causes, said in
an e-mail message that working with her at the company ``was a real joy'' but that they had
``substantially different views on a number of fundamental political issues.''

Others, including some who typically favor Democrats, said they would back her candidacy.

``We need somebody with fierce intelligence, good leadership and a practical approach to solving
problems,'' said Rajiv Dutta, who worked at eBay with Ms.~Whitman for 11 years in positions like
chief financial officer and president of its marketplace.

``I look at the packages of qualities which made Meg a very able business leader and think that's
exactly what the state needs,'' said Mr.~Dutta, who supported the candidacy of President Obama.

Yet Ms.~Whitman may have a harder time winning over the entrepreneurs she takes credit for helping
at eBay. Many have intensely mixed feelings toward the company.

``She will not be getting my vote, and she will not be getting the vote of anyone I'm conversant
with on eBay in California,'' said Jay Senese, a registered Republican who has sold items on eBay
for a decade from his home in Sierra Madre.

Mr.~Senese said eBay should have long ago started registering and verifying sellers on the site, as
rival Amazon does, which would have blocked the fraudulent retailers who sullied the company's
reputation.

Randy Smythe, a blogger and former eBay seller, sums up the sentiment by saying Ms.~Whitman had
``let the marketplace manage itself far too long.'' But Mr.~Smythe, a Republican living in
California, said he would probably vote for Ms.~Whitman in the primary because she was smart and ``a
capable manager.''

Even with the mixed reviews, Steve Westley, a former eBay executive who lost in the Democratic
primary for governor in 2006, said Ms.~Whitman's experience with the company would help her with
most voters.

Mr.~Westley said Californians tended to view eBay as one of the more innovative and profitable
technology companies in Silicon Valley. ``People do respect business leaders who run profitable
enterprises,'' he said. ``It's obviously one of the concerns about the current governor and
Legislature.''


\section{China Fears Tremors as Jobs Vanish From Coast}

TANJIA, China -- Tan Tianying might not look like a troublemaker, but she and millions of other
workers like her have government leaders fretting about the country's stability.

A shy, delicately built seamstress who makes aprons and coveralls in Guangzhou, Ms.~Tan, 24, is part
of an army of migrants, 130 million strong, who have flocked to cities for jobs, but whose prospects
for continued employment are increasingly dim.

As the global economic crisis deepens and the demand for Chinese exports slackens, manufacturing
jobs in the Pearl River Delta and all along the once-booming coast are disappearing at a stunning
pace. Over the last few months, more than 20 million migrant workers have been cast into the ranks
of the unemployed, depriving impoverished towns like Tanjia of the much-needed income the workers
sent home.

Since December, hundreds of employees at Ms.~Tan's uniform factory have been let go and wages have
been cut by a third as orders from the United States dry up. Last year, 2,400 factories in and
around Guangzhou closed.

``I hope I still have a job,'' Ms.~Tan said this month, a few hours before leaving Tanjia on a train
for the 10-hour ride that in recent years has carried away most of the town's working-age residents.
``I don't want to go back to being a poor farmer.''

In a nation obsessed with social harmony, the well-being of China's mobile work force has become the
top priority for a government that has long seen its fortunes tied to those of the country's 800
million rural dwellers. Mao's revolution, after all, was fueled by embittered peasants, and it has
not gone unnoticed in Beijing that decades of heady growth has fed a widening gap between urban
residents and those who live in the rural interior.

Although the government has not released updated information about rural unrest, officials have been
strategizing about how best to keep large protests and riots from spreading, should the dispossessed
grow unruly.

This week, more than 3,000 public security directors from across the country are gathering in the
capital to learn how to neutralize rallies and strikes before they blossom into so-called mass
incidents. At a meeting of the Chinese cabinet last month, Prime Minister Wen Jiabao told government
leaders they should prepare for rough times ahead. ``The country's employment situation is extremely
grim,'' he said.

To ameliorate the hardship of idled migrants, the central government has announced a series of
initiatives that include vocational training, an expansion of rural health care and crop subsidies
to ensure that those who return to the land can make a living despite a slump in agricultural
prices. A \$585 billion stimulus package introduced in November, much of it weighted toward
labor-intensive construction projects, is also expected to absorb some of the newly unemployed.

But here in Tanjia and the surrounding countryside of northeast Hunan Province, most people say they
have yet to see much in the way of government largess. As the Lunar New Year came to an end two
weeks ago, many migrants who had come home for the holidays were anxious to return south, where they
hoped to reclaim their old jobs or find new ones.

About 40 percent of the town's 2,000 residents work outside the province, and their remittances have
been a lifeline for the children and elderly people who remain behind. Much of that money has been
spent on motorcycles, high school educations and new homes, some trimmed with Corinthian columns and
ceramic dragons, that are the brick-and-mortar embodiment of this newfound prosperity.

Ms.~Tan's family home, like those of her neighbors, is a work in progress. Since 2005, her mother,
father and brother, all migrant workers, have poured \$15,000 into the two-story house, but they
still need another \$9,000 for appliances, fixtures and a white tiled facade. ``We have no
savings,'' said her father, Tan Liangsheng, 52, a haggard-looking man who recently lost his job as a
construction worker. ``All our hard work and bitterness is invested in this house.''

Just behind him sat the mud-brick structure where the extended Tan clan used to live.

In some ways, Tanjia's residents are luckier than most. Unlike China's drought-stricken north and
its chronically arid west, Hunan Province is well watered and blessed with a temperate climate that
allows farmers to grow food much of the year.

Still, with 64 million people squeezed into an area the size of Kansas, most people make do with
tiny plots of land; in Tanjia the average size is a tenth of an acre. ``Maybe we won't starve to
death, but life would become very difficult if everyone came back home,'' said Long Feng, 29, who
works at a car repair shop in Shenzhen, not far from the Hong Kong border.

In Zhuzhou, the nearest city of any consequence, government officials are not very concerned about a
surge in jobless farmers.

Chen Shuxian, director of Zhuzhou's employment center, said he was more worried about the 3.7
million people who live in and around his booming city, people who have become accustomed to
relatively comfortable lives. ``They have cellphone bills and rent to pay,'' he said. ``The migrants
don't have a lot of expectations and they can always fall back on the land and their family
savings.''

Such sentiments are common in China, where rural laborers are often viewed as dime-a-dozen
workhorses capable of enduring enormous hardship. He Xuefeng, a professor who studies rural life,
said many manufacturers believed the most productive workers were spent by 40.

``As workers grow older, they can't work as quickly or accurately, so they are naturally
eliminated,'' said Mr.~He, who teaches at Huazhong University of Science and Technology in Hubei
Province. ``The financial crisis will simply speed up that process by two or three years and force
them to return home earlier.''

After he lost his job at a glass factory in Guangzhou last year, Wang Liming, 39, returned to his
home on the outskirts of Zhuzhou thinking he could find employment nearby. Things turned more dire
after his wife lost her job just before the New Year festivities.

He acknowledged that there was work to be had in Zhuzhou, but those jobs generally pay less than
\$100 a month, about half what a semiskilled assembly line position pays in Guangzhou.

``I couldn't even afford my daughter's high school tuition on that kind of salary,'' he said,
standing in front of his home, a half-built box that lacks windows and a refrigerator.

A gruff, chain-smoking man, Mr.~Wang said the decade he spent in the south turned him off to
agricultural work. ``I hate working the fields,'' he said as his neighbors nodded in agreement. Even
if they wanted to, he and his fellow villagers could not make much money from farming: some of the
best patches of land have been swallowed up by Zhuzhou's rapid development, including the electric
generating plant that dominates the view from his front door.

Asked about his plans, Mr.~Wang shook his head, glanced at his cellphone and said he was waiting for
friends in Guangzhou to call him about a job. ``I'm just hoping the phone rings,'' he said.

\section{In Silicon Valley, Recruiters Are Sending Out Their Own R\'esum\'es}

MOUNTAIN VIEW, Calif. -- It is hard to think of any job-hunting skills that Alexis Lovell lacks. As
a recruiter for Silicon Valley technology companies, and before that, for retailers, she has advised
job candidates on r\'esum\'e preparation, personal presentation and interview skills for the last
eight years. Networking strategies and trolling social networks and online job sites are the tools
of her trade.

Yet none of those things is helping one candidate in need of a job these days: Ms.~Lovell herself.

Unemployed since mid-November, when Plantronics let go of its five recruiters, Ms.~Lovell has
reached out by e-mail message to nearly 400 well-connected hiring managers and technology executives
she knows, and she has phoned about that many.

``No bites,'' she said during a networking luncheon for recruiters earlier this month in Mountain
View, not far from the campuses of Google, Yahoo, Microsoft and other tech giants. When she is not
looking for work, Ms.~Lovell spends much of her time with her 2-year-old daughter, whom she took out
of day care to save money.

``I am trying to make the best of my time at home,'' Ms.~Lovell said. ``And not shop,'' she
chuckled.

The majority of the approximately 90 recruiters who attended the networking luncheon were in the
same situation. The monthly luncheon, now in its 11th year, has long been a source of job leads for
countless recruiters, and many showed up last week with the faint hope of hearing about an opening
for themselves. What they found were old friends, unemployed colleagues and words of encouragement.
They also got a few tips on adapting their skills to other professions and one offer for affordable
health care.

``It was pretty hard to see so many people in the same situation,'' Ms.~Lovell said.

There are no precise counts of recruiters in Silicon Valley, and no one knows how many are
unemployed. But interviews with more than two dozen recruiters suggest that the recession has
slammed the profession particularly hard, both here and across the country.

Scores of recruiters have been let go in recent months and new positions are virtually nonexistent.
Those that pop up attract as many as 500 applicants. And rates paid to recruiters, many of whom work
as contractors, have fallen by about 50 percent.

``Recruiters are kind of the canary in the coal mine,'' said John Moed, who moderates an online
group for San Francisco-area recruiters that has about 3,700 members. ``When things are great, the
bird is singing away and you can't find enough recruiters. But they are the first to go when things
are slow.''

First indeed. Consider Google, a company that in 10 years had never laid off employees because of
economic conditions. In its first round of recession-related job cuts last month, it fired 100
recruiters.

Most recruiters in Silicon Valley, however, work as contractors, so they typically lose their jobs
with little fanfare: there is no layoff announcement, just a contract that ends and is not renewed.
Before it laid off its staff recruiters, Google had quietly cut a small army of contract recruiters
around the world, which several people who know the company said had numbered in the hundreds.

And as contractors, many recruiters who find themselves jobless cannot collect unemployment.

Recruiters have never been the elite denizens of Silicon Valley. That is a distinction reserved for
the rock stars of Silicon Valley, the engineers, serial entrepreneurs, product designers or
marketers or the venture capitalists who finance start-ups.

But recruiters have long played a vital role as foot soldiers in the Valley's famous talent wars for
those rock stars. When the emerging Web 2.0 companies like Facebook, YouTube and LinkedIn competed
with each other and with more established players like Google and Yahoo for top-flight talent,
recruiters were in high demand. Wages rose accordingly and many good recruiters could easily command
an hourly rate of \$100, which for a full-time contract translates to about \$200,000 a year. (Many
recruiters now say they would be lucky to find work that pays \$30 to \$50 an hour.)

Ms.~Lovell spent many of those good years at Google, where, as a contractor, she helped recruit
other recruiters and built the company's global talent acquisition team. While Google paid less than
some other large companies -- \$50 to \$90 an hour, according to people with knowledge of its
compensation plans -- the rewards of working for the Valley's hottest company made up for it,
Ms.~Lovell said.

``It felt like the pinnacle of my career,'' Ms.~Lovell said. ``As a recruiter in the good times, it
is really good.''

Back then, Google was hiring at a furious rate. In the middle of 2007, it added more than 2,100
workers in a single quarter. In the most recent quarter, Google grew by a mere 99 positions, and the
slowdown in hiring goes a long way toward explaining the layoffs in recruiting.

The memories of a painful downturn still haunt many in Silicon Valley. It was only eight years ago
in the dot-com collapse that one in five of the region's jobs vanished. Yet many recruiters say that
for them, things are worse this time around.

``Since October, the business has been dreadful,'' said Herb Deitz, who, during the dot-com crash,
had to let go all 30 recruiters who worked for him at a technology consulting firm. ``It's probably
the worst that I've seen it.''

The dot-com meltdown left several pockets of strength in the technology sector and biotechnology.
Mr.~Deitz went to work for VMware, a fast-growing company that provides technology to data centers.

Others left the recruiting profession and applied their sales skills in more promising sectors of
the economy, especially real estate and mortgages.

Debra Young was one of them. She got a real estate license and began working as a mortgage broker.
But recruiting is her passion, so in 2004, when things began to pick up again in Silicon Valley, she
returned to the talent wars and enjoyed a few good years. Two days before Christmas, her contract
with Yahoo ended, and she has not found anything since.

With no credit card debt, no car payments and no ``mortgage mess,'' Ms.~Young said she was not too
worried about making it through this downturn. ``I have no problem living frugally,'' she said. She
kept a hand in real estate and is still underwriting mortgages.

The biggest toll, she said, is emotional. And if things don't pick up, she is confident that she can
make another career switch.

``Reinventing yourself isn't that much fun, but I can do it,'' Ms.~Young said.

Ms.~Lovell, whose husband is still working, said she had not given up hope. ``I'm trying to remain
positive,'' she said. But going from two incomes to one has not been easy.

``We are just being ultra-sensitive and aware how close to the edge we are,'' Ms.~Lovell said. ``It
has been a tremendous shift for us to lose that income.''



\pagebreak 
\printindex
\end{CJK*}
\end{document}
