\documentclass[12pt]{article}
\usepackage{config}

\chead{\scriptsize{\textsf{美军士兵守则}}}

\begin{document}
\setcounter{section}{0}
\pagestyle{fancy}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}


\begin{center}
\makebox[0.2\textwidth][s]{\Large \textsf{美军士兵守则}}
\end{center}

\newcommand{\aarrule}[2]{%
\begin{minipage}{1\columnwidth}%
\vspace{1ex}
{\color{blue} #1}

{\small #2}
\vspace{1ex}
\end{minipage}
}

\aarrule{1. You are not a superman.}{你不是超人.(不要无谓的冒险,不要做傻事)}

\aarrule{2. If it's stupid but works,it isn't stupid.}{如果一个蠢方法有效,那它就不是一个蠢方法.}

\aarrule{3. Don't look conspicuous - it draws fire. (This is why aircraft carriers are c called
``Bomb Magnets''.)}{不要太显眼,因为那会引来对方火力攻击.(这就是航母被称为``炸弹磁铁''的原因.)}

\aarrule{4. Never share a foxhole with anyone braver than you are.}{别和比你勇敢的战友躲在同一个散兵
坑里.}

\aarrule{5. Never forget that the lowest bidder made your weapon.}{别忘了你手上的武器是由最低价的承包
商得标制造的.}

\aarrule{6. If your attack is going really well,it's an ambush.}{如果你的攻击进行得很顺利,那一定是你
中了圈套.}

\aarrule{7. All five-second grenade fuses will burn down in three seconds.}{所有五秒的手榴弹引线都会
在三秒内烧完.}

\aarrule{8. Try to look unimportant because bad guys may be low on ammo.}{尽量显得是一个无关紧要的人,因
为敌人可能弹药不够了.(他会先打最重要的人)}

\aarrule{9. If you are forward of your position,the artillary will fall short.}{每当你要攻击前进时,炮
兵往往也快要用完了炮弹.}

\aarrule{10. The enemy diversion you are ignoring is the main attack.}{那支你以为是敌军疑兵而不加注意
的部队恰恰就是敌人的攻击主力.}

\aarrule{11. The important things are always simple.}{重要的事总是简单的.}

\aarrule{12. The simple things are always hard.}{简单的事总是难作到.}

\aarrule{13. The easy way is always mined.}{好走的路总是已被敌军布上了地雷.}

\aarrule{14. If you are short of everything except enemy. You are in combat.}{如果你除了敌人不缺,其它
什么都缺,那你往往就要面临作战了.}

\aarrule{15. Incoming fire has the right of way.}{飞来的子弹有优先通行权.(挡它的道你就要倒大楣!)}

\aarrule{16. If the enemy is in range, SO ARE YOU!}{如果敌人正在你的射程内,你也是.}

\aarrule{17. No combat ready unit has ever passed inspections.}{从没有一支完成战备的单位能通过校阅.}

\aarrule{18. Things that must be together to work usually can't be shipped together.}{必须要装配在一
起才能发挥效力的武器装备通常不会一起运来.}

\aarrule{19. Radios will fail as soon as you need fire support desperately.}{无线电通讯会有可能在你
急需火力支援时失灵.}

\aarrule{20. Anything you do can get you shot - including doing nothing.}{你作的任何事都可能挨枪子儿
-- 包括你什么都不做.}

\aarrule{21. Tracers work both ways.}{曳光弹可以帮你找到敌踪;但也会让敌人找到你.}

\aarrule{22. The only thing more accurate than incoming enemy fire is incoming friendly fire.}{唯一比
敌人火力还精确的是友军打过来的炮火.(误射)}

\aarrule{23. Make it tough for the enemy to get in and you can't get out.}{当你防守严密到敌人攻不进来
时,那往往你自己也打不出去.}

\aarrule{24. If you take more than your fair share of objectives, you will have more than your fair
share of objectives to take.}{如果你多报战功,那下次你会被给予超过你能力的目标让你去打.(自讨苦吃)}

\aarrule{25. When both sides are convinced that they are about to lose, they are both right.}{当两军
都觉得自己快输时,那他们可能都是对的.}

\aarrule{26. Professional soldiers are predictable but the world is full of amateurs.}{专业士兵的行为
是你能预测的,可惜战场上业余的士兵占多数,因此敌人的行为大部分是你所无法预测的.}

\end{document}

