% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Wu Xiaochun}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{10 Parkway Forest Dr.}
 \moveleft.5\hoffset\centerline{North York, ON M2J 1L3}
 \moveleft.5\hoffset\centerline{(647) 918-9825}


\begin{resume}
 
\section{OBJECTIVE}  A position in the field of computers with special 
                interests in telecom or business applications programming, 
                information processing, and management systems. 
 

\section{EDUCATION} 
                {\sl Master of Science,} Instrument Science Engineering\\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                Southeast University, Nanjing, China, 
                April 1999 \\
                Concentration: Computer Science \\

                {\sl Bachelor of Science,} Electrical Engineering\\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                Nanchang University, Nanchang, China, 
                July 1996 \\
                Concentration: Electrical Machine \\
 
 
\section{SKILLS} 
                {\sl Computer Skills:} C, C++, Java, OOA, OOD.

                {\sl Knowledges:} Telecom Network, Next Generation Network (NGN), Softswitch, Voice
                over IP technology. SIP, H.323 and other related protocols.
                Project Management Knowledges, CMM.
 
\section{EXPERIENCE} 
                {\sl Software development Manager} \hfill July 2006 - Auguest 2011 \\
                Network Division of ZTE Corporation, China
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Incharging of the whole process of software development for ZTE Softswich
                   device
                 \item Incharging of system analysis and design
                 \item Incharging of totally telcom solution design and decision

{\it
                   ZTE Softswich is a core device of Next Generation Network (NGN) which support
                   over million users. And it is one of the more successful products of ZTE. as
                   oppucies the largest market share in China. Even in world telcom market, ZTE is
                   also a major device provider.
}
                \end{itemize}
 
                {\sl System Analysis and Design Engineer} \hfill  April 2003 - July 2006 \\
                Network Division of ZTE Corporation, China
                Institute 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Incharging of System analysis and design for new ZTE VoIP Gateway
                 \item Director of software development of stack module of Gateway
                 \item Analysis user requirements and protocol
                 \item Coding using C and Java languages

                   {\it This type of Gateway is the first VoIP gateway for telecommunication market
                     which support up to 7200 concurrent busy lines. }

                 \end{itemize} 

                {\sl Software Development Engineer} \hfill        April 1999 - April 2003 \\
                Network Division of ZTE Corporation, China
                  \begin{itemize}
                   \item Analysis user requirements and protocol
                   \item Coding using C languages

                     {\sl In charge of H.323 stack module's development and maintenance. This module
                       is the core part of ZTE VoIP Gateway which is aimed to enterprise market. ZTE
                       VoIP Gateway supports 120 concurrent busy lines. }
                   \end{itemize} 
\end{resume}
\end{document}
